\bibitem{apache_drill}
Apache drill.
\newblock \url{https://drill.apache.org/}.

\bibitem{Agarwal2013}
S.~Agarwal, B.~Mozafari, A.~Panda, H.~Milner, S.~Madden, and I.~Stoica.
\newblock {BlinkDB: Queries with Bounded Errors and Bounded Response Times on
  Very Large Data}.
\newblock In {\em Proceedings of the ACM European Conference on Computer
  Systems (EuroSys)}, pages 29--42, 2013.

\bibitem{Agrawal2004}
S.~Agrawal, S.~Chaudhuri, L.~Koll{\'{a}}r, A.~P. Marathe, V.~R. Narasayya, and
  M.~Syamala.
\newblock {Database Tuning Advisor for Microsoft SQL Server 2005}.
\newblock In {\em Proceedings of the International Conference on Very Large
  Data Bases (VLDB)}, pages 1110--1121, 2004.

\bibitem{scientific_data}
A.~Ailamaki, V.~Kantere, and D.~Dash.
\newblock Managing scientific data.
\newblock {\em Communications of the ACM}, 53, 06 2010.

\bibitem{Alagiannis2012a}
I.~Alagiannis, R.~Borovica, M.~Branco, S.~Idreos, and A.~Ailamaki.
\newblock {NoDB: Efficient Query Execution on Raw Data Files}.
\newblock In {\em Proceedings of the ACM SIGMOD International Conference on
  Management of Data}, pages 241--252, 2012.

\bibitem{Alagiannis2015}
I.~Alagiannis, R.~Borovica-Gajic, M.~Branco, S.~Idreos, and A.~Ailamaki.
\newblock {NoDB: Efficient Query Execution on Raw Data Files}.
\newblock {\em Communications of the ACM}, 58(12):112--121, 2015.

\bibitem{quERy}
H.~Altwaijry, S.~Mehrotra, and D.~V. Kalashnikov.
\newblock {QuERy: A Framework for Integrating Entity Resolution with Query
  Processing}.
\newblock {\em {PVLDB}}, 9(3), 2015.

\bibitem{Chaudhuri2001b}
S.~Chaudhuri, G.~Das, and V.~Narasayya.
\newblock {A Robust, Optimization-based Approach for Approximate Answering of
  Aggregate Queries}.
\newblock In {\em Proceedings of the ACM SIGMOD International Conference on
  Management of Data}, pages 295--306, 2001.

\bibitem{Chaudhuri1997}
S.~Chaudhuri and V.~R. Narasayya.
\newblock {An Efficient Cost-Driven Index Selection Tool for Microsoft SQL
  Server}.
\newblock In {\em Proceedings of the International Conference on Very Large
  Data Bases (VLDB)}, pages 146--155, 1997.

\bibitem{Chen2012a}
Y.~Chen, S.~Alspaugh, and R.~H. Katz.
\newblock {Interactive Analytical Processing in Big Data Systems: A
  Cross-Industry Study of MapReduce Workloads}.
\newblock {\em Proceedings of the VLDB Endowment}, 5(12):1802--1813, 2012.

\bibitem{Cormode2012}
G.~Cormode, M.~N. Garofalakis, P.~J. Haas, and C.~Jermaine.
\newblock {Synopses for Massive Data: Samples, Histograms, Wavelets, Sketches}.
\newblock {\em Foundations and Trends in Databases}, 4(1-3):1--294, 2012.

\bibitem{nadeef}
M.~Dallachiesa, A.~Ebaid, A.~Eldawy, A.~Elmagarmid, I.~F. Ilyas, M.~Ouzzani,
  and N.~Tang.
\newblock {NADEEF: A Commodity Data Cleaning System}.
\newblock In {\em {SIGMOD}}, 2013.

\bibitem{exploratory_analysis}
T.~Dasu and T.~Johnson.
\newblock {\em Exploratory Data Mining and Data Cleaning}.
\newblock John Wiley \& Sons, Inc., New York, NY, USA, 1 edition, 2003.

\bibitem{dependencies}
W.~Fan.
\newblock Dependencies revisited for improving data quality.
\newblock In {\em {PODS}}, 2008.

\bibitem{data_quality}
W.~Fan.
\newblock Data quality: From theory to practice.
\newblock {\em SIGMOD Rec.}, 44(3):7--18, Dec. 2015.

\bibitem{monoids}
L.~Fegaras and D.~Maier.
\newblock {Optimizing Object Queries Using an Effective Calculus}.
\newblock {\em TODS}, 25(4):457--516, Dec. 2000.

\bibitem{query_driven_cleaning}
S.~Giannakopoulou.
\newblock Query-driven data cleaning for exploratory queries.
\newblock In {\em {CIDR} 2019, 9th Biennial Conference on Innovative Data
  Systems Research, Asilomar, CA, USA, January 13-16, 2019, Online
  Proceedings}, 2019.

\bibitem{cleanm}
S.~Giannakopoulou, M.~Karpathiotakis, B.~Gaidioz, and A.~Ailamaki.
\newblock Cleanm: An optimizable query language for unified scale-out data
  cleaning.
\newblock {\em Proc. VLDB Endow.}, 10(11):1466--1477, Aug. 2017.

\bibitem{incomplete_dbs}
P.~Guagliardo and L.~Libkin.
\newblock Making sql queries correct on incomplete databases: A feasibility
  study.
\newblock In {\em Proceedings of the 35th ACM SIGMOD-SIGACT-SIGAI Symposium on
  Principles of Database Systems}, PODS '16, pages 211--223, New York, NY, USA,
  2016. ACM.

\bibitem{transform-by-ex}
Y.~He, K.~Ganjam, K.~Lee, Y.~Wang, V.~Narasayya, S.~Chaudhuri, X.~Chu, and
  Y.~Zheng.
\newblock Transform-data-by-example (tde): Extensible data transformation in
  excel.
\newblock In {\em Proceedings of the 2018 International Conference on
  Management of Data}, SIGMOD '18, pages 1785--1788, New York, NY, USA, 2018.
  ACM.

\bibitem{IBM2012}
IBM.
\newblock {Managing big data for smart grids and smart meters}.
\newblock {\em IBM White Paper}, 2012.

\bibitem{Idreos2011a}
S.~Idreos, I.~Alagiannis, R.~Johnson, and A.~Ailamaki.
\newblock {Here are my Data Files. Here are my Queries. Where are my Results?}
\newblock In {\em Proceedings of the Biennial Conference on Innovative Data
  Systems Research (CIDR)}, pages 57--68, 2011.

\bibitem{Idreos2011}
S.~Idreos, S.~Manegold, H.~Kuno, and G.~Graefe.
\newblock {Merging What's Cracked, Cracking What's Merged: Adaptive Indexing in
  Main-Memory Column-Stores}.
\newblock {\em Proceedings of the VLDB Endowment}, 4(9):586--597, 2011.

\bibitem{quickr}
S.~Kandula, A.~Shanbhag, A.~Vitorovic, M.~Olma, R.~Grandl, S.~Chaudhuri, and
  B.~Ding.
\newblock {Quickr: Lazily Approximating Complex AdHoc Queries in BigData
  Clusters}.
\newblock In {\em SIGMOD}, 2016.

\bibitem{Karpathiotakis2016}
M.~Karpathiotakis, I.~Alagiannis, and A.~Ailamaki.
\newblock {Fast Queries Over Heterogeneous Data Through Engine Customization}.
\newblock {\em Proceedings of the VLDB Endowment}, 9(12):972--983, 2016.

\bibitem{Karpathiotakis2015}
M.~Karpathiotakis, I.~Alagiannis, T.~Heinis, M.~Branco, and A.~Ailamaki.
\newblock {Just-In-Time Data Virtualization: Lightweight Data Management with
  ViDa}.
\newblock In {\em Proceedings of the Biennial Conference on Innovative Data
  Systems Research (CIDR)}, 2015.

\bibitem{Karpathiotakis2014}
M.~Karpathiotakis, M.~Branco, I.~Alagiannis, and A.~Ailamaki.
\newblock {Adaptive Query Processing on RAW Data}.
\newblock {\em Proceedings of the VLDB Endowment}, 7(12):1119--1130, 2014.

\bibitem{bigdansing}
Z.~Khayyat, I.~F. Ilyas, A.~Jindal, S.~Madden, M.~Ouzzani, P.~Papotti, J.-A.
  Quian{\'e}-Ruiz, N.~Tang, and S.~Yin.
\newblock {BigDansing: A System for Big Data Cleansing}.
\newblock In {\em {SIGMOD}}, 2015.

\bibitem{buckley_new_2012}
S.~Lohr.
\newblock {For Big-Data Scientists, 'Janitor Work' Is Key Hurdle to Insights,
  The New York Times}, 2014.

\bibitem{online_queryrelax}
I.~Muslea and T.~J. Lee.
\newblock Online query relaxation via bayesian causal structures discovery.
\newblock In {\em AAAI}, 2005.

\bibitem{Olma2017a}
M.~Olma, M.~Karpathiotakis, I.~Alagiannis, M.~Athanassoulis, and A.~Ailamaki.
\newblock {Slalom: Coasting Through Raw Data via Adaptive Partitioning and
  Indexing}.
\newblock {\em Proceedings of the VLDB Endowment}, 10(10):1106--1117, 2017.

\bibitem{Olma2019}
M.~Olma, O.~Papapetrou, R.~Appuswamy, and A.~Ailamaki.
\newblock {Taster: Self-Tuning, Elastic and Online Approximate Query
  Processing}.
\newblock In {\em Proceedings of the IEEE International Conference on Data
  Engineering (ICDE)}, 2019.

\bibitem{Papadomanolakis2004}
S.~Papadomanolakis and A.~Ailamaki.
\newblock {AutoPart: Automating Schema Design for Large Scientific Databases
  Using Data Partitioning}.
\newblock In {\em Proceedings of the International Conference on Scientific and
  Statistical Database Management (SSDBM)}, page 383, 2004.

\bibitem{Schnaitter2006}
K.~Schnaitter, S.~Abiteboul, T.~Milo, and N.~Polyzotis.
\newblock {COLT: Continuous On-Line Database Tuning}.
\newblock In {\em Proceedings of the ACM SIGMOD International Conference on
  Management of Data}, pages 793--795, 2006.

\bibitem{xml_to_relational}
J.~Shanmugasundaram, K.~Tufte, C.~Zhang, G.~He, D.~J. DeWitt, and J.~F.
  Naughton.
\newblock Relational databases for querying xml documents: Limitations and
  opportunities.
\newblock In {\em Proceedings of the 25th International Conference on Very
  Large Data Bases}, VLDB '99, pages 302--314, San Francisco, CA, USA, 1999.
  Morgan Kaufmann Publishers Inc.

\bibitem{queryrelax_incomplete}
S.~Shen.
\newblock Database relaxation: An approach to query processing in incomplete
  databases.
\newblock {\em Information Processing and Management}, 24(2):151 -- 159, 1988.

\bibitem{onesize_fitsall}
M.~Stonebraker.
\newblock Technical perspective - one size fits all: an idea whose time has
  come and gone.
\newblock {\em Commun. ACM}, 51:76, 2008.

\bibitem{Stonebraker_datacuration}
M.~Stonebraker, G.~Beskales, A.~Pagan, D.~Bruckner, M.~Cherniack, S.~Xu,
  V.~Analytics, I.~F. Ilyas, and S.~Zdonik.
\newblock {Data Curation at Scale: The Data Tamer System}.
\newblock In {\em CIDR}, 2013.

\bibitem{probabilistic_dbs}
D.~Suciu, D.~Olteanu, R.~Christopher, and C.~Koch.
\newblock {\em Probabilistic Databases}.
\newblock Morgan \& Claypool Publishers, 1st edition, 2011.

\bibitem{eda}
J.~W. Tukey.
\newblock {\em Exploratory data analysis}.
\newblock Addison-Wesley series in behavioral science : quantitative methods.
  Addison-Wesley, 1977.

\bibitem{scare}
M.~Yakout, L.~Berti-\'{E}quille, and A.~K. Elmagarmid.
\newblock Don't be scared: Use scalable automatic repairing with maximal
  likelihood and bounded changes.
\newblock In {\em Proceedings of the 2013 ACM SIGMOD International Conference
  on Management of Data}, SIGMOD '13, pages 553--564, New York, NY, USA, 2013.
  ACM.

\bibitem{spark}
M.~Zaharia, M.~Chowdhury, T.~Das, A.~Dave, J.~Ma, M.~McCauley, M.~J. Franklin,
  S.~Shenker, and I.~Stoica.
\newblock {Resilient Distributed Datasets: A Fault-tolerant Abstraction for
  In-memory Cluster Computing}.
\newblock In {\em NSDI}, 2012.

\bibitem{data_growth}
M.~Zwolenski, L.~Weatherill, et~al.
\newblock The digital universe: Rich data and the increasing value of the
  internet of things.
\newblock {\em Australian Journal of Telecommunications and the Digital
  Economy}, 2(3):47, 2014.