\begin{thebibliography}{10}
\itemsep=1pt
\begin{small}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%introduction
\bibitem{hyndman2018forecasting}Hyndman, R. \& Athanasopoulos, G. Forecasting: principles and practice. (OTexts,2018)

\bibitem{gardner2006exponential}Gardner Jr, E. Exponential smoothing: The state of the art—Part II. {\em International Journal Of Forecasting}. \textbf{22}, 637-666 (2006)

\bibitem{shi2015convolutional}Shi, X., Chen, Z., Wang, H., Yeung, D., Wong, W. \& Woo, W. Convolutional LSTM network: A machine learning approach for precipitation nowcasting. {\em Advances In Neural Information Processing Systems}. \textbf{28} (2015)

\bibitem{Dwork2006}
C.~Dwork, ``Differential privacy,'' in \emph{International colloquium on
	automata, languages, and programming}.\hskip 1em plus 0.5em minus 0.4em\relax
Springer, 2006, pp. 1--12.

\bibitem{ye2020local}Ye, Q. \& Hu, H. Local differential privacy: Tools, challenges, and opportunities. {\em International Conference On Web Information Systems Engineering}. pp. 13-23 (2020)

\bibitem{Yang2023}
M.~Yang, T.~Guo, T.~Zhu, I.~Tjuawinata, J.~Zhao, and K.-Y. Lam, ``Local
differential privacy and its applications: A comprehensive survey,''
\emph{Computer Standards \& Interfaces}, p. 103827, 2023.

\bibitem{wang2017locally}Wang, T., Blocki, J., Li, N. \& Jha, S. Locally differentially private protocols for frequency estimation. {\em 26th USENIX Security Symposium (USENIX Security 17)}. pp. 729-745 (2017)

\bibitem{wang2018privacy}Wang, Z., Pang, X., Chen, Y., Shao, H., Wang, Q., Wu, L., Chen, H. \& Qi, H. Privacy-preserving crowd-sourced statistical data publishing with an untrusted server. {\em IEEE Transactions On Mobile Computing}. \textbf{18}, 1356-1367 (2018)

\bibitem{wang2019locallyhv}Wang, T., Li, N. \& Jha, S. Locally differentially private heavy hitter identification. {\em IEEE Transactions On Dependable And Secure Computing}. \textbf{18}, 982-993 (2019)

\bibitem{fu2023collecting}Fu, Y., Ye, Q., Du, R. \& Hu, H. Collecting Multi-type and Correlation-Constrained Streaming Sensor Data with Local Differential Privacy. {\em ACM Transactions On Sensor Networks}. (2023)

\bibitem{li2020estimating}Li, Z., Wang, T., Lopuhaä-Zwakenberg, M., Li, N. \& Škoric, B. Estimating numerical distributions under local differential privacy. {\em Proceedings Of The 2020 ACM SIGMOD International Conference On Management Of Data}. pp. 621-635 (2020)

\bibitem{ye2020towards}Ye, Q., Hu, H., Au, M., Meng, X. \& Xiao, X. Towards locally differentially private generic graph metric estimation. {\em 2020 IEEE 36th International Conference On Data Engineering (ICDE)}. pp. 1922-1925 (2020)

\bibitem{zhang2012functional}Zhang, J., Zhang, Z., Xiao, X., Yang, Y. \& Winslett, M. Functional mechanism: Regression analysis under differential privacy. {\em ArXiv Preprint ArXiv:1208.0219}. (2012)

\bibitem{abadi2016deep}Abadi, M., Chu, A., Goodfellow, I., McMahan, H., Mironov, I., Talwar, K. \& Zhang, L. Deep learning with differential privacy. {\em Proceedings Of The 2016 ACM SIGSAC Conference On Computer And Communications Security}. pp. 308-318 (2016)

\bibitem{fu2023dpsur}Fu, J., Ye, Q., Hu, H., Chen, Z., Wang, L., Wang, K. \& Xun, R. DPSUR: Accelerating Differentially Private Stochastic Gradient Descent Using Selective Update and Release. {\em ArXiv Preprint ArXiv:2311.14056}. (2023)


\bibitem{dwork2010differential}Dwork, C., Naor, M., Pitassi, T. \& Rothblum, G. Differential privacy under continual observation. {\em Proceedings Of The Forty-second ACM Symposium On Theory Of Computing}. pp. 715-724 (2010)

\bibitem{chan2011private}Chan, T., Shi, E. \& Song, D. Private and continual release of statistics. {\em ACM Transactions On Information And System Security (TISSEC)}. \textbf{14}, 1-24 (2011)

\bibitem{fan2013adaptive}Fan, L. \& Xiong, L. An adaptive approach to real-time aggregate monitoring with differential privacy. {\em IEEE Transactions On Knowledge And Data Engineering}. \textbf{26}, 2094-2106 (2013)

\bibitem{Kellaris14}Kellaris, G., Papadopoulos, S., Xiao, X. \& Papadias, D. Differentially private event sequences over infinite streams. {\em Proc. VLDB Endow.}. \textbf{7}, 1155-1166 (2014,8), https://doi.org/10.14778/2732977.2732989

\bibitem{shao2020structured}Shao, M., Li, J., Yan, Q., Chen, F., Huang, H. \& Chen, X. Structured sparsity model based trajectory tracking using private location data release. {\em IEEE Transactions On Dependable And Secure Computing}. \textbf{18}, 2983-2995 (2020)

\bibitem{cao2017quantifying}Cao, Y., Yoshikawa, M., Xiao, Y. \& Xiong, L. Quantifying differential privacy under temporal correlations. {\em 2017 IEEE 33rd International Conference On Data Engineering (ICDE)}. pp. 821-832 (2017)

\bibitem{xiao2017loclok}Xiao, Y., Xiong, L., Zhang, S. \& Cao, Y. Loclok: Location cloaking with differential privacy via hidden markov model. {\em Proceedings Of The VLDB Endowment}. \textbf{10}, 1901-1904 (2017)

\bibitem{dwork2014algorithmic}Dwork, C., Roth, A. \& Others The algorithmic foundations of differential privacy. {\em Foundations And Trends® In Theoretical Computer Science}. \textbf{9}, 211-407 (2014)

\bibitem{zhao2022survey}Zhao, Y. \& Chen, J. A survey on differential privacy for unstructured data content. {\em ACM Computing Surveys (CSUR)}. \textbf{54}, 1-28 (2022)

\bibitem{zhao2024scenario}Zhao, Y., Du, J. \& Chen, J. Scenario-based Adaptations of Differential Privacy: A Technical Survey. {\em ACM Computing Surveys}. \textbf{56}, 1-39 (2024)

\bibitem{miranda2023sok}Miranda-Pascual, À., Guerra-Balboa, P., Parra-Arnau, J., Forné, J. \& Strufe, T. SoK: Differentially private publication of trajectory data. {\em Proceedings On Privacy Enhancing Technologies}. (2023)

\bibitem{katsomallos2019privacy}Katsomallos, M., Tzompanaki, K. \& Kotzinos, D. Privacy, space and time: A survey on privacy-preserving continuous data publishing. {\em Journal Of Spatial Information Science}. \textbf{2019}, 57-103 (2019)

\bibitem{li2015matrix}Li, C., Miklau, G., Hay, M., McGregor, A. \& Rastogi, V. The matrix mechanism: optimizing linear counting queries under differential privacy. {\em The VLDB Journal}. \textbf{24} pp. 757-781 (2015)

\bibitem{andres2013geo}Andrés, M., Bordenabe, N., Chatzikokolakis, K. \& Palamidessi, C. Geo-indistinguishability: Differential privacy for location-based systems. {\em Proceedings Of The 2013 ACM SIGSAC Conference On Computer \& Communications Security}. pp. 901-914 (2013)


	
	
	
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%Preliminaries
\bibitem{Ding2017}
B.~Ding, J.~Kulkarni, and S.~Yekhanin, ``Collecting telemetry data privately,''
\emph{Advances in Neural Information Processing Systems}, vol.~30, 2017.

\bibitem{Erlingsson2014}
{\'U}.~Erlingsson, V.~Pihur, and A.~Korolova, ``Rappor: Randomized aggregatable
privacy-preserving ordinal response,'' in \emph{Proceedings of the 2014 ACM
	SIGSAC conference on computer and communications security}, 2014, pp.
1054--1067.

\bibitem{Thakurta2017}
A.~G. Thakurta, A.~H. Vyrros, U.~S. Vaishampayan, G.~Kapoor, J.~Freudiger,
V.~R. Sridhar, and D.~Davidson, ``Learning new words,'' Mar.~14 2017, uS
Patent 9,594,741.


\bibitem{Dwork2019}
C.~Dwork, ``{Differential Privacy and the US Census},'' in \emph{Proceedings of
	the 38th ACM SIGMOD-SIGACT-SIGAI symposium on principles of database
	systems}, 2019, pp. 1--1.
	
\bibitem{li2017differential}Li, N., Lyu, M., Su, D. \& Yang, W. Differential privacy: From theory to practice. (Springer,2017)

\bibitem{kifer2014pufferfish}Kifer, D. \& Machanavajjhala, A. Pufferfish: A framework for mathematical privacy definitions. {\em ACM Transactions On Database Systems (TODS)}. \textbf{39}, 1-36 (2014)

	
\bibitem{song2017pufferfish}Song, S., Wang, Y. \& Chaudhuri, K. Pufferfish privacy mechanisms for correlated data. {\em Proceedings Of The 2017 ACM International Conference On Management Of Data}. pp. 1291-1306 (2017)	

\bibitem{korolova2009releasing}Korolova, A., Kenthapadi, K., Mishra, N. \& Ntoulas, A. Releasing search queries and clicks privately. {\em Proceedings Of The 18th International Conference On World Wide Web}. pp. 171-180 (2009)

\bibitem{xiao2010differential}Xiao, X., Wang, G. \& Gehrke, J. Differential privacy via wavelet transforms. {\em IEEE Transactions On Knowledge And Data Engineering}. \textbf{23}, 1200-1214 (2010)

\bibitem{wang2019collecting}Wang, N., Xiao, X., Yang, Y., Zhao, J., Hui, S., Shin, H., Shin, J. \& Yu, G. Collecting and analyzing multidimensional data with local differential privacy. {\em 2019 IEEE 35th International Conference On Data Engineering (ICDE)}. pp. 638-649 (2019)

\bibitem{xue2022mean}Xue, Q., Zhu, Y. \& Wang, J. Mean estimation over numeric data with personalized local differential privacy. {\em Frontiers Of Computer Science}. \textbf{16} pp. 1-10 (2022)

\bibitem{zhou2022locally}Zhou, M., Wang, T., Chan, T., Fanti, G. \& Shi, E. Locally differentially private sparse vector aggregation. {\em 2022 IEEE Symposium On Security And Privacy (SP)}. pp. 422-439 (2022)

\bibitem{wei2024aaa}Wei, F., Bao, E., Xiao, X., Yang, Y. \& Ding, B. AAA: an Adaptive Mechanism for Locally Differential Private Mean Estimation. {\em ArXiv Preprint ArXiv:2404.01625}. (2024)
	
\bibitem{ye2020lf}Ye, Q., Hu, H., Au, M., Meng, X. \& Xiao, X. LF-GDPR: A framework for estimating graph metrics with local differential privacy. {\em IEEE Transactions On Knowledge And Data Engineering}. \textbf{34}, 4905-4920 (2020)

\bibitem{ma2024decision}Ma, Y., Zhang, H., Cai, Y. \& Yang, H. Decision tree for locally private estimation with public data. {\em Advances In Neural Information Processing Systems}. \textbf{36} (2024)

\bibitem{esling2012time}Esling, P. \& Agon, C. Time-series data mining. {\em ACM Computing Surveys (CSUR)}. \textbf{45}, 1-34 (2012)


\bibitem{silva2013data}Silva, J., Faria, E., Barros, R., Hruschka, E., Carvalho, A. \& Gama, J. Data stream clustering: A survey. {\em ACM Computing Surveys (CSUR)}. \textbf{46}, 1-31 (2013)	

\bibitem{ruiz2021great}Ruiz, A., Flynn, M., Large, J., Middlehurst, M. \& Bagnall, A. The great multivariate time series classification bake off: a review and experimental evaluation of recent algorithmic advances. {\em Data Mining And Knowledge Discovery}. \textbf{35}, 401-449 (2021)

%\bibitem{zhao2022survey}Zhao, Y. \& Chen, J. A survey on differential privacy for unstructured data content. {\em ACM Computing Surveys (CSUR)}. \textbf{54}, 1-28 (2022)






%%%%%%% Count query
\bibitem{dong2023continual}Dong, W., Luo, Q. \& Yi, K. Continual Observation under User-level Differential Privacy. {\em 2023 IEEE Symposium On Security And Privacy (SP)}. pp. 2190-2207 (2023)

\bibitem{henzinger2023almost}Henzinger, M., Upadhyay, J. \& Upadhyay, S. Almost tight error bounds on differentially private continual counting. {\em Proceedings Of The 2023 Annual ACM-SIAM Symposium On Discrete Algorithms (SODA)}. pp. 5003-5039 (2023)

\bibitem{cardoso2022differentially}Cardoso, A. \& Rogers, R. Differentially private histograms under continual observation: Streaming selection into the unknown. {\em International Conference On Artificial Intelligence And Statistics}. pp. 2397-2419 (2022)

\bibitem{knop2023counting}Knop, A. \& Steinke, T. Counting Distinct Elements Under Person-Level Differential Privacy. {\em 37th Conference On Neural Information Processing Systems (NeurIPS 2023)}. (2023)


\bibitem{bun2016concentrated}Bun, M. \& Steinke, T. Concentrated differential privacy: Simplifications, extensions, and lower bounds. {\em Theory Of Cryptography Conference}. pp. 635-658 (2016)

\bibitem{kalemaj2023counting}Kalemaj, I., Jain, P., Raskhodnikova, S., Sivakumar, S. \& Smith, A. Counting Distinct Elements in the Turnstile Model with Differential Privacy under Continual Observation. {\em Advances In Neural Information Processing Systems, NeurIPS 2023}. (2023)

\bibitem{epasto2023differentially}Epasto, A., Mao, J., Medina, A., Mirrokni, V., Vassilvitskii, S. \& Zhong, P. Differentially private continual releases of streaming frequency moment estimations. {\em ArXiv Preprint ArXiv:2301.05605}. (2023)

\bibitem{zhang2023differentially}Zhang, B., Doroshenko, V., Kairouz, P., Steinke, T., Thakurta, A., Ma, Z., Apte, H. \& Spacek, J. Differentially Private Stream Processing at Scale. {\em ArXiv Preprint ArXiv:2303.18086}. (2023)

% 3.4
\bibitem{koga2022privacy}Koga, T., Meehan, C. \& Chaudhuri, K. Privacy amplification by subsampling in time domain. {\em International Conference On Artificial Intelligence And Statistics}. pp. 4055-4069 (2022)

\bibitem{fan2013differentially}Fan, L. \& Xiong, L. Differentially private anomaly detection with a case study on epidemic outbreak detection. {\em 2013 IEEE 13th International Conference On Data Mining Workshops}. pp. 833-840 (2013)

\bibitem{li2015differentially}Li, H., Xiong, L., Jiang, X. \& Liu, J. Differentially private histogram publication for dynamic datasets: an adaptive sampling approach. {\em Proceedings Of The 24th ACM International On Conference On Information And Knowledge Management}. pp. 1001-1010 (2015)

\bibitem{wang2017secweb}Wang, Q., Lu, X., Zhang, Y., Wang, Z., Qin, Z. \& Ren, K. Secweb: Privacy-preserving web browsing monitoring with w-event differential privacy. {\em Security And Privacy In Communication Networks: 12th International Conference, SecureComm 2016, Guangzhou, China, October 10-12, 2016, Proceedings 12}. pp. 454-474 (2017)

%\bibitem{fioretto2019optstream}Fioretto, F. \& Van Hentenryck, P. Optstream: Releasing time series privately. {\em Journal Of Artificial Intelligence Research}. \textbf{65} pp. 423-456 (2019)

\bibitem{liang2020pufferfish}Liang, W., Chen, H., Liu, R., Wu, Y. \& Li, C. A pufferfish privacy mechanism for monitoring web browsing behavior under temporal correlations. {\em Computers \& Security}. \textbf{92} pp. 101754 (2020)

		
\bibitem{ding2022publishing}Ding, J., Ghosh, A., Sarkar, R. \& Gao, J. Publishing Asynchronous Event Times with Pufferfish Privacy. {\em 2022 18th International Conference On Distributed Computing In Sensor Systems (DCOSS)}. pp. 53-60 (2022)

\bibitem{erlingsson2014rappor}Erlingsson, Ú., Pihur, V. \& Korolova, A. Rappor: Randomized aggregatable privacy-preserving ordinal response. {\em Proceedings Of The 2014 ACM SIGSAC Conference On Computer And Communications Security}. pp. 1054-1067 (2014)

\bibitem{ding2017collecting}Ding, B., Kulkarni, J. \& Yekhanin, S. Collecting telemetry data privately. {\em Advances In Neural Information Processing Systems}. \textbf{30} (2017)

\bibitem{xue2022ddrm}Xue, Q., Ye, Q., Hu, H., Zhu, Y. \& Wang, J. DDRM: A continual frequency estimation mechanism with local differential privacy. {\em IEEE Transactions On Knowledge And Data Engineering}. (2022)

\bibitem{arcolezi2022frequency}Arcolezi, H., Pinzón, C., Palamidessi, C. \& Gambs, S. Frequency estimation of evolving data under local differential privacy. {\em ArXiv Preprint ArXiv:2210.00262}. (2022)

\bibitem{he2022ordinal}He, Y., Wang, F., Deng, X., Ni, J., Feng, J. \& Liu, S. Ordinal data stream collection with condensed local differential privacy. {\em 2022 IEEE 24th Int Conf On High Performance Computing \& Communications; 8th Int Conf On Data Science \& Systems; 20th Int Conf On Smart City; 8th Int Conf On Dependability In Sensor, Cloud \& Big Data Systems \& Application (HPCC/DSS/SmartCity/DependSys)}. pp. 562-569 (2022)

\bibitem{gursoy2019secure}Gursoy, M., Tamersoy, A., Truex, S., Wei, W. \& Liu, L. Secure and utility-aware data collection with condensed local differential privacy. {\em IEEE Transactions On Dependable And Secure Computing}. \textbf{18}, 2365-2378 (2019)

\bibitem{feng2023dpi}Feng, S., Mohammady, M., Wang, H., Li, X., Qin, Z. \& Hong, Y. DPI: Ensuring Strict Differential Privacy for Infinite Data Streaming. {\em ArXiv Preprint ArXiv:2312.04738}. (2023)

\bibitem{li2024local}Li, X., Liu, W., Lou, J., Hong, Y., Zhang, L., Qin, Z. \& Ren, K. Local differentially private heavy hitter detection in data streams with bounded memory. {\em Proceedings Of The ACM On Management Of Data}. \textbf{2}, 1-27 (2024)

\bibitem{gu2023differential}Gu, H., Plagemann, T., Benndorf, M., Goebel, V. \& Koldehofe, B. Differential Privacy for Protecting Private Patterns in Data Streams. {\em 2023 IEEE 39th International Conference On Data Engineering Workshops (ICDEW)}. pp. 118-124 (2023)




%%%%%%%%%%%%%%%%%%%%%%%%%%%%Sum/Mean Query
\bibitem{bolot2013private}Bolot, J., Fawaz, N., Muthukrishnan, S., Nikolov, A. \& Taft, N. Private decayed predicate sums on streams. {\em Proceedings Of The 16th International Conference On Database Theory}. pp. 284-295 (2013)

\bibitem{henzinger2024unifying}Henzinger, M., Upadhyay, J. \& Upadhyay, S. A unifying framework for differentially private sums under continual observation. {\em Proceedings Of The 2024 Annual ACM-SIAM Symposium On Discrete Algorithms (SODA)}. pp. 995-1018 (2024)

\bibitem{wang2021continuous}Wang, T., Chen, J., Zhang, Z., Su, D., Cheng, Y., Li, Z., Li, N. \& Jha, S. Continuous release of data streams under both centralized and local differential privacy. {\em Proceedings Of The 2021 ACM SIGSAC Conference On Computer And Communications Security}. pp. 1237-1253 (2021)

\bibitem{ye2021beyond}Ye, Q., Hu, H., Li, N., Meng, X., Zheng, H. \& Yan, H. Beyond value perturbation: Local differential privacy in the temporal setting. {\em IEEE INFOCOM 2021-IEEE Conference On Computer Communications}. pp. 1-10 (2021)

\bibitem{ye2023stateful}Ye, Q., Hu, H., Huang, K., Au, M. \& Xue, Q. Stateful switch: Optimized time series release with local differential privacy. {\em IEEE INFOCOM 2023-IEEE Conference On Computer Communications}. pp. 1-10 (2023)

\bibitem{perrier2018private}Perrier, V., Asghar, H. \& Kaafar, D. Private continual release of real-valued data streams. {\em ArXiv Preprint ArXiv:1811.03197}. (2018)

\bibitem{wang2020towards}Wang, Z., Liu, W., Pang, X., Ren, J., Liu, Z. \& Chen, Y. Towards pattern-aware privacy-preserving real-time data collection. {\em IEEE INFOCOM 2020-IEEE Conference On Computer Communications}. pp. 109-118 (2020)

\bibitem{kurt2022online}Kurt, M., Yılmaz, Y., Wang, X. \& Mosterman, P. Online privacy-preserving data-driven network anomaly detection. {\em IEEE Journal On Selected Areas In Communications}. \textbf{40}, 982-998 (2022)



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% time series release
\bibitem{ren2022ldp}Ren, X., Shi, L., Yu, W., Yang, S., Zhao, C. \& Xu, Z. LDP-IDS: Local differential privacy for infinite data streams. {\em Proceedings Of The 2022 International Conference On Management Of Data}. pp. 1064-1077 (2022)

\bibitem{wang2016rescuedp}Wang, Q., Zhang, Y., Lu, X., Wang, Z., Qin, Z. \& Ren, K. RescueDP: Real-time spatio-temporal crowd-sourced data publishing with differential privacy. {\em IEEE INFOCOM 2016-The 35th Annual IEEE International Conference On Computer Communications}. pp. 1-9 (2016)

\bibitem{zhang2017re}Zhang, J., Liang, X., Zhang, Z., He, S. \& Shi, Z. Re-DPoctor: Real-time health data releasing with w-day differential privacy. {\em GLOBECOM 2017-2017 IEEE Global Communications Conference}. pp. 1-6 (2017)


%5.1.2
\bibitem{ren2018textsf}Ren, X., Yu, C., Yu, W., Yang, S., Yang, X., McCann, J. \& Philip, S.  {LoPub} : high-dimensional crowdsourced data publication with local differential privacy. {\em IEEE Transactions On Information Forensics And Security}. \textbf{13}, 2151-2166 (2018)

\bibitem{wang2019locally}Wang, T., Yang, X., Ren, X., Yu, W. \& Yang, S. Locally private high-dimensional crowdsourced data release based on copula functions. {\em IEEE Transactions On Services Computing}. \textbf{15}, 778-792 (2019)

\bibitem{fioretto2019optstream}Fioretto, F. \& Van Hentenryck, P. Optstream: Releasing time series privately. {\em Journal Of Artificial Intelligence Research}. \textbf{65} pp. 423-456 (2019)

\bibitem{zhang2022differentially}Zhang, X., Khalili, M. \& Liu, M. Differentially private real-time release of sequential data. {\em ACM Transactions On Privacy And Security}. \textbf{26}, 1-29 (2022)

\bibitem{li2023locally}Li, X., Cao, Y. \& Yoshikawa, M. Locally Private Streaming Data Release with Shuffling and Subsampling. {\em 2023 IEEE 39th International Conference On Data Engineering Workshops (ICDEW)}. pp. 125-131 (2023)

\bibitem{bao2021cgm}Bao, E., Yang, Y., Xiao, X. \& Ding, B. CGM: an enhanced mechanism for streaming data collection with local differential privacy. {\em Proceedings Of The VLDB Endowment}. \textbf{14}, 2258-2270 (2021)

%\bibitem{he2022ordinal}He, Y., Wang, F., Deng, X., Ni, J., Feng, J. \& Liu, S. Ordinal data stream collection with condensed local differential privacy. {\em 2022 IEEE 24th Int Conf On High Performance Computing \& Communications; 8th Int Conf On Data Science \& Systems; 20th Int Conf On Smart City; 8th Int Conf On Dependability In Sensor, Cloud \& Big Data Systems \& Application (HPCC/DSS/SmartCity/DependSys)}. pp. 562-569 (2022)


% 5.2
\bibitem{xie2018differentially}Xie, L., Lin, K., Wang, S., Wang, F. \& Zhou, J. Differentially private generative adversarial network. {\em ArXiv Preprint ArXiv:1802.06739}. (2018)

\bibitem{jordon2018pate}Jordon, J., Yoon, J. \& Van Der Schaar, M. PATE-GAN: Generating synthetic data with differential privacy guarantees. {\em International Conference On Learning Representations}. (2018)


\bibitem{he2024online}He, Y., Vershynin, R. \& Zhu, Y. Online Differentially Private Synthetic Data Generation. {\em ArXiv Preprint ArXiv:2402.08012}. (2024)

\bibitem{bun2024continual}Bun, M., Gaboardi, M., Neunhoeffer, M. \& Zhang, W. Continual Release of Differentially Private Synthetic Data from Longitudinal Data Collections. {\em Proceedings Of The ACM On Management Of Data}. \textbf{2}, 1-26 (2024)

\bibitem{frigerio2019differentially}Frigerio, L., Oliveira, A., Gomez, L. \& Duverger, P. Differentially private generative adversarial networks for time series, continuous, and discrete open data. {\em ICT Systems Security And Privacy Protection: 34th IFIP TC 11 International Conference, SEC 2019, Lisbon, Portugal, June 25-27, 2019, Proceedings 34}. pp. 151-164 (2019)

\bibitem{wang2020part}Wang, S., Rudolph, C., Nepal, S., Grobler, M. \& Chen, S. PART-GAN: Privacy-preserving time-series sharing. {\em Artificial Neural Networks And Machine Learning–ICANN 2020: 29th International Conference On Artificial Neural Networks, Bratislava, Slovakia, September 15–18, 2020, Proceedings, Part I 29}. pp. 578-593 (2020)

\bibitem{torfi2022differentially}Torfi, A., Fox, E. \& Reddy, C. Differentially private synthetic medical data generation using convolutional GANs. {\em Information Sciences}. \textbf{586} pp. 485-500 (2022)

\bibitem{lamp2024glucosynth}Lamp, J., Derdzinski, M., Hannemann, C., Linden, J., Feng, L., Wang, T. \& Evans, D. GlucoSynth: Generating Differentially-Private Synthetic Glucose Traces. {\em Advances In Neural Information Processing Systems}. \textbf{36} (2024)

\bibitem{mao2023utility} Mao, Y., Ye, Q., Wang, Q. \& Hu, H. Utility-Aware Time Series Data Release with Anomalies under TLDP. {\em IEEE Transactions On Mobile Computing}. (2023)





%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% trajectory
\bibitem{bordenabe2014optimal}Bordenabe, N., Chatzikokolakis, K. \& Palamidessi, C. Optimal geo-indistinguishable mechanisms for location privacy. {\em Proceedings Of The 2014 ACM SIGSAC Conference On Computer And Communications Security}. pp. 251-262 (2014)

\bibitem{weggenmann2021differential}Weggenmann, B. \& Kerschbaum, F. Differential privacy for directional data. {\em Proceedings Of The 2021 ACM SIGSAC Conference On Computer And Communications Security}. pp. 1205-1222 (2021)

\bibitem{zhao2022geo}Zhao, Y., Yuan, D., Du, J. \& Chen, J. Geo-ellipse-indistinguishability: community-aware location privacy protection for directional distribution. {\em IEEE Transactions On Knowledge And Data Engineering}. (2022)

\bibitem{liang2023concentrated}Liang, Y. \& Yi, K. Concentrated geo-privacy. {\em Proceedings Of The 2023 ACM SIGSAC Conference On Computer And Communications Security}. pp. 1934-1948 (2023)

\bibitem{zhao2023vector}Zhao, Y. \& Chen, J. Vector-indistinguishability: location dependency based privacy protection for successive location data. {\em IEEE Transactions On Computers}. (2023)

\bibitem{yu2017dynamic}Yu, L., Liu, L. \& Pu, C. Dynamic Differential Location Privacy with Personalized Error Bounds.. {\em NDSS}. (2017)

\bibitem{cao2019priste}Cao, Y., Xiao, Y., Xiong, L. \& Bai, L. PriSTE: from location privacy to spatiotemporal event privacy. {\em 2019 IEEE 35th International Conference On Data Engineering (ICDE)}. pp. 1606-1609 (2019)

\bibitem{niu2020eclipse}Niu, B., Chen, Y., Wang, Z., Li, F., Wang, B. \& Li, H. Eclipse: Preserving differential location privacy against long-term observation attacks. {\em IEEE Transactions On Mobile Computing}. \textbf{21}, 125-138 (2020)

\bibitem{qiu2020location}Qiu, C., Squicciarini, A., Pang, C., Wang, N. \& Wu, B. Location privacy protection in vehicle-based spatial crowdsourcing via geo-indistinguishability. {\em IEEE Transactions On Mobile Computing}. \textbf{21}, 2436-2450 (2020)

\bibitem{haydari2022differentially}Haydari, A., Chuah, C., Zhang, M., Macfarlane, J. \& Peisert, S. Differentially private map matching for mobility trajectories. {\em Proceedings Of The 38th Annual Computer Security Applications Conference}. pp. 293-303 (2022)



% 6.2
\bibitem{xiao2015protecting}Xiao, Y. \& Xiong, L. Protecting locations with differential privacy under temporal correlations. {\em Proceedings Of The 22nd ACM SIGSAC Conference On Computer And Communications Security}. pp. 1298-1309 (2015)

\bibitem{liu2019protecting}Liu, B., Zhu, T., Zhou, W., Wang, K., Zhou, H. \& Ding, M. Protecting privacy-sensitive locations in trajectories with correlated positions. {\em 2019 IEEE Global Communications Conference (GLOBECOM)}. pp. 1-6 (2019)

\bibitem{ma2019real}Ma, Z., Zhang, T., Liu, X., Li, X. \& Ren, K. Real-time privacy-preserving data release over vehicle trajectory. {\em IEEE Transactions On Vehicular Technology}. \textbf{68}, 8091-8102 (2019)

\bibitem{cao2023differentially}Cao, X., Cao, Y., Pappachan, P., Nakamura, A. \& Yoshikawa, M. Differentially Private Streaming Data Release Under Temporal Correlations via Post-processing. {\em IFIP Annual Conference On Data And Applications Security And Privacy}. pp. 184-200 (2023)

\bibitem{ahuja2023neural}Ahuja, R., Zeighami, S., Ghinita, G. \& Shahabi, C. A Neural Approach to Spatio-Temporal Data Release with User-Level Differential Privacy. {\em Proceedings Of The ACM On Management Of Data}. \textbf{1}, 1-25 (2023)

% 6.3
\bibitem{wang2022srr}Wang, H., Hong, H., Xiong, L., Qin, Z. \& Hong, Y. L-srr: Local differential privacy for location-based services with staircase randomized response. {\em Proceedings Of The 2022 ACM SIGSAC Conference On Computer And Communications Security}. pp. 2809-2823 (2022)

\bibitem{cunningham2021real}Cunningham, T., Cormode, G., Ferhatosmanoglu, H. \& Srivastava, D. Real-world trajectory sharing with local differential privacy. {\em ArXiv Preprint ArXiv:2108.02084}. (2021)

\bibitem{zhang2023trajectory}Zhang, Y., Ye, Q., Chen, R., Hu, H. \& Han, Q. Trajectory data collection with local differential privacy. {\em ArXiv Preprint ArXiv:2307.09339}. (2023)

\bibitem{gursoy2018differentially}Gursoy, M., Liu, L., Truex, S. \& Yu, L. Differentially private and utility preserving publication of trajectory data. {\em IEEE Transactions On Mobile Computing}. \textbf{18}, 2315-2329 (2018)

\bibitem{gursoy2018utility}Gursoy, M., Liu, L., Truex, S., Yu, L. \& Wei, W. Utility-aware synthesis of differentially private and attack-resilient location traces. {\em Proceedings Of The 2018 ACM SIGSAC Conference On Computer And Communications Security}. pp. 196-211 (2018)

\bibitem{du2023ldptrace}Du, Y., Hu, Y., Zhang, Z., Fang, Z., Chen, L., Zheng, B. \& Gao, Y. Ldptrace: Locally differentially private trajectory synthesis. {\em Proceedings Of The VLDB Endowment}. \textbf{16}, 1897-1909 (2023)

\bibitem{hu2024real}Hu, Y., Du, Y., Zhang, Z., Fang, Z., Chen, L., Zheng, K. \& Gao, Y. Real-Time Trajectory Synthesis with Local Differential Privacy. {\em ArXiv Preprint ArXiv:2404.11450}. (2024)

\bibitem{sun2023synthesizing}Sun, X., Ye, Q., Hu, H., Wang, Y., Huang, K., Wo, T. \& Xu, J. Synthesizing realistic trajectory data with differential privacy. {\em IEEE Transactions On Intelligent Transportation Systems}. (2023)





\end{small}
\end{thebibliography}