\documentclass[11pt]{article}
%\documentclass[11pt,dvipdfm]{article} 

\usepackage{deauthor,times,graphicx}
%\usepackage[hidelinks]{hyperref}
\usepackage{tcolorbox}
%\graphicspath{{istvan/}} 
\usepackage{xpatch}
\usepackage{xspace}
\usepackage{multirow}


\makeatletter

\makeatletter

\newcommand{\hi}[1]{\noindent {\bf #1}}

\newcommand{\lgl}[1]{{\textcolor{blue}{{#1}}}}

\newcommand{\oursys}{\textsf{XuanYuan}\xspace}

\begin{document}

%\pagestyle{plain}
%\pagenumbering{arabic}


\setcounter{figure}{0}  

% ****************** AUTHORS **************************************

\title{\oursys: An AI-Native Database}

%\author{Zsolt Istv\'{a}n\\ \small IMDEA Software Institute, Madrid, Spain\\  \small \{first.lastname@imdea.org\}}
\author{Guoliang Li, Xuanhe Zhou, Sihao Li\\ 
\small Department of Computer Science,Tsinghua University, Beijing, China\\
\small Gauss Database Group, Huawei Company\\  
\small liguoliang@tsinghua.edu.cn}

\maketitle

\input{submissions/ainative/sections/abstract}
\input{submissions/ainative/sections/introduction}

%\input{sections/background}
%\input{submissions/ainative/sections/motivation}
\input{submissions/ainative/sections/work}
\input{submissions/ainative/sections/challenge}
\input{submissions/ainative/sections/conclusions}
%\input{sections/acknowledgement}
%\input{sections/remove}



\begin{thebibliography}{10}

\bibitem{DBLP:conf/sigmod/AkenPGZ17}
D.~V. Aken, A.~Pavlo, G.~J. Gordon, and B.~Zhang.
\newblock Automatic database management system tuning through large-scale
  machine learning.
\newblock In {\em SIGMOD}, pages 1009--1024, 2017.

\bibitem{DBLP:books/daglib/0006734}
C.~J. Date.
\newblock {\em An introduction to database systems {(7.} ed.)}.
\newblock Addison-Wesley-Longman, 2000.

\bibitem{DBLP:journals/jidm/FigueiredoBM10}
G.~Figueiredo, V.~Braganholo, and M.~Mattoso.
\newblock Processing queries over distributed {XML} databases.
\newblock {\em {JIDM}}, 1(3):455--470, 2010.

\bibitem{DBLP:journals/kais/GaniSSH16}
A.~Gani, A.~Siddiqa, S.~Shamshirband, and F.~H. Nasaruddin.
\newblock A survey on indexing techniques for big data: taxonomy and
  performance evaluation.
\newblock {\em Knowl. Inf. Syst.}, 46(2):241--284, 2016.

\bibitem{DBLP:conf/cidr/IdreosDQAHRLJGL19}
S.~Idreos, N.~Dayan, W.~Qin, M.~Akmanalp, S.~Hilgard, A.~Ross, J.~Lennon,
  V.~Jain, H.~Gupta, D.~Li, and Z.~Zhu.
\newblock Design continuums and the path toward self-designing key-value stores
  that know and learn.
\newblock In {\em CIDR}, 2019.

\bibitem{DBLP:conf/cidr/KipfKRLBK19}
A.~Kipf, T.~Kipf, B.~Radke, V.~Leis, P.~A. Boncz, and A.~Kemper.
\newblock Learned cardinalities: Estimating correlated joins with deep
  learning.
\newblock In {\em CIDR}, 2019.

\bibitem{DBLP:conf/sigmod/KraskaBCDP18}
T.~Kraska, A.~Beutel, E.~H. Chi, J.~Dean, and N.~Polyzotis.
\newblock The case for learned index structures.
\newblock In {\em SIGMOD}, pages 489--504, 2018.

\bibitem{DBLP:journals/corr/abs-1808-03196}
S.~Krishnan, Z.~Yang, K.~Goldberg, J.~M. Hellerstein, and I.~Stoica.
\newblock Learning to optimize join queries with deep reinforcement learning.
\newblock {\em CoRR}, abs/1808.03196, 2018.

\bibitem{DBLP:conf/vldb/qtune19}
G.~Li, X.~Zhou, B.~Gao, and S.~Li.
\newblock Qtune: A query-aware database tuning system with deep reinforcement
  learning.
\newblock In {\em VLDB}, 2019.

\bibitem{DBLP:journals/corr/abs-1903-01363}
X.~Liang, A.~J. Elmore, and S.~Krishnan.
\newblock Opportunistic view materialization with deep reinforcement learning.
\newblock {\em CoRR}, abs/1903.01363, 2019.

\bibitem{DBLP:conf/sigmod/MaAHMPG18}
L.~Ma, D.~V. Aken, A.~Hefny, G.~Mezerhane, A.~Pavlo, and G.~J. Gordon.
\newblock Query-based workload forecasting for self-driving database management
  systems.
\newblock In {\em Proceedings of the 2018 International Conference on
  Management of Data, {SIGMOD} Conference 2018, Houston, TX, USA, June 10-15,
  2018}, pages 631--645, 2018.

\bibitem{DBLP:conf/sigmod/MarcusP18}
R.~Marcus and O.~Papaemmanouil.
\newblock Deep reinforcement learning for join order enumeration.
\newblock In {\em Proceedings of the First International Workshop on Exploiting
  Artificial Intelligence Techniques for Data Management, aiDM@SIGMOD 2018,
  Houston, TX, USA, June 10, 2018}, pages 3:1--3:4, 2018.

\bibitem{DBLP:journals/corr/abs-1802-00884}
M.~Mitzenmacher.
\newblock A model for learned bloom filters and related structures.
\newblock {\em CoRR}, abs/1802.00884, 2018.

\bibitem{DBLP:conf/sigmod/OrtizBGK18}
J.~Ortiz, M.~Balazinska, J.~Gehrke, and S.~S. Keerthi.
\newblock Learning state representations for query optimization with deep
  reinforcement learning.
\newblock In {\em SIGMOD}, pages 4:1--4:4, 2018.

\bibitem{DBLP:conf/hais/PedrozoNR18}
W.~G. Pedrozo, J.~C. Nievola, and D.~C. Ribeiro.
\newblock An adaptive approach for index tuning with learning classifier
  systems on hybrid storage environments.
\newblock In {\em HAIS}, pages 716--729, 2018.

\bibitem{DBLP:conf/aaai/HasseltGS16}
H.~van Hasselt, A.~Guez, and D.~Silver.
\newblock Deep reinforcement learning with double q-learning.
\newblock In {\em AAAI}, pages 2094--2100, 2016.

\bibitem{DBLP:conf/mm/WangCDGOTW15}
W.~Wang, G.~Chen, T.~T.~A. Dinh, J.~Gao, B.~C. Ooi, K.~Tan, and S.~Wang.
\newblock {SINGA:} putting deep learning in the hands of multimedia users.
\newblock In {\em SIGMM}, pages 25--34, 2015.

\bibitem{DBLP:journals/sigmod/0059Z0JOT16}
W.~Wang, M.~Zhang, G.~Chen, H.~V. Jagadish, B.~C. Ooi, and K.~Tan.
\newblock Database meets deep learning: Challenges and opportunities.
\newblock {\em {SIGMOD} Record}, 45(2):17--22, 2016.

\bibitem{DBLP:conf/aaai/YuZWY17}
L.~Yu, W.~Zhang, J.~Wang, and Y.~Yu.
\newblock Seqgan: Sequence generative adversarial nets with policy gradient.
\newblock In {\em AAAI}, pages 2852--2858, 2017.

\bibitem{DBLP:conf/sigmod/cdbtune19}
J.~Zhang, Y.~Liu, K.~Zhou, and G.~Li.
\newblock An end-to-end automatic cloud database tuning system using deep
  reinforcement learning.
\newblock In {\em SIGMOD}, 2019.

\bibitem{DBLP:journals/corr/abs-1902-05687}
Z.~Zhou, J.~Liang, Y.~Song, L.~Yu, H.~Wang, W.~Zhang, Y.~Yu, and Z.~Zhang.
\newblock Lipschitz generative adversarial nets.
\newblock {\em CoRR}, abs/1902.05687, 2019.

\bibitem{DBLP:journals/corr/abs-1902-10680}
S.~Zong, A.~Ritter, G.~Mueller, and E.~Wright.
\newblock Analyzing the perceived severity of cybersecurity threats reported on
  social media.
\newblock {\em CoRR}, abs/1902.10680, 2019.

\end{thebibliography}


%\clearpage
%\balance
%{%\scriptsize
%\bibliographystyle{abbrv}
%\bibliography{submissions/ainative/DA}  

%}

%\input{sections/removed}

%\input{sections/appendix}

\end{document}
