%\documentclass[11pt,dvipdfm]{article}
%\usepackage[utf8]{inputenc}

%\title{The 2019 IEEE TCDE Awards}
%\author{2019 IEEE TCDE Awards Committee}
%\date{September 2019}

%\begin{document}
%\maketitle

%\vspace{-0.1in}

The IEEE TCDE (Technical Committee of Data Engineering) has established several highly prestigious awards to encourage innovative long term contributions to the field of data engineering. It is our pleasure to present letters from the 2019 award winners in this issue.

%\begin{itemize}

%\item 
\  
\\
{\bf Rising Star Award.} The IEEE TCDE Rising Star Award is based on an individual's whole body of work in the first five years after the PhD. The award aims to promote current database researchers as they create their career. The 2019 IEEE TCDE Rising Star Award goes to Viktor Leis from the Technical University of Munich
for \emph{contributions to main-memory indexing and database architectures for NVM}.

%\item 
\  
\\
{\bf Impact Award.} The IEEE TCDE Impact Award recognizes database researchers whose research resulted in impact beyond the data engineering field, impact beyond research to industrial practice, and/or impact resulting in expansion of the data engineering field itself. The 2019 IEEE TCDE Impact Award goes to 
Christian Jensen from Aalborg University for \emph{contributions to spatial, temporal, and spatio-temporal data management}.

%\item 
\  
\\
{\bf Service Award.} The IEEE TCDE Service Award recognizes an individual who has contributed significantly to ICDE, TCDE, and the data engineering community in general. The 2019 IEEE TCDE Service Award goes to David Lomet from Microsoft for 
\emph{leadership as the Editor-in-Chief of the Data Engineering Bulletin for over 25 years}.\\
%\end{itemize}
\indent
\ 
\\
Congratulations again to the winners, and we hope you will enjoy reading their letters as much as we did.

%\newline
\vspace{0.1in}

\begin{flushright}
\indent {\bf The 2019 Awards Committee} \\
%\vspace{ex} \\
%\vspace{0.1in} \\
\indent Anastasia Ailamaki\\
\indent Paolo Atzeni\\
\indent Michael Carey \\
\indent Xin Luna Dong \\
\indent Johannes Gehrke (chair) \\
\indent Sunita Sarawagi
\end{flushright}
\end{document}
