\documentclass[11pt]{article}
% guidelines at http://tab.computer.org/tcde/bull_author.html
\usepackage{deauthor,times,graphicx}
%\graphicspath{{authorname/}}

%\usepackage[dvipsnames,svgnames]{xcolor}
\usepackage{tikz}
\usepackage{amssymb, framed}
\usepackage{rotating}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{tikz}
\usetikzlibrary{trees,shapes,snakes,patterns}
% % % --------------------------------------- % % %
% % % Macros to write comments for internal usage % % %
% % % --------------------------------------- % % %

\newcommand{\red}[1]{\textcolor{red}{#1}}

\begin{document}
\title{Platform Design for Crowdsourcing and Future of Work}
%The future of Crowdsourcing Platforms: Ecosystems and Interoperability}

\author{David\, Gross-Amblard\\
 University of Rennes, France\\
\texttt{{\footnotesize dga@irisa.fr}}
\and
Atsuyuki Morishima\\
University of Tsukuba\\
\texttt{{\footnotesize mori@slis.tsukuba.ac.jp}}
\and
Saravanan Thirumuruganathan\\
QCRI, HBKU\\
\texttt{{\footnotesize sthirumuruganathan@hbku.edu.qa}}
\and
Marion\, Tommasi\\
University of Lille and INRIA\\
\texttt{{\footnotesize marion.tommasi@inria.fr}}
\and
Ko\, Yoshida\\
CrowdWorks\\
\texttt{{\footnotesize yoshida@crowdworks.co.jp}}
}
\maketitle

\newcommand{\scream}[1]{\textbf{***#1***}}

% -------------------------------------------------------- %

\input{submissions/atsuyuki/abstract}
\input{submissions/atsuyuki/introduction}
\input{submissions/atsuyuki/motivation}
\input{submissions/atsuyuki/platformDesign}
\input{submissions/atsuyuki/platformInteroperability}
\input{submissions/atsuyuki/conclusion}
\vspace{-.6cm}
\enlargethispage{1cm}
\bibliographystyle{abbrv}

\begin{thebibliography}{10}

\bibitem{basu2015task}
S.~Basu~Roy, I.~Lykourentzou, S.~Thirumuruganathan, S.~Amer-Yahia, and G.~Das.
\newblock Task assignment optimization in knowledge-intensive crowdsourcing.
\newblock {\em The VLDB Journal—The International Journal on Very Large Data
	Bases}, 24(4):467--491, 2015.

\bibitem{brawley2016work}
A.~M. Brawley and C.~L. Pury.
\newblock Work experiences on mturk: Job satisfaction, turnover, and
information sharing.
\newblock {\em Computers in Human Behavior}, 54:531--546, 2016.

\bibitem{doan2011crowdsourcing}
A.~Doan, R.~Ramakrishnan, and A.~Y. Halevy.
\newblock Crowdsourcing systems on the world-wide web.
\newblock {\em Communications of the ACM}, 54(4):86--96, 2011.

\bibitem{ho2012online}
C.-J. Ho and J.~W. Vaughan.
\newblock Online task assignment in crowdsourcing markets.
\newblock In {\em Twenty-Sixth AAAI Conference on Artificial Intelligence},
2012.

\bibitem{ikeda2016collaborative}
K.~Ikeda, A.~Morishima, H.~Rahman, S.~B. Roy, S.~Thirumuruganathan,
S.~Amer-Yahia, and G.~Das.
\newblock Collaborative crowdsourcing with crowd4u.
\newblock {\em Proceedings of the VLDB Endowment}, 9(13):1497--1500, 2016.

\bibitem{irani2013turkopticon}
L.~C. Irani and M.~Silberman.
\newblock Turkopticon: Interrupting worker invisibility in amazon mechanical
turk.
\newblock In {\em Proceedings of the SIGCHI conference on human factors in
	computing systems}, pages 611--620. ACM, 2013.

\bibitem{DBLP:conf/www/MavridisGM16}
P.~Mavridis, D.~Gross{-}Amblard, and Z.~Mikl{\'{o}}s.
\newblock Using hierarchical skills for optimized task assignment in
knowledge-intensive crowdsourcing.
\newblock In {\em Proceedings of the 25th International Conference on World
	Wide Web, {WWW} 2016, Montreal, Canada, April 11 - 15, 2016}, pages 843--853,
2016.

\bibitem{mcfeely2018workplace}
S.~McFeely and R.~Pendell.
\newblock What workplace leaders can learn from the real gig economy. gallup,
2018.

\bibitem{morishima2014crowd4u}
A.~Morishima, S.~Amer-Yahia, and S.~B. Roy.
\newblock Crowd4u: An initiative for constructing an open academic
crowdsourcing network.
\newblock In {\em Second AAAI conference on human computation and
	crowdsourcing}, 2014.

\bibitem{morishima2012cylog}
A.~Morishima, N.~Shinagawa, T.~Mitsuishi, H.~Aoki, and S.~Fukusumi.
\newblock Cylog/crowd4u: A declarative platform for complex data-centric
crowdsourcing.
\newblock {\em Proceedings of the VLDB Endowment}, 5(12):1918--1921, 2012.

\bibitem{rahman2015task}
H.~Rahman, S.~B. Roy, S.~Thirumuruganathan, S.~Amer-Yahia, and G.~Das.
\newblock Task assignment optimization in collaborative crowdsourcing.
\newblock In {\em 2015 IEEE International Conference on Data Mining}, pages
949--954. IEEE, 2015.

\bibitem{salehi2015we}
N.~Salehi, L.~C. Irani, M.~S. Bernstein, A.~Alkhatib, E.~Ogbe, K.~Milland,
et~al.
\newblock We are dynamo: Overcoming stalling and friction in collective action
for crowd workers.
\newblock In {\em Proceedings of the 33rd annual ACM conference on human
	factors in computing systems}, pages 1621--1630. ACM, 2015.

\bibitem{DBLP:books/daglib/0031391}
D.~Schall.
\newblock {\em Service-Oriented Crowdsourcing - Architecture, Protocols and
	Algorithms}.
\newblock Springer Briefs in Computer Science. Springer, 2012.

\bibitem{DBLP:journals/www/SchallSP14}
D.~Schall, B.~Satzger, and H.~Psaier.
\newblock Crowdsourcing tasks to social networks in bpel4people.
\newblock {\em World Wide Web}, 17(1):1--32, 2014.

\end{thebibliography}

\end{document}
