\documentclass[11pt]{article} 

\usepackage{deauthor,times,graphicx}
%\usepackage{url}
\usepackage{hyperref}

\begin{document}
Around the time we published our last issue in March, the nation went
into a lockdown. Life in the last 3 months has been unprecedented in
many ways. As governments around the world scrambled to fight
coronavirus, people in the scientific community, especially those on
the frontline -- doctors, healthcare professionals, medical staff and
researchers -- made heroic efforts and sacrifices to curb the pandemic
and save lives. The data management and data science communities also
sprang to action immediately. Globally, it is the first time that data
driven approaches are being used at such a large scale toward solving
a common problem. Under this backdrop, in this special issue of the
Data Engineering Bulletin edited by Joseph Gonzalez, we feature 9
papers on the topic of {\it digital contact tracing}, a technique that
may prove crucial in the fight against Covid-19.

This issue also features two opinion pieces. Divyakant Agrawal and Amr
El Abbadi's wake-up call on managing data in an untrusted environment
takes us to the fascinating world of cryptocurrencies and
blockchains. It shows what the database community, which was
responsible for creating and perfecting transaction management and
distributed systems, can learn from the blockchain approach when it
comes to handling untrusted behaviours from the underlying
infrastructure. The second opinion piece, written by Jeffrey
D. Ullman, addresses a question on the mind of every data management
person: What is our role in the machine learning and AI revolution?
Have we missed the boat again and become irrelevant? Ullman's
perspective, illustrated by his remake of the well known Conway Venn
Diagram that illustrates the relationship between computer science,
mathematics \& statistics, and domain knowledge is incisive,
thought-provoking, and entertaining at the same time.
\end{document}

