%Open Calls for Nominations 

 

The IEEE Technical Community on Data Engineering (TCDE) Nominations Committee requests nominations for qualified individuals to fill the TCDE Chair position for the 2023-2024 term.

 

Self-nominations are allowed. Nominations should be submitted to the Nominations Committee chair Erich Neuhold erich.neuhold@univie.ac.at with copies to Amr El Abbadi <amr@cs.ucsb.edu> and Farshad Firouzi <farshad.firouzi@duke.edu>.

 

The Nominations \& Appointments Committee requests the following information regarding each candidate for consideration: 

\begin{enumerate}
\item Candidate's name and contact information (as it should appear on all election materials), Business Title/Position, Business Name, Business Address, Preferred Phone, Email address, and a short Bio not exceeding 250 words. 

\item A brief statement, not to exceed 250 words, on the candidate’s prior achievements for the benefit of IEEE CS and IEEE TCDE.  

\item A statement of candidacy (not to exceed 250 words) explaining the candidate’s plans for using their office to strengthen IEEE TCDE.
\end{enumerate}

 

Duties from the Technical and Confernce Activities Board Handbook:

     The Chair is the leader for TC vitality, and is responsible for building a strong organization and officer structure in support of the TC’s mission. The chair is responsible for making sure T\&C Activities Board policy is carried out in relation to TC activities, and is the vital communication link between the TC and the T\&C Activities Board. It is the responsibility of the Chair to see that the TC operates within T\&C Activities Board guidelines, and that any deviations from T\&C Activities Board policy are brought to the attention of the T\&C Activities Board. Roles specific to the technical committee of interest should be discussed with the current or previous chair, as each TC is different. The Chair is accountable to both TC members and the T\&C Activities Board.

    The TC Chair has ultimate authority and responsibility for the conduct of a TC. While duties may be delegated to other parties, typically a Vice Chair or Executive Committee members, it is the Chair that bears responsibility for the successful operation of the TC. Only the Vice-President for Technical and Conference Activities or the CS President may overturn the decision of a Chair.
