
\documentclass[11pt]{article}

\usepackage{deauthor}
\usepackage{times}
\usepackage{authblk}
\usepackage{graphicx}

\usepackage{float,color}
\usepackage{makecell}
\usepackage{comment}
%\usepackage[normalem]{ulem}
\usepackage{algorithmic}
\usepackage{algorithm}
\usepackage{array}
\usepackage{xurl}
\usepackage{subfig}
\usepackage{caption}
\usepackage{enumitem,kantlipsum}
\usepackage{placeins}
\usepackage{amsmath}
\usepackage{diagbox}
\usepackage{chngpage}
\usepackage{subfig}


\newcommand{\gchecker}{\textsc{KompaRe}}
\newtheorem{pro-stat}{Problem Definition}
\newcommand{\hide}[1]{}
\newcommand{\hh}[1]{{\small\color{red}{\bf hh: #1}}}
\newcommand{\lliu}[1]{{\small\color{blue}{\bf lihui: #1}}}
\newcommand{\heng}[1]{{\small\color{red}{\bf heng: #1}}}
\newcommand{\bx}[1]{{\small\color{green}{\bf Boxin: #1}}}
\newcommand{\mkclean}{
	\renewcommand{\hh}[1]{}
	\renewcommand{\bx}[1]{}
	\renewcommand{\heng}[1]{}
	\renewcommand{\lliu}[1]{}
}



\mkclean
\begin{document}


\title{Knowledge Graph Comparative Reasoning for Fact Checking: Problem Definition and Algorithms}



% \author{Junchao Chen,\quad Suyash Gupta$^{\dagger}$,\quad Sajjad Rahnama,\quad Mohammad Sadoghi\\
%     \textit{Moka Blox LLC} \\
%     Exploratory Systems Lab \\
%     University of California, Davis \\
%     $^{\dagger}$University of California, Berkeley
% }


\author{Lihui Liu*, Ruining Zhao*,  Boxin Du$\ddagger$\footnote{The publication was written prior to the employee joining Amazon.}, Yi Ren Fung*, Heng Ji*, Jiejun Xu$\dagger$, Hanghang Tong* \\
  *Department of Computer Science, University of Illinois at Urbana Champaign \\
  $\dagger$HRL Laboratories, LLC., jxu@hrl.com \\
  $\ddagger$Amazon, boxin@amazon.com\\
  %\institution{$\dagger$jxu@hrl.com}
  *{lihuil2, ruining9, yifung2, hengji, htong}@illinois.edu
}


%


\maketitle

\begin{abstract}
\input{submissions/logical-queries-uiuc/000abs.tex}
\end{abstract}



\section{Introduction}
\input{submissions/logical-queries-uiuc/001intro.tex}

%\section{Problem Definition}

%\input{002probDef.tex}

%\subsection{Knowledge Graph Search}
%\input{002probDef01match.tex}
%\subsection{Knowledge Graph Reasoning}
%\input{002probDef02Reason.tex}

\section{Problem Definition}\label{problem_definition}
\input{submissions/logical-queries-uiuc/002sysOverview.tex}

\section{Knowledge Segment Extraction}\label{ks_extractt}

%
\input{submissions/logical-queries-uiuc/003basics.tex}
%\input{004search.tex}

\section{Comparative Reasoning}\label{methods}
\input{submissions/logical-queries-uiuc/004comparison}

\section{Experimental Results} \label{experiments}
\input{submissions/logical-queries-uiuc/006experiment.tex}

\section{Related Work}\label{related-work}

\input{submissions/logical-queries-uiuc/007relwork.tex}

%\vspace{-0.9\baselineskip}
\section{Conclusions}\label{conclusion}

\input{submissions/logical-queries-uiuc/009conclusion.tex}

%\input{revision}




%\bibliographystyle{plain}
%\bibliography{submissions/logical-queries-uiuc/008reference}

%%
%% If your work has an appendix, this is the place to put it.

\begin{thebibliography}{10}

\bibitem{transE}
B.~Antoine, U.~Nicolas, G.~Alberto, W~Jason, and Y.~Oksana.
\newblock Translating embeddings for modeling multi-relational data.
\newblock In {\em NIPS '13}, NIPS '13, pages 2787--2795.

\bibitem{KL}
Giovanni~Luca Ciampaglia, Prashant Shiralkar, and Rocha.
\newblock Computational fact checking from knowledge networks.
\newblock 2015.

\bibitem{ciampaglia2015computational}
Giovanni~Luca Ciampaglia, Prashant Shiralkar, Luis~M Rocha, Johan Bollen,
  Filippo Menczer, and Alessandro Flammini.
\newblock Computational fact checking from knowledge networks.
\newblock {\em PloS one}, 10(6):e0128193, 2015.

\bibitem{Cui2019SAMES}
Limeng Cui, Suhang Wang, and Dongwon Lee.
\newblock Same : Sentiment-aware multi-modal embedding for detecting fake news.
\newblock 2019.

\bibitem{bert}
Jacob Devlin, Ming-Wei Chang, Kenton Lee, and Kristina Toutanova.
\newblock Bert: Pre-training of deep bidirectional transformers for language
  understanding, 2018.

\bibitem{sysvester}
Boxin Du, Lihui Liu, and Hanghang Tong.
\newblock Sylvester tensor equation for multi-way association.
\newblock In {\em Proceedings of the 27th ACM SIGKDD Conference on Knowledge
  Discovery and Data Mining}, KDD '21, page 311–321, New York, NY, USA, 2021.
  Association for Computing Machinery.

\bibitem{Faloutsos2004}
C.~Faloutsos, K.~McCurley, and A.~Tomkins.
\newblock Fast discovery of connection subgraphs.
\newblock In {\em KDD '04}, pages 118--127, New York, NY, USA, 2004. ACM.

\bibitem{Freitas}
S.~{Freitas}, N.~{Cao}, Y.~{Xia}, D.~H.~P. {Chau}, and H.~{Tong}.
\newblock Local partition in rich graphs.
\newblock BigData '19, pages 1001--1008, Dec 2018.

\bibitem{knowledge-path}
C.~Giovanni, S.~Prashant, R.~Luis, B.~Johan, M.~Filippo, and F.~Alessandro.
\newblock Computational fact checking from knowledge networks.
\newblock {\em PloS one}, 10, 01 2015.

\bibitem{GQBE}
N.~{Jayaram}, A.~{Khan}, C.~{Li}, X.~{Yan}, and R.~{Elmasri}.
\newblock Querying knowledge graphs by example entity tuples.
\newblock 27(10):2797--2811, Oct 2015.

\bibitem{Koren2006MEP}
Y.~Koren, S.~North, and C.~Volinsky.
\newblock Measuring and extracting proximity in networks.
\newblock KDD '06, pages 245--255, New York, NY, USA, 2006. ACM.

\bibitem{entity-predicate}
H.~William L., B.~Payal, Z.~Marinka, J.~Dan, and L.~Jure.
\newblock Embedding logical queries on knowledge graphs.
\newblock NIPS’18, page 2030–2041, Red Hook, NY, USA, 2018.

\bibitem{williamCohen}
Ni~L, Tom M, and William~W. C.
\newblock Random walk inference and learning in a large scale knowledge base.
\newblock EMNLP ’11, USA, 2011.

\bibitem{jaccard}
David Liben-Nowell and Jon Kleinberg.
\newblock The link prediction problem for social networks.
\newblock CIKM '03.

\bibitem{lin2018fact}
Peng Lin, Qi~Song, and Yinghui Wu.
\newblock Fact checking in knowledge graphs with ontological subgraph patterns.
\newblock {\em Data Science and Engineering}, 3(4):341--358, 2018.

\bibitem{Lin2015TransR}
Y.~Lin, Z.~Liu, M.~Sun, Y.~Liu, and X.~Zhu.
\newblock Learning entity and relation embeddings for knowledge graph
  completion.
\newblock AAAI'15. AAAI Press, 2015.

\bibitem{lihui}
L.~{Liu}, B.~{Du}, and H.~{Tong}.
\newblock Gfinder: Approximate attributed subgraph matching.
\newblock BigData '19, Dec 2019.

\bibitem{kompare}
Lihui Liu, Boxin Du, Yi~Ren Fung, Heng Ji, Jiejun Xu, and Hanghang Tong.
\newblock Kompare: A knowledge graph comparative reasoning system.
\newblock In {\em Proceedings of the 27th ACM SIGKDD Conference on Knowledge
  Discovery and Data Mining}, KDD '21, page 3308–3318, New York, NY, USA,
  2021. Association for Computing Machinery.

\bibitem{prototype_liu}
Lihui Liu, Boxin Du, Heng Ji, and Hanghang Tong.
\newblock A knowledge graph reasoning prototype.
\newblock {\em NeurIPS (demo track)}, 2020.

\bibitem{binet}
Lihui Liu, Boxin Du, Jiejun Xu, Yinglong Xia, and Hanghang Tong.
\newblock Joint knowledge graph completion and question answering.
\newblock In {\em Proceedings of the 28th ACM SIGKDD Conference on Knowledge
  Discovery and Data Mining}, KDD '22, page 1098–1108, New York, NY, USA,
  2022. Association for Computing Machinery.

\bibitem{multimodal}
Kai Nakamura, Sharon Levy, and William~Yang Wang.
\newblock r/fakeddit: {A} new multimodal benchmark dataset for fine-grained
  fake news detection.
\newblock {\em CoRR}, abs/1911.03854, 2019.

\bibitem{das-etal-2017-chains}
D.~Rajarshi, N.~Arvind, B.~David, and M.~Andrew.
\newblock Chains of reasoning over entities, relations, and text using
  recurrent neural networks.
\newblock ACL '17, April 2017.

\bibitem{conan}
Shane Roach, Connie Ni, Alexei Kopylov, Tsai-Ching Lu, Jiejun Xu, Si~Zhang,
  Boxin Du, Dawei Zhou, Jun Wu, Lihui Liu, Yuchen Yan, Jingrui He, and Hanghang
  Tong.
\newblock Canon: Complex analytics of network of networks for modeling
  adversarial activities.
\newblock In {\em 2020 IEEE International Conference on Big Data (Big Data)},
  pages 1634--1643, 2020.

\bibitem{Shiralkar2017}
Prashant S, Alessandro F, Filippo M, and Giovanni C.
\newblock Finding streams in knowledge graphs to support fact checking.
\newblock pages 859--864, 11 2017.

\bibitem{Shi2016dpp}
B.~Shi and T.~Weninger.
\newblock Discriminative predicate path mining for fact checking in knowledge
  graphs.
\newblock {\em Know.-Based Syst.}, 104(C):123--133, July 2016.

\bibitem{kgminer}
Baoxu Shi and Tim Weninger.
\newblock Discriminative predicate path mining for fact checking in knowledge
  graphs.

\bibitem{shi2016discriminative}
Baoxu Shi and Tim Weninger.
\newblock Discriminative predicate path mining for fact checking in knowledge
  graphs.
\newblock {\em Knowledge-based systems}, 104:123--133, 2016.

\bibitem{shiralkar2017finding}
Prashant Shiralkar, Alessandro Flammini, Filippo Menczer, and Giovanni~Luca
  Ciampaglia.
\newblock Finding streams in knowledge graphs to support fact checking.
\newblock In {\em 2017 IEEE International Conference on Data Mining (ICDM)},
  pages 859--864. IEEE, 2017.

\bibitem{YinghuiWu}
Q.~{Song}, Y.~{Wu}, P.~{Lin}, L.~X. {Dong}, and H.~{Sun}.
\newblock {\em IEEE Transactions on Knowledge and Data Engineering},
  30(10):1887--1900, Oct 2018.

\bibitem{yago}
Fabian~M. Suchanek, Gjergji Kasneci, and Gerhard Weikum.
\newblock Yago: A core of semantic knowledge.
\newblock WWW ’07. Association for Computing Machinery, 2007.

\bibitem{rotatE}
Z.~Sun, Z.~Deng, J.~Nie, and J.~Tang.
\newblock Rotate: Knowledge graph embedding by relational rotation in complex
  space.
\newblock {\em ArXiv}, abs/1902.10197, 2019.

\bibitem{tchechmedjiev2019claimskg}
Andon Tchechmedjiev, Pavlos Fafalios, Katarina Boland, Malo Gasquet,
  Matth{\"a}us Zloch, Benjamin Zapilko, Stefan Dietze, and Konstantin Todorov.
\newblock Claimskg: a knowledge graph of fact-checked claims.
\newblock In {\em International Semantic Web Conference}, pages 309--324.
  Springer, 2019.

\bibitem{Tong2006CSP}
Hanghang Tong and Christos Faloutsos.
\newblock Center-piece subgraphs: Problem definition and fast solutions.
\newblock KDD '06, pages 404--413, New York, NY, USA, 2006. ACM.

\bibitem{Tong2006rdwalk}
Hanghang Tong, Christos Faloutsos, Christos Faloutsos, and Jia-Yu Pan.
\newblock Fast random walk with restart and its applications.
\newblock ICDM '06, pages 613--622, Washington, DC, USA, 2006. IEEE Computer
  Society.

\bibitem{pprop}
William~Yang Wang and William~W. Cohen.
\newblock Learning first-order logic embeddings via matrix factorization.
\newblock IJCAI’16, page 2132–2138. AAAI Press, 2016.

\bibitem{Wang2015QUT}
Z.~Wang, K.~Zhao, H.~Wang, X.~Meng, and J.~Wen.
\newblock Query understanding through knowledge-based conceptualization.
\newblock IJCAI'15, pages 3264--3270. AAAI Press, 2015.

\bibitem{willianWang}
W~Xiong, T~Hoang, and W~Wang.
\newblock Deeppath: A reinforcement learning method for knowledge graph
  reasoning.
\newblock In {\em EMNLP}, 2017.

\bibitem{bright}
Yuchen Yan, Si~Zhang, and Hanghang Tong.
\newblock Bright: A bridging algorithm for network alignment.
\newblock In {\em Proceedings of the Web Conference 2021}, WWW '21, page
  3907–3917, New York, NY, USA, 2021. Association for Computing Machinery.

\bibitem{Yang2014vldb}
Shengqi Yang, Yinghui Wu, Huan Sun, and Xifeng Yan.
\newblock Schemaless and structureless graph querying.
\newblock {\em Proc. VLDB Endow.}, 7(7):565--576, March 2014.

\bibitem{tongtao2018Gaia}
T.~Zhang, G.~Shi, L.~Huang, and D.~Lu and.
\newblock {GAIA} - {A} multi-media multi-lingual knowledge extraction and
  hypothesis generation system.
\newblock TAC' 18, 2018.

\bibitem{qinghai}
Q.~{Zhou}, L.~{Li}, N.~{Cao}, L.~{Ying}, and H.~{Tong}.
\newblock adversarial attacks on multi-network mining: problem definition and
  fast solutions.
\newblock ICDM '19, Dec 2019.

\end{thebibliography}

\end{document}

%%
%% End of file `sample-sigconf.tex'.
