\clearpage
\newpage

\newcommand{\bibauthors}[1]{{#1}}
\newcommand{\bibtitle}[1]{\emph{#1}}
\newcommand{\bibconf}[1]{{#1}}

\begin{thebibliography}{10}

\bibitem{Bajaj:arxiv2018}
\bibauthors{Payal Bajaj, Daniel Campos, Nick Craswell, Li Deng, Jianfeng Gao, Xiaodong Liu, Rangan Majumder, Andrew McNamara, Bhaskar Mitra, Tri Nguyen, Mir Rosenberg, Xia Song, Alina Stoica, Saurabh Tiwary, Tong Wang.}
\bibtitle{MS MARCO: A Human Generated MAchine Reading COmprehension Dataset.}
In \bibconf{arXiv 2018}.

\bibitem{DBLP:conf/acl/ChenFWB17}
\bibauthors{Danqi Chen, Adam Fisch, Jason Weston and Antoine Bordes.}
\bibtitle{Reading Wikipedia to Answer Open-Domain Questions.}
In \bibconf{ACL 2017}.

\bibitem{Christmann-CONVINSE:SIGIR2022}
\bibauthors{Philipp Christmann, Rishiraj Saha Roy, Gerhard Weikum.}
\bibtitle{Conversational Question Answering on Heterogeneous Sources.}
In \bibconf{SIGIR 2022}.

\bibitem{Christmann-CLOCQ:WSDM2022}
\bibauthors{Philipp Christmann, Rishiraj Saha Roy, Gerhard Weikum.}
\bibtitle{Beyond NED: Fast and Effective Search Space Reduction for Complex Question Answering over Knowledge Bases.}
In \bibconf{WSDM 2022}.

\bibitem{Christmann-Explaignn:SIGIR2023}
\bibauthors{Philipp Christmann, Rishiraj Saha Roy, Gerhard Weikum.}
\bibtitle{Explainable Conversational Question Answering over Heterogeneous Sources via Iterative Graph Neural Networks.}
In \bibconf{SIGIR 2023}.

\bibitem{Christmann-CompMix:WWW2024}
\bibauthors{Philipp Christmann, Rishiraj Saha Roy, Gerhard Weikum.}
\bibtitle{CompMix: A Benchmark for Heterogeneous Question Answering.}
In \bibconf{WWW 2024}.

\bibitem{Dejean:arxiv2024}
\bibauthors{Herve Dejean, Stephane Clinchant, Thibault Formal.}
\bibtitle{A Thorough Comparison of Cross-Encoders and LLMs for Reranking SPLADE.}
In \bibconf{arXiv 2024}.

\bibitem{Dhingra-time-aware-LLM:TACL2022}
\bibauthors{Bhuwan Dhingra, Jeremy R Cole, Julian Martin Eisenschlos, Daniel Gillick, Jacob Eisenstein, and William W Cohen.}
\bibtitle{Time-Aware Language Models as Temporal Knowledge Bases.}
In \bibconf{TACL 2022}.

\bibitem{Dong-Trust:PVLDB2015}
\bibauthors{Xin Luna Dong, Evgeniy Gabrilovich, Kevin Murphy, Van Dang, Wilko Horn, Camillo Lugaresi, Shaohua Sun, Wei Zhang.}
\bibtitle{Knowledge-Based Trust: Estimating the Trustworthiness of Web Sources.}
In \bibconf{PVLDB 2015}.

\bibitem{DBLP:journals/arXiv/abs-2312-10997}
\bibauthors{Yunfan Gao, Yun Xiong, Xinyu Gao, Kangxiang Jia, Jinliu Pan, Yuxi Bi, Yi Dai, Jiawei Sun, Qianyu Guo, Meng Wang, Haofen Wang.}
\bibtitle{Retrieval-Augmented Generation for Large Language Models: A Survey.}
In \bibconf{arXiv 2023}.

\bibitem{Gao-citations:emnlp2023}
\bibauthors{Tianyu Gao, Howard Yen, Jiatong Yu, Danqi Chen.}
\bibtitle{Enabling Large Language Models to Generate Text with Citations.}
In \bibconf{EMNLP 2023}.

\bibitem{Guu-REALM:ICML2020}
\bibauthors{Kelvin Guu, Kenton Lee, Zora Tung, Panupong Pasupat, Ming-Wei Chang.}
\bibtitle{Retrieval Augmented Language Model Pre-Training.}
In \bibconf{ICML 2020}.

\bibitem{DBLP:conf/eacl/IzacardG21}
\bibauthors{Gautier Izacard, Edouard Grave.}
\bibtitle{Leveraging Passage Retrieval with Generative Models for Open Domain Question Answering.}
In \bibconf{EACL 2021}.

\bibitem{Jia-TimeQuestions}
\bibauthors{Zhen Jia, Soumajit Pramanik, Rishiraj Saha Roy, and Gerhard Weikum.}
\bibtitle{Complex Temporal Question Answering on Knowledge Graphs.}
In \bibconf{CIKM 2021}.

\bibitem{Jia-FAITH:WWW2024}
\bibauthors{Zhen Jia, Philipp Christmann, Gerhard Weikum.}
\bibtitle{Faithful Temporal Question Answering over Heterogeneous Sources.}
In \bibconf{WWW 2024}.

\bibitem{DBLP:journals/arXiv/abs-2305-06984}
\bibauthors{Ehsan Kamalloo, Nouha Dziri, Charles L. A. Clarke, Davood Rafiei.}
\bibtitle{Evaluating Open-Domain Question Answering in the Era of Large Language Models.}
In \bibconf{arXiv 2023}.

\bibitem{Kandpal:ICML2023}
\bibauthors{Nikhil Kandpal, Haikang Deng, Adam Roberts, Eric Wallace, Colin Raffel.}
\bibtitle{Large Language Models Struggle to Learn Long-Tail Knowledge.}
In \bibconf{ICML 2023}.

\bibitem{DBLP:conf/emnlp/KarpukhinOMLWEC20}
\bibauthors{Vladimir Karpukhin, Barlas Oguz, Sewon Min, Patrick S. H. Lewis, Ledell Wu, Sergey Edunov, Danqi Chen, Wen-tau Yih.}
\bibtitle{Dense Passage Retrieval for Open-Domain Question Answering.}
In \bibconf{EMNLP 2020}.

\bibitem{Lee-MATTER:ACL2024}
\bibauthors{Dongkyu Lee, Chandana Satya Prakash, Jack FitzGerald, Jens Lehmann.}
\bibtitle{MATTER: Memory-Augmented Transformer Using Heterogeneous Knowledge Sources.}
In \bibconf{ACL 2024}.

\bibitem{DBLP:conf/acl/LewisLGGMLSZ20}
\bibauthors{Mike Lewis, Yinhan Liu, Naman Goyal, Marjan Ghazvininejad, Abdelrahman Mohamed, Omer Levy, Veselin Stoyanov, Luke Zettlemoyer.}
\bibtitle{BART: Denoising Sequence-to-Sequence Pre-training for Natural Language Generation, Translation, and Comprehension.}
In \bibconf{ACL 2020}.

\bibitem{DBLP:conf/nips/LewisPPPKGKLYR020}
\bibauthors{Patrick S. H. Lewis, Ethan Perez, Aleksandra Piktus, Fabio Petroni, Vladimir Karpukhin, Naman Goyal, Heinrich Küttler, Mike Lewis, Wen-tau Yih, Tim Rocktäschel, Sebastian Riedel, Douwe Kiela.}
\bibtitle{Retrieval-Augmented Generation for Knowledge-Intensive NLP Tasks.}
In \bibconf{NeurIPS 2020}.

\bibitem{Lin:MC2021}
\bibauthors{Jimmy Lin, Rodrigo Frassetto Nogueira, Andrew Yates.}
\bibtitle{Pretrained Transformers for Text Ranking: BERT and Beyond.}
In \bibconf{Morgan \& Claypool Publishers 2021}.

\bibitem{Liu-SUQL:NAACL2024}
\bibauthors{Shicheng Liu, Jialiang Xu, Wesley Tjangnaka, Sina J. Semnani, Chen Jie Yu, Monica Lam.}
\bibtitle{SUQL: Conversational Search over Structured and Unstructured Data with Large Language Models.}
In \bibconf{NAACL-HLT 2024}.

\bibitem{Mavi:FnT2024}
\bibauthors{Vaibhav Mavi, Anubhav Jangra, Adam Jatowt.}
\bibtitle{Multi-hop Question Answering.}
In \bibconf{Foundations and Trends in Information Retrieval 2024}.

\bibitem{Minaee-LLM-survey}
\bibauthors{Shervin Minaee, Tomas Mikolov, Narjes Nikzad, Meysam Chenaghlu, Richard}
\bibtitle{Socher, Xavier Amatriain, and Jianfeng Gao.}
Large Language Models: A Survey.
In \bibconf{arXiv 2024}.

\bibitem{Nogueira:arxiv2019}
\bibauthors{Rodrigo Frassetto Nogueira, Kyunghyun Cho.}
\bibtitle{Passage Re-ranking with BERT.}
In \bibconf{arXiv 2019}.

\bibitem{Oguz-UniK-QA:NAACL2022}
\bibauthors{Barlas Oguz, Xilun Chen, Vladimir Karpukhin, Stan Peshterliev, Dmytro Okhonko, Michael Sejr Schlichtkrull, Sonal Gupta, Yashar Mehdad, Scott Yih.}
\bibtitle{UniK-QA: Unified Representations of Structured and Unstructured Knowledge for Open-Domain Question Answering.}
In \bibconf{NAACL-HLT 2022}.

\bibitem{RogersGA:CS2023}
\bibauthors{Anna Rogers, Matt Gardner, Isabelle Augenstein.}
\bibtitle{QA Dataset Explosion: A Taxonomy of NLP Resources for Question Answering and Reading Comprehension.}
In \bibconf{ACM Computing Surveys 2023}.

\bibitem{RoyAnand:MC2021}
\bibauthors{Rishiraj Saha Roy, Avishek Anand.}
\bibtitle{Question Answering for the Curated Web: Tasks and Methods in QA over Knowledge Bases and Text Collections.}
In \bibconf{Synthesis Lectures on Information Concepts, Retrieval, and Services, Morgan \& Claypool Publishers 2021}.

\bibitem{Pramanik-Uniqorn:JWS2024}
\bibauthors{Soumajit Pramanik, Jesujoba Alabi, Rishiraj Saha Roy, Gerhard Weikum.}
\bibtitle{UNIQORN: Unified Question Answering over RDF Knowledge Graphs and Natural Language Text.}
In \bibconf{Journal of Web Semantics 2024}.

\bibitem{Sun-PullNet:EMNLP2019}
\bibauthors{Haitian Sun, Tania Bedrax-Weiss, William W. Cohen.}
\bibtitle{PullNet: Open Domain Question Answering with Iterative Retrieval on Knowledge Bases and Text.}
In \bibconf{EMNLP/IJCNLP 2019}.

\bibitem{Sun:NAACL2024}
\bibauthors{Kai Sun, Yifan Ethan Xu, Hanwen Zha, Yue Liu, Xin Luna Dong.}
\bibtitle{Head-to-Tail: How Knowledgeable are Large Language Models (LLMs)? A.K.A. Will LLMs Replace Knowledge Graphs?}
In \bibconf{NAACL-HLT 2024}.

\bibitem{Touvron-LLaMA}
\bibauthors{Hugo Touvron, Thibaut Lavril, Gautier Izacard, Xavier Martinet, Marie-Anne Lachaux, Timothée Lacroix, Baptiste Rozière, Naman Goyal, Eric Hambro, Faisal Azhar, Aurelien Rodriguez, Armand Joulin, Edouard Grave, Guillaume Lample.}
\bibtitle{Llama: Open and efficient foundation language models.}
In \bibconf{arXiv 2023}.

\bibitem{Wu-STARK:arxiv2024}
\bibauthors{Shirley Wu, Shiyu Zhao, Michihiro Yasunaga, Kexin Huang, Kaidi Cao, Qian Huang, Vassilis N. Ioannidis, Karthik Subbian, James Zou, Jure Leskovec.}
\bibtitle{STaRK: Benchmarking LLM Retrieval on Textual and Relational Knowledge Bases.}
In \bibconf{arXiv 2024}.

\bibitem{Wu:IEEE2021}
\bibauthors{Zonghan Wu, Shirui Pan, Fengwen Chen, Guodong Long, Chengqi Zhang, Philip S. Yu.}
\bibtitle{A Comprehensive Survey on Graph Neural Networks.}
In \bibconf{IEEE Transactions on Neural Networks and Learning Systems 2021}.

\bibitem{Yang-CRAG}
\bibauthors{Xiao Yang, Kai Sun, Hao Xin, Yushi Sun, Nikita Bhalla, Xiangsen Chen, Sajal Choudhary, Rongze D. Gui, Ziran W. Jiang, Ziyu Jiang, Lingkun Kong, Brian Moran, Jiaqi Wang, Yifan Ethan Xu, An Yan, Chenyu Yang, Eting Yuan, Hanwen Zha, Nan Tang, Lei Chen, Nicolas Scheffer, Yue Liu, Nirav Shah, Rakesh Wanga, Anuj Kumar, Wen-tau Yih, Xin Luna Dong.}
\bibtitle{CRAG -- Comprehensive RAG Benchmark.}
In \bibconf{arXiv 2024}.

\bibitem{Yasunaga:NAACL2021}
\bibauthors{Michihiro Yasunaga, Hongyu Ren, Antoine Bosselut, Percy Liang, Jure Leskovec.}
\bibtitle{QA-GNN: Reasoning with Language Models and Knowledge Graphs for Question Answering.}
In \bibconf{NAACL-HLT 2021}.

\bibitem{Zhang-Spaghetti:ACL2024}
\bibauthors{Heidi C. Zhang, Sina J. Semnani, Farhad Ghassemi, Jialiang Xu, Shicheng Liu, Monica S. Lam.}
\bibtitle{SPAGHETTI: Open-Domain Question Answering from Heterogeneous Data Sources with Retrieval and Semantic Parsing.}
In \bibconf{ACL 2024}.

\bibitem{Zhang:NAACL2024}
\bibauthors{Jiahao Zhang, Haiyang Zhang, Dongmei Zhang, Yong Liu, Shen Huang.}
\bibtitle{End-to-End Beam Retrieval for Multi-Hop Question Answering.}
In \bibconf{NAACL-HLT 2024}.

\bibitem{Zhao-LLMsurvey}
\bibauthors{Wayne Xin Zhao, Kun Zhou, Junyi Li, Tianyi Tang, Xiaolei Wang, Yupeng Hou, Yingqian Min, Beichen Zhang, Junjie Zhang, Zican Dong, Yifan Du, Chen Yang, Yushuo Chen, Zhipeng Chen, Jinhao Jiang, Ruiyang Ren, Yifan Li, Xinyu Tang, Zikang Liu, Peiyu Liu, Jian-Yun Nie, Ji-Rong Wen.}
\bibtitle{A Survey of Large Language Models.}
In \bibconf{arXiv 2023}.

\bibitem{Zhao:arxiv2024}
\bibauthors{Penghao Zhao, Hailin Zhang, Qinhan Yu, Zhengren Wang, Yunteng Geng, Fangcheng Fu, Ling Yang, Wentao Zhang, Bin Cui.}
\bibtitle{Retrieval-Augmented Generation for AI-Generated Content: A Survey.}
In \bibconf{arXiv 2024}.

\bibitem{Zhu-ODQA-survey:arxiv2021}
\bibauthors{Fengbin Zhu, Wenqiang Lei, Chao Wang, Jianming Zheng, Soujanya Poria, Tat-Seng Chua.}
\bibtitle{Retrieving and Reading: A Comprehensive Survey on Open-domain Question Answering.}
In \bibconf{arXiv 2021}.

\end{thebibliography}
