\documentclass[11pt]{article} 

\usepackage{deauthor,times,graphicx}
\usepackage{hyperref}

\begin{document}
Machine learning and artificial intelligence, fueled by big data, fast
communication channels, and information openness, are shaping our
future. What is the role of data management in this trend?  The
September issue of the Data Engineering Bulletin takes a look at the
big promise and challenge of the technology, and the ongoing work of
the data management community.

Christian Jensen envisions a future where massive volumes of data that
capture vehicle movements become available. How will we use the data
for better routing solutions that save travel costs, such as travel
time?  Beng Chin Ooi et al look into 5G, one of the most important
enabling technologies for a future that will be defined by the
internet of things, and analyzes the impact of 5G technologies on the
landscape of computing, in particular, data management.

While setting our eyes on the potential benefits of data-driven
technologies, we must not overlook the risks and dangers when humanity
hand over decision making to AI systems. In recent years, fairness has
become one of the most popular topics in machine learning. Alexandra
Meliou, the associate editor of this issue, has put together an exciting
collection of recent and ongoing work that focuses on the problems of
fairness, diversity, and transparency in data-driven systems.

I would also like to congratulate the 2019 TCDE awards winners. The
awards committee chaired by Johannes Gehrke presents the TKDE impact
award, service award, and rising star award to Christian Jensen, David
Lomet, and Viktor Leis, respectively. The letters from the awards
winners share their personal reflection and vision based on the great
work they have accomplished.


\end{document}

