\documentclass[11pt]{article}
% guidelines at http://tab.computer.org/tcde/bull_author.html
\usepackage{deauthor,times,graphicx}
%\graphicspath{{authorname/}}

%\usepackage[dvipsnames,svgnames]{xcolor}
\usepackage{tikz}
\usepackage{amssymb, framed}
\usepackage{tikz}
\usepackage{rotating}
\usepackage{xcolor}
\usepackage{hyperref}
\usetikzlibrary{trees,shapes,snakes,patterns}
% % % --------------------------------------- % % %
% % % Macros to write comments for internal usage % % %
% % % --------------------------------------- % % %

\newcommand{\red}[1]{\textcolor{red}{#1}}
\newcommand{\eat}[1]{}
\newcommand{\argmax}{\mathop{\rm arg~max}\limits}

\begin{document}
\title{%How AI and People Work Together: 
Computational Division of Labor with Human and AI Workers}
%The future of Crowdsourcing Platforms: Ecosystems and Interoperability}

%\author{Atsuyuki Morishima,\\ University of Tsukuba\\
%\texttt{{\footnotesize mori@slis.tsukuba.ac.jp}}
%\and
%Masaki Matsubara\\
%University of Tsukuba\\
%\texttt{{\footnotesize masaki@slis.tsukuba.ac.jp}}
%\and
%Kei Wakabayashi\\
%University of Tsukuba\\
%\texttt{{\footnotesize kwakaba@slis.tsukuba.ac.jp}}
%\and
%Nobutaka Suzuki\\
%University of Tsukuba\\
%\texttt{{\footnotesize nsuzuki@slis.tsukuba.ac.jp}}
%\and
%Hiroyoshi Ito\\
%Universityu of Tsukuba\\
%\texttt{{\footnotesize ito@slis.tsukuba.ac.jp}}
%}

\author{
	Atsuyuki Morishima,
	Masaki Matsubara,
	Kei Wakabayashi,
	Nobutaka Suzuki,
	Hiroyoshi Ito \\
	University of Tsukuba\\
	\texttt{{\footnotesize \{mori, masaki, kwakaba, nsuzuki, ito\}@slis.tsukuba.ac.jp}}
}

\maketitle

\newcommand{\scream}[1]{\textbf{***#1***}}

% -------------------------------------------------------- %

\input{submissions_new/morishima/abstract}
\input{submissions_new/morishima/introduction}
%\input{motivation}
%\input{platformDesign}
%\input{platformInteroperability}
\input{submissions_new/morishima/conclusion}
%\vspace{-.6cm}
%\enlargethispage{1cm}
%\bibliographystyle{abbrv}
%\bibliography{crowdsourcing}
%\bibliography{platformsBib}

\begin{thebibliography}{10}
	
	\bibitem{Sih+20}
	S.~Amer-Yahia et~al.
	\newblock Making ai machines work for humans in fow.
	\newblock {\em ACM SIGMOD RECORD (to appear)}, 2020.
	
	\bibitem{AR16}
	S.~Amer{-}Yahia and S.~B. Roy.
	\newblock Toward worker-centric crowdsourcing.
	\newblock {\em {IEEE} Data Eng. Bull.}, 39(4):3--13, 2016.
	
	\bibitem{BLM+10}
	M.~S. Bernstein, G.~Little, R.~C. Miller, B.~Hartmann, M.~S. Ackerman, D.~R.
	Karger, D.~Crowell, and K.~Panovich.
	\newblock Soylent: a word processor with a crowd inside.
	\newblock In {\em Proceedings of the 23rd Annual {ACM} Symposium on User
		Interface Software and Technology, New York, NY, USA, October 3-6, 2010},
	pages 313--322, 2010.
	
	\bibitem{Dha16}
	V.~Dhar.
	\newblock When to trust robots with decisions, and when not to.
	\newblock {\em Harvard Business Review}, May 2016.
	
	\bibitem{FZL+12}
	M.~Fang, X.~Zhu, B.~Li, W.~Ding, and X.~Wu.
	\newblock {Self-Taught} active learning from crowds.
	\newblock In {\em 2012 {IEEE} 12th International Conference on Data Mining},
	pages 858--863, Dec. 2012.
	
	\bibitem{FKK+11}
	M.~J. Franklin, D.~Kossmann, T.~Kraska, S.~Ramesh, and R.~Xin.
	\newblock Crowddb: answering queries with crowdsourcing.
	\newblock In {\em Proceedings of the {ACM} {SIGMOD} International Conference on
		Management of Data, {SIGMOD} 2011, Athens, Greece, June 12-16, 2011}, pages
	61--72, 2011.
	
	\bibitem{GK11}
	J.~GREUBEL and G.~KECKLUND.
	\newblock The impact of organizational changes on work stress, sleep, recovery
	and health.
	\newblock {\em Industrial Health}, advpub:1102240056--1102240056, 2011.
	
	\bibitem{GMT+19}
	D.~Gross{-}Amblard, A.~Morishima, S.~Thirumuruganathan, M.~Tommasi, and
	K.~Yoshida.
	\newblock Platform design for crowdsourcing and future of work.
	\newblock {\em {IEEE} Data Eng. Bull.}, 42(4):35--45, 2019.
	
	\bibitem{HHM+15}
	S.~Hao, S.~C.~H. Hoi, C.~Miao, and P.~Zhao.
	\newblock Active crowdsourcing for annotation.
	\newblock In {\em 2015 {IEEE/WIC/ACM} International Conference on Web
		Intelligence and Intelligent Agent Technology ({WI-IAT})}, pages 1--8. IEEE,
	Dec. 2015.
	
	\bibitem{JAB15}
	E.~Johns, O.~Mac~Aodha, and G.~J. Brostow.
	\newblock Becoming the expert - interactive multi-class machine teaching.
	\newblock In {\em Proceedings of the {IEEE} Conference on Computer Vision and
		Pattern Recognition}, pages 2616--2624, 2015.
	
	\bibitem{KWM20b}
	M.~Kimura, K.~Wakabayashi, and A.~Morishima.
	\newblock Batch prioritization of data labeling tasks for training classifiers.
	\newblock In {\em Proceedings of the Eighth {AAAI} Conference on Human
		Computation and Crowdsourcing,HCOMP 2020}, 2020.
	
	\bibitem{KMM+18}
	M.~Kobayashi, H.~Morita, M.~Matsubara, N.~Shimizu, and A.~Morishima.
	\newblock An empirical study on short- and long-term effects of self-correction
	in crowdsourced microtasks.
	\newblock In {\em Proceedings of the Sixth {AAAI} Conference on Human
		Computation and Crowdsourcing, {HCOMP} 2018, Z{\"{u}}rich, Switzerland, July
		5-8, 2018}, pages 79--87, 2018.
	
	\bibitem{KWM20}
	M.~Kobayashi, K.~Wakabayashi, and A.~Morishima.
	\newblock Quality-aware dynamic task assignment in human+ai crowd.
	\newblock In A.~E.~F. Seghrouchni, G.~Sukthankar, T.~Liu, and M.~van Steen,
	editors, {\em Companion of The 2020 Web Conference 2020, Taipei, Taiwan,
		April 20-24, 2020}, pages 118--119. {ACM} / {IW3C2}, 2020.
	
	\bibitem{KCH12}
	A.~Kulkarni, M.~Can, and B.~Hartmann.
	\newblock Collaboratively crowdsourcing workflows with turkomatic.
	\newblock In {\em Proceedings of the ACM 2012 Conference on Computer Supported
		Cooperative Work}, CSCW '12, pages 1003--1012, New York, NY, USA, 2012. ACM.
	
	\bibitem{KMS+18}
	K.~Kumai, M.~Matsubara, Y.~Shiraishi, D.~Wakatsuki, J.~Zhang, T.~Shionome,
	H.~Kitagawa, and A.~Morishima.
	\newblock Skill-and-stress-aware assignment of crowd-worker groups to task
	streams.
	\newblock In {\em Proceedings of the Sixth {AAAI} Conference on Human
		Computation and Crowdsourcing, {HCOMP} 2018, Z{\"{u}}rich, Switzerland, July
		5-8, 2018.}, pages 88--97, 2018.
	
	\bibitem{Kur01}
	R.~Kurzweil.
	\newblock The law of accelerating returns, 2001.
	\newblock kurzweilai.net/the-law-of-accelerating-returns.
	
	\bibitem{LDH+17}
	W.~Liu, B.~Dai, A.~Humayun, C.~Tay, C.~Yu, L.~B. Smith, J.~M. Rehg, and
	L.~Song.
	\newblock Iterative machine teaching.
	\newblock {\em arXiv preprint arXiv:1705.10470}, 2017.
	
	\bibitem{NWL15}
	A.~T. Nguyen, B.~C. Wallace, and M.~Lease.
	\newblock Combining crowd and expert labels using decision theoretic active
	learning.
	\newblock In E.~Gerber and P.~Ipeirotis, editors, {\em Proceedings of the Third
		{AAAI} Conference on Human Computation and Crowdsourcing, {HCOMP} 2015,
		November 8-11, 2015, San Diego, California, {USA}}, pages 120--129. {AAAI}
	Press, 2015.
	
	\bibitem{PPG+12}
	A.~G. Parameswaran, H.~Park, H.~Garcia{-}Molina, N.~Polyzotis, and J.~Widom.
	\newblock Deco: declarative crowdsourcing.
	\newblock In {\em 21st {ACM} International Conference on Information and
		Knowledge Management, CIKM'12, Maui, HI, USA, October 29 - November 02,
		2012}, pages 1203--1212, 2012.
	
	\bibitem{PAS+18}
	J.~Pilourdault, S.~Amer-Yahia, S.~B. Roy, and D.~Lee.
	\newblock Task relevance and diversity as worker motivation in crowdsourcing.
	\newblock In {\em 2018 IEEE 34th International Conference on Data Engineering
		(ICDE)}, pages 365--376. IEEE, 2018.
	
	\bibitem{RRT+19}
	H.~Rahman, S.~B. Roy, S.~Thirumuruganathan, S.~Amer-Yahia, and G.~Das.
	\newblock Optimized group formation for solving collaborative tasks.
	\newblock {\em The VLDB Journal}, 28(1):1--23, 2019.
	
	\bibitem{RPR14}
	F.~Rodrigues, F.~Pereira, and B.~Ribeiro.
	\newblock Gaussian process classification and active learning with multiple
	annotators.
	\newblock 32(2):433--441, 2014.
	
	\bibitem{RLT+15}
	S.~B. Roy, I.~Lykourentzou, S.~Thirumuruganathan, S.~Amer{-}Yahia, and G.~Das.
	\newblock Task assignment optimization in knowledge-intensive crowdsourcing.
	\newblock {\em {VLDB} J.}, 24(4):467--491, 2015.
	
	\bibitem{YXG18}
	C.~P.~G. Runzhe~Yang, Yexiang~Xue.
	\newblock Pedagogical value-aligned crowdsourcing: Inspiring the wisdom of
	crowds via interactive teaching.
	\newblock {\em International Conference on Autonomous Agents and Multiagent
		Systems(AAMAS)}, 2018.
	
	\bibitem{KGS14}
	S.~S. Sara C.~Kingsley, Mary L.~Gray.
	\newblock Monopsony and the crowd: Labor for lemons?
	\newblock In {\em Proceedings of the Internet, Policy \& Politics Conference
		(IPP2014)}, 2014.
	
	\bibitem{Set09}
	B.~Settles.
	\newblock Active learning literature survey.
	\newblock Technical report, University of Wisconsin-Madison Department of
	Computer Sciences, 2009.
	
	\bibitem{Smi76}
	A.~Smith.
	\newblock {\em An Inquiry into the Nature and Causes of the Wealth of Nations}.
	\newblock McMaster University Archive for the History of Economic Thought,
	1776.
	
	\bibitem{SSL+16}
	R.~Suzuki, N.~Salehi, M.~S. Lam, J.~C. Marroquin, and M.~S. Bernstein.
	\newblock Atelier: Repurposing expert crowdsourcing tasks as micro-internships.
	\newblock In {\em Proceedings of the 2016 CHI Conference on Human Factors in
		Computing Systems}, pages 2645--2656, 2016.
	
	\bibitem{TZZ+20}
	Y.~Tong, Z.~Zhou, Y.~Zeng, L.~Chen, and C.~Shahabi.
	\newblock Spatial crowdsourcing: a survey.
	\newblock {\em {VLDB} J.}, 29(1):217--250, 2020.
	
	\bibitem{VRT+17}
	M.~A. Valentine, D.~Retelny, A.~To, N.~Rahmati, T.~Doshi, and M.~S. Bernstein.
	\newblock Flash organizations: Crowdsourcing complex work by structuring crowds
	as organizations.
	\newblock In {\em Proceedings of the 2017 CHI conference on human factors in
		computing systems}, pages 3523--3537, 2017.
	
	\bibitem{YRF+11}
	Y.~Yan, R.~Rosales, G.~Fung, and J.~G. Dy.
	\newblock Active learning from crowds.
	\newblock In {\em Proceedings of the 28th International Conference on Machine
		Learning, {ICML} 2011, Bellevue, Washington, USA, June 28 - July 2, 2011},
	pages 1161--1168, 2011.
	
	\bibitem{ZC15}
	C.~Zhang and K.~Chaudhuri.
	\newblock Active learning from weak and strong labelers.
	\newblock In C.~Cortes, N.~D. Lawrence, D.~D. Lee, M.~Sugiyama, and R.~Garnett,
	editors, {\em Advances in Neural Information Processing Systems 28}, pages
	703--711. Curran Associates, Inc., 2015.
	
\end{thebibliography}


\end{document}
