\documentclass[11pt]{article} 

\usepackage{deauthor,times,graphicx}
%\usepackage{url}
%\usepackage{hyperref}

\begin{document}

The June issue of the Data Engineering Bulletin features an opinion
piece by Carlo Zaniolo et al, a collection of papers on the topic of
knowledge management for e-commerce, and letters from the 2021 IEEE
TCDE Award winners.

It feels nostalgic to read the opinion piece written by Carlo Zaniolo
et al on the topic of stable semantics and aggregates. It continues to
amaze me that aggregates combined with recursion can be so powerful
and at the same time so elegant. The immediate contribution of the
paper is to unify the semantics of programs with different aggregates,
and thus significantly simplify the verification of their stable model
semantics. But the paper is really a culmination of a long history of
research focusing on how to express very powerful algorithms using
declarative programs and the root of the research dates back to a few
seminal works by Zaniolo decades ago, including the work on the Logic
Database Language (LDL).

The subject of this special issue is knowledge management for
e-commerce, curated by associate editors Bing Yin and Sreyashi Nag,
who work on e-commerce search at Amazon. Despite e-commerce's huge
growth in the last decades and the massive technology investment
behind online shopping, the field is still in its early stage when it
comes to creating an amazing customer experience. The challenge is
that a great customer experience must be founded on a clear
understanding of customers' needs and the products that can
potentially fulfill the needs. It has become clear that knowledge
management -- from customer profiling to product knowledge graph
curation -- lies at the core of this effort.

We would like to congratulate Divesh Srivastava and Arun Kumar for
winning the 2021 IEEE TCDE Award. Srivastava is the recipient of the
Impact Award for his contributions to many areas of data management in
the last three decades, including deductive databases, streaming
algorithms, and data integration, etc. Kumar is the recipient of the
Rising Star Award for his vision and pioneering work on DB+ML
systems. In their letters, they shared their unique perspectives on
the past and the future of data management.

\end{document}
