%!TEX root=../bulletin.tex
\begin{abstract}
	
Data preparation is a crucial phase for data analysis applications. Data scientists spend most of their time on collecting and preparing data in order to efficiently and accurately extract valuable insights. Data preparation
involves multiple steps of transformations until data is ready for analysis. 
%functionality
Users often need to integrate heterogeneous data; to query data of various formats, one has to transform the data to a common format. % and load them into a DBMS that can handle their functionality requirements. 
%accuracy
To accurately execute queries over the transformed data, users have to remove any inconsistencies by applying cleaning operations. 
%performance
To efficiently execute queries, they need to tune access paths over the data. 
Data preparation, however is i) time-consuming since it involves 
expensive operations, and ii) lacks knowledge of the workload; a lot 
of preparation effort is wasted on data never meant to be used.

To address the functionality and performance requirements of data analysis, we re-design data preparation in a way that is weaved into data analysis. We eliminate the transform-and-load cost 
%when it comes to integrating heterogeneous data 
using in-situ query processing approaches which adapt to any data 
format and facilitate querying diverse datasets. 
To address the scalability issues of cleaning and tuning tasks, we 
inject cleaning operations into query processing, and adapt access 
paths on-the-fly. By integrating the aforementioned tasks into data 
analysis, we adapt data preparation to each workload and thereby 
minimize response times.
	
\end{abstract}