\documentclass[11pt]{article}
\usepackage{deauthor}
\usepackage{times}
\usepackage{wrapfig}
\usepackage{graphicx}
\usepackage{xspace}
% \usepackage[it,small]{caption}
% \usepackage[export]{adjustbox}
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{textcomp}
\usepackage{graphicx}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{xcolor}


% ensure times
\usepackage{txfonts}
\usepackage{url}

\usepackage{balance}  % for  \balance command ON LAST PAGE  (only there!)
\usepackage{booktabs} % For formal tables
\usepackage{enumitem}
\usepackage{multirow}
\usepackage{subcaption}
\usepackage{authblk}

% \usepackage[pdfpagelabels=false]{hyperref}

\usepackage{listings}

\usepackage{outlines}



% Break URLs properly

\title{The Road for Recovery: 
Aligning COVID-19 efforts and building a more resilient future}

\author{Meredith M. Lee, Alicia D. Johnson, Katherine A. Yelick, and Jennifer T. Chayes
\\
UC Berkeley Division of Computing, Data Science, and Society, \\
West Big Data Innovation Hub, \\
UC Berkeley Office of Emergency Management, \\
UC Berkeley Department of Electrical Engineering and Computer Sciences, \\
and Lawrence Berkeley National Laboratory}

\begin{document}

\maketitle

%\begin{abstract}
%Governments around the world have become increasingly frustrated with tech giants dictating public health policy. The software created by Apple and Google enables individuals to track their own potential exposure through collated exposure notifications. However, the same software prohibits location tracking, denying key information needed by public health officials for robust contract tracing. This information is needed to treat and isolate COVID-19 positive people, identify transmission hotspots, and protect against continued spread of infection.
%In this article, we present two simple ideas: the \textbf{lighthouse} and the \textbf{covid-commons} that address the needs of public health authorities while preserving the privacy-sensitive goals of the Apple and google exposure notification protocols. 
%\end{abstract}

\input{section1}

\input{section2}

\input{section3}

\input{section4}

\input{section5}
\input{section6}
\input{acknowledgements}

% \bibliographystyle{IEEEtran}
% \bibliography{references}


% Generated by IEEEtran.bst, version: 1.14 (2015/08/26)
\begin{thebibliography}{10}
\providecommand{\url}[1]{#1}
\csname url@samestyle\endcsname
\providecommand{\newblock}{\relax}
\providecommand{\bibinfo}[2]{#2}
\providecommand{\BIBentrySTDinterwordspacing}{\spaceskip=0pt\relax}
\providecommand{\BIBentryALTinterwordstretchfactor}{4}
\providecommand{\BIBentryALTinterwordspacing}{\spaceskip=\fontdimen2\font plus
\BIBentryALTinterwordstretchfactor\fontdimen3\font minus
  \fontdimen4\font\relax}
\providecommand{\BIBforeignlanguage}[2]{{%
\expandafter\ifx\csname l@#1\endcsname\relax
\typeout{** WARNING: IEEEtran.bst: No hyphenation pattern has been}%
\typeout{** loaded for the language `#1'. Using the pattern for}%
\typeout{** the default language instead.}%
\else
\language=\csname l@#1\endcsname
\fi
#2}}
\providecommand{\BIBdecl}{\relax}
\BIBdecl

\bibitem{Lewnardm1923}
J.~A. Lewnard~et al., ``{Incidence, clinical outcomes, and transmission
  dynamics of severe coronavirus disease 2019 in California and Washington:
  prospective cohort study},'' \emph{BMJ}, vol. 369, 2020.

\bibitem{best_boice_2020}
\BIBentryALTinterwordspacing
R.~Best and J.~Boice, ``{Where the latest COVID-19 models think we're headed -
  and why they disagree},'' May 2020. [Online]. Available:
  \url{https://projects.fivethirtyeight.com/covid-forecasts/}
\BIBentrySTDinterwordspacing

\bibitem{institute}
\BIBentryALTinterwordspacing
``{Institute for Health Metrics and Evaluation}.'' [Online]. Available:
  \url{http://www.healthdata.org/}
\BIBentrySTDinterwordspacing

\bibitem{covidactnow}
\BIBentryALTinterwordspacing
``{CovidActNow.org}.'' [Online]. Available: \url{https://www.covidactnow.org/}
\BIBentrySTDinterwordspacing

\bibitem{altieri2020curating}
\BIBentryALTinterwordspacing
N.~Altieri~et al., ``{Curating a COVID-19 data repository and forecasting
  county-level death counts in the United States},'' 2020. [Online]. Available:
  \url{https://arxiv.org/abs/2005.07882}
\BIBentrySTDinterwordspacing

\bibitem{Modi2020.04.15.20067074}
\BIBentryALTinterwordspacing
C.~Modi, V.~Boehm, S.~Ferraro, G.~Stein, and U.~Seljak, ``{How deadly is
  COVID-19? A rigorous analysis of excess mortality and age-dependent fatality
  rates in Italy},'' \emph{medRxiv}, 2020. [Online]. Available:
  \url{https://www.medrxiv.org/content/early/2020/05/14/2020.04.15.20067074}
\BIBentrySTDinterwordspacing

\bibitem{Yadlowsky2020.03.24.20043067}
\BIBentryALTinterwordspacing
S.~Yadlowsky, N.~Shah, and J.~Steinhardt, ``{Estimation of SARS-CoV-2 infection
  prevalence in Santa Clara County},'' \emph{medRxiv}, 2020. [Online].
  Available:
  \url{https://www.medrxiv.org/content/early/2020/03/27/2020.03.24.20043067}
\BIBentrySTDinterwordspacing

\bibitem{steinhardt}
\BIBentryALTinterwordspacing
J.~Steinhardt and A.~Ilyas, ``{Prevalence tracking mechanisms for
  SARS-CoV-2},'' (Accessed 29 May 2020). [Online]. Available:
  \url{http://web.archive.org/web/20200529022542/https://www.stat.berkeley.edu/~jsteinhardt/publications/CovidPrevalenceTracking.pdf}
\BIBentrySTDinterwordspacing

\bibitem{Smith2020}
\BIBentryALTinterwordspacing
M.~Smith and J.~C. Smith, ``{Repurposing therapeutics for COVID-19:
  Supercomputer-based docking to the SARS-CoV-2 viral spike protein and viral
  spike protein-human ACE2 interface},'' 3 2020. [Online]. Available:
  \url{https://chemrxiv.org/articles/Repurposing_Therapeutics_for_the_Wuhan_Coronavirus_nCov-2019_Supercomputer-Based_Docking_to_the_Viral_S_Protein_and_Human_ACE2_Interface/11871402}
\BIBentrySTDinterwordspacing

\bibitem{Chen2020.04.17.047548}
\BIBentryALTinterwordspacing
S.~H. Chen, M.~T. Young, J.~Gounley, C.~Stanley, and D.~Bhowmik, ``{Distinct
  structural flexibility within SARS-CoV-2 spike protein reveals potential
  therapeutic targets},'' \emph{bioRxiv}, 2020. [Online]. Available:
  \url{https://www.biorxiv.org/content/early/2020/04/18/2020.04.17.047548}
\BIBentrySTDinterwordspacing

\bibitem{nextstrain}
\BIBentryALTinterwordspacing
``{Nextstrain.org},'' (Accessed 29 May 2020). [Online]. Available:
  \url{http://web.archive.org/web/20200529023700/https://nextstrain.org/ncov-sit-reps/}
\BIBentrySTDinterwordspacing

\bibitem{schneider2019rethinking}
P.~Schneider~et al., ``Rethinking drug design in the artificial intelligence
  era,'' \emph{Nature Reviews Drug Discovery}, pp. 1--12, 2019.

\bibitem{kaggle}
\BIBentryALTinterwordspacing
``{kaggle CORD-19 Research Challenge},'' (Accessed 29 May 2020). [Online].
  Available:
  \url{http://web.archive.org/web/20200529015651/https://www.kaggle.com/allen-institute-for-ai/CORD-19-research-challenge}
\BIBentrySTDinterwordspacing

\bibitem{crisisstandard}
\BIBentryALTinterwordspacing
``{Digital Crisis Standard - covid19.ca.gov},'' (Accessed 15 May 2020).
  [Online]. Available:
  \url{http://web.archive.org/web/20200515011426/https://github.com/cagov/covid19/wiki/Crisis-standard}
\BIBentrySTDinterwordspacing

\bibitem{cavoukian2013privacy}
A.~Cavoukian, ``Privacy by design: leadership, methods, and results,'' in
  \emph{European Data Protection: Coming of Age}.\hskip 1em plus 0.5em minus
  0.4em\relax Springer, 2013, pp. 175--202.

\bibitem{GDPR}
\BIBentryALTinterwordspacing
``{General Data Protection Regulation}.'' [Online]. Available:
  \url{https://ec.europa.eu/commission/priorities/
  justice-and-fundamental-rights/data-protection/2018-reform-eu-data-protection-rules_en}
\BIBentrySTDinterwordspacing

\bibitem{mares2019iot}
C.~D. Mares, ``{IoT: Privacy, security, and your civil rights},'' in
  \emph{Women Securing the Future with TIPPSS for IoT}.\hskip 1em plus 0.5em
  minus 0.4em\relax Springer, 2019, pp. 15--36.

\bibitem{FPF}
\BIBentryALTinterwordspacing
G.~Zanfir-Fortuna, ``{European Union’s data-based policy against the
  pandemic, explained},'' (Accessed 29 May 2020). [Online]. Available:
  \url{http://web.archive.org/web/20200529042315/https://fpf.org/2020/04/30/european-unions-data-based-policy-against-the-pandemic-explained/}
\BIBentrySTDinterwordspacing

\bibitem{10.1007/3-540-45427-6_23}
M.~Langheinrich, ``Privacy by design - principles of privacy-aware ubiquitous
  systems,'' in \emph{Ubiquitous Computing}, G.~D. Abowd, B.~Brumitt, and
  S.~Shafer, Eds.\hskip 1em plus 0.5em minus 0.4em\relax Berlin: Springer,
  2001, pp. 273--291.

\bibitem{10.1145/642611.642635}
L.~Palen and P.~Dourish, ``Unpacking “privacy” for a networked world,'' in
  \emph{Proceedings of the SIGCHI Conference on Human Factors in Computing
  Systems}, 2003, p. 129–136.

\bibitem{covidrace}
\BIBentryALTinterwordspacing
``{The COVID Racial Data Tracker}.'' [Online]. Available:
  \url{https://covidtracking.com/race}
\BIBentrySTDinterwordspacing

\bibitem{Obermeyer447}
Z.~Obermeyer, B.~Powers, C.~Vogeli, and S.~Mullainathan, ``Dissecting racial
  bias in an algorithm used to manage the health of populations,''
  \emph{Science}, vol. 366, no. 6464, pp. 447--453, 2019.

\bibitem{GARE}
\BIBentryALTinterwordspacing
``{Government Alliance on Race and Equity}.'' [Online]. Available:
  \url{https://www.racialequityalliance.org/}
\BIBentrySTDinterwordspacing

\bibitem{blumenstock2020machine}
J.~Blumenstock, ``{Machine learning can help get COVID-19 aid to those who need
  it most},'' \emph{Nature}, 2020.

\bibitem{blumenstock2016fighting}
J.~E. Blumenstock, ``Fighting poverty with data,'' \emph{Science}, vol. 353,
  no. 6301, pp. 753--754, 2016.

\bibitem{zade}
\BIBentryALTinterwordspacing
H.~Zade, K.~Shah, V.~Rangarajan, P.~Kshirsagar, M.~Imran, and K.~Starbird,
  ``From situational awareness to actionability: Towards improving the utility
  of social media data for crisis response,'' \emph{Proc. ACM Hum.-Comput.
  Interact.}, vol.~2, no. CSCW, Nov. 2018. [Online]. Available:
  \url{https://doi.org/10.1145/3274464}
\BIBentrySTDinterwordspacing

\bibitem{UN}
\BIBentryALTinterwordspacing
``{UN tackles ‘infodemic’ of misinformation and cybercrime in COVID-19
  crisis}.'' [Online]. Available:
  \url{http://web.archive.org/web/20200529050148/https://www.un.org/}
\BIBentrySTDinterwordspacing

\bibitem{Hany}
S.~J. Nightingale, M.~Faddoul, and H.~Farid, ``{Quantifying the reach and
  belief in COVID-19 misinformation},'' in press.

\bibitem{zhou2020clinical}
F.~Zhou~et al., ``{Clinical course and risk factors for mortality of adult
  inpatients with COVID-19 in Wuhan, China: a retrospective cohort study},''
  \emph{The Lancet}, 2020.

\bibitem{onder2020case}
G.~Onder, G.~Rezza, and S.~Brusaferro, ``{Case-fatality rate and
  characteristics of patients dying in relation to COVID-19 in Italy},''
  \emph{JAMA}, vol. 323, no.~18, pp. 1775--1776, 2020.

\bibitem{FEMAPOG}
\BIBentryALTinterwordspacing
{U.S. Department of Homeland Security, Federal Emergency Management Agency},
  ``{COVID-19 Pandemic Operational Guidance for the 2020 Hurricane Season}.''
  [Online]. Available:
  \url{https://www.fema.gov/media-library-data/1589997234798-adb5ce5cb98a7a89e3e1800becf0eb65/2020_Hurricane_Pandemic_Plan.pdf}
\BIBentrySTDinterwordspacing

\bibitem{doi:10.1056/NEJMc2009432}
\BIBentryALTinterwordspacing
M.~L. Zeidel, C.~Kirk, and B.~Linville-Engler, ``Opening up new supply
  chains,'' \emph{New England Journal of Medicine}, vol. 382, no.~21, p. e73,
  2020. [Online]. Available: \url{https://doi.org/10.1056/NEJMc2009432}
\BIBentrySTDinterwordspacing

\bibitem{western}
\BIBentryALTinterwordspacing
``{California, Oregon, and Washington announce western states pact}.''
  [Online]. Available:
  \url{https://www.gov.ca.gov/2020/04/13/california-oregon-washington-announce-western-states-pact/}
\BIBentrySTDinterwordspacing

\bibitem{abebe2020roles}
R.~Abebe, S.~Barocas, J.~Kleinberg, K.~Levy, M.~Raghavan, and D.~G. Robinson,
  ``Roles for computing in social change,'' in \emph{Proceedings of the 2020
  Conference on Fairness, Accountability, and Transparency}, 2020, pp.
  252--260.

\bibitem{stoyan}
J.~Stoyanovich, B.~Howe, S.~Abiteboul, G.~Miklau, A.~Sahuguet, and G.~Weikum,
  ``Fides: Towards a platform for responsible data science,'' in
  \emph{Proceedings of the 29th International Conference on Scientific and
  Statistical Database Management}, 2017.

\bibitem{gotterbarn2017acm}
D.~Gotterbarn, A.~Bruckman, C.~Flick, K.~Miller, and M.~J. Wolf, ``{ACM code of
  ethics: a guide for positive action},'' \emph{Communications of the ACM},
  vol.~61, no.~1, pp. 121--128, 2017.

\bibitem{bloomberg}
L.~Erickson, N.~Evans~Harris, and M.~M. Lee, ``It's time for data ethics
  conversations at your dinner table,'' \emph{Tech at Bloomberg}, 2018.

\bibitem{EthicalOS}
\BIBentryALTinterwordspacing
{Omidyar Network and the Institute for the Future}, ``The ethical operating
  system.'' [Online]. Available: \url{https://ethicalos.org/}
\BIBentrySTDinterwordspacing

\bibitem{Guidebook}
\BIBentryALTinterwordspacing
N.~Evans~Harris, ``Sharing data for social impact: Guidebook to establishing
  responsible governance practices.'' [Online]. Available:
  \url{https://beeckcenter.georgetown.edu/wp-content/uploads/2020/01/Data-Sharing-Report.pdf}
\BIBentrySTDinterwordspacing

\bibitem{le2020temporary}
C.~Le~Qu{\'e}r{\'e}~et al., ``{Temporary reduction in daily global CO2
  emissions during the COVID-19 forced confinement},'' \emph{Nature Climate
  Change}, pp. 1--7, 2020.

\bibitem{UCBinterview}
\BIBentryALTinterwordspacing
E.~Lempinen, ``The pandemic could open a door to new technology — and
  dramatic innovation — in education,'' 2020. [Online]. Available:
  \url{http://web.archive.org/web/20200530235421/https://news.berkeley.edu/2020/05/27/the-pandemic-could-open-a-door-to-new-technology-and-dramatic-innovation-in-education/}
\BIBentrySTDinterwordspacing

\bibitem{Jenna}
\BIBentryALTinterwordspacing
J.~Burrell, ``{The value of the internet to rural populations: a case study
  from Mendocino County, CA},'' 2016. [Online]. Available:
  \url{https://web.archive.org/web/20200530234610/http://www.mendocinobroadband.org/wp-content/uploads/Jenna-Rural-Internet-Report.pdf}
\BIBentrySTDinterwordspacing

\bibitem{Pardos}
\BIBentryALTinterwordspacing
Z.~Pardos, ``{What to look for in online learning apps for K-12},'' 2020.
  [Online]. Available:
  \url{http://web.archive.org/web/20200530235325/https://gse.berkeley.edu/news/what-look-online-learning-apps-k-12}
\BIBentrySTDinterwordspacing

\bibitem{unesco}
\BIBentryALTinterwordspacing
{United Nations Educational Scientific and Cultural Organization}, ``Supporting
  learning and knowledge sharing through open educational resources,'' 2020.
  [Online]. Available:
  \url{http://web.archive.org/web/20200511005825/https://en.unesco.org/sites/default/files/covid19_joint_oer_call_en.pdf}
\BIBentrySTDinterwordspacing

\end{thebibliography}



\end{document}
