
\bibitem{AbiteboulHVBook}
Serge Abiteboul, Richard Hull, and Victor Vianu.
\newblock {\em Foundations of Databases}.
\newblock Addison-Wesley, 1995.

\bibitem{ainy2015approximated}
Eleanor Ainy, Pierre Bourhis, Susan~B Davidson, Daniel Deutch, and Tova Milo.
\newblock Approximated summarization of data provenance.
\newblock In {\em Proceedings of the 24th ACM International on Conference on
  Information and Knowledge Management}, pages 483--492. ACM, 2015.

\bibitem{antenucci2018constraint}
Dolan Antenucci and Michael Cafarella.
\newblock Constraint-based explanation and repair of filter-based
  transformations.
\newblock {\em Proceedings of the VLDB Endowment}, 11(9):947--960, 2018.

\bibitem{avin2005identifiability}
Chen Avin, Ilya Shpitser, and Judea Pearl.
\newblock Identifiability of path-specific effects.
\newblock In {\em Proceedings of International Joint Conference on Artificial
  Intelligence}, pages 357--363, 2005.

\bibitem{bertossi2017causes}
Leopoldo Bertossi and Babak Salimi.
\newblock Causes for query answers from databases: Datalog abduction,
  view-updates, and integrity constraints.
\newblock {\em International Journal of Approximate Reasoning}, 90:226--252,
  2017.

\bibitem{DBLP:series/synthesis/2011Bertossi}
Leopoldo~E. Bertossi.
\newblock {\em Database Repairing and Consistent Query Answering}.
\newblock Synthesis Lectures on Data Management. Morgan {\&} Claypool
  Publishers, 2011.

\bibitem{calders2009building}
Toon Calders, Faisal Kamiran, and Mykola Pechenizkiy.
\newblock Building classifiers with independency constraints.
\newblock In {\em Data mining workshops, 2009. ICDMW'09. IEEE international
  conference on}, pages 13--18. IEEE, 2009.

\bibitem{chapman2009not}
Adriane Chapman and HV~Jagadish.
\newblock Why not?
\newblock In {\em Proceedings of the 2009 ACM SIGMOD International Conference
  on Management of data}, pages 523--534. ACM, 2009.

\bibitem{chouldechova2017fair}
Alexandra Chouldechova.
\newblock Fair prediction with disparate impact: A study of bias in recidivism
  prediction instruments.
\newblock {\em Big data}, 5(2):153--163, 2017.

\bibitem{corbett2017algorithmic}
Sam Corbett-Davies, Emma Pierson, Avi Feller, Sharad Goel, and Aziz Huq.
\newblock Algorithmic decision making and the cost of fairness.
\newblock In {\em Proceedings of the 23rd ACM SIGKDD International Conference
  on Knowledge Discovery and Data Mining}, pages 797--806. ACM, 2017.

\bibitem{courtland2018bias}
Rachel Courtland.
\newblock Bias detectives: the researchers striving to make algorithms fair.
\newblock {\em Nature}, 558, 2018.

\bibitem{dwork2012fairness}
Cynthia Dwork, Moritz Hardt, Toniann Pitassi, Omer Reingold, and Richard Zemel.
\newblock Fairness through awareness.
\newblock In {\em Proceedings of the 3rd innovations in theoretical computer
  science conference}, pages 214--226. ACM, 2012.

\bibitem{galhotra2017fairness}
Sainyam Galhotra, Yuriy Brun, and Alexandra Meliou.
\newblock Fairness testing: testing software for discrimination.
\newblock In {\em Proceedings of the 2017 11th Joint Meeting on Foundations of
  Software Engineering}, pages 498--510. ACM, 2017.

\bibitem{glavic2007data}
Boris Glavic and Klaus Dittrich.
\newblock Data provenance: A categorization of existing approaches.
\newblock {\em Datenbanksysteme in Business, Technologie und Web (BTW
  2007)--12. Fachtagung des GI-Fachbereichs" Datenbanken und
  Informationssysteme"(DBIS)}, 2007.

\bibitem{hardt2016equality}
Moritz Hardt, Eric Price, Nati Srebro, et~al.
\newblock Equality of opportunity in supervised learning.
\newblock In {\em Advances in neural information processing systems}, pages
  3315--3323, 2016.

\bibitem{kilbertus2017avoiding}
Niki Kilbertus, Mateo~Rojas Carulla, Giambattista Parascandolo, Moritz Hardt,
  Dominik Janzing, and Bernhard Sch{\"o}lkopf.
\newblock Avoiding discrimination through causal reasoning.
\newblock In {\em Advances in Neural Information Processing Systems}, pages
  656--666, 2017.

\bibitem{kusner2017counterfactual}
Matt~J Kusner, Joshua Loftus, Chris Russell, and Ricardo Silva.
\newblock Counterfactual fairness.
\newblock In {\em Advances in Neural Information Processing Systems}, pages
  4069--4079, 2017.

\bibitem{larson2016we}
Jeff Larson, Surya Mattu, Lauren Kirchner, and Julia Angwin.
\newblock How we analyzed the compas recidivism algorithm.
\newblock {\em ProPublica (5 2016)}, 9, 2016.

\bibitem{DBLP:conf/pods/LevyMSS95}
Alon~Y. Levy, Alberto~O. Mendelzon, Yehoshua Sagiv, and Divesh Srivastava.
\newblock Answering queries using views.
\newblock In {\em Proceedings of the Fourteenth {ACM} {SIGACT-SIGMOD-SIGART}
  Symposium on Principles of Database Systems, May 22-25, 1995, San Jose,
  California, {USA}}, pages 95--104, 1995.

\bibitem{adult}
M.~Lichman.
\newblock Uci machine learning repository, 2013.

\bibitem{DBLP:conf/pods/LivshitsKR18}
Ester Livshits, Benny Kimelfeld, and Sudeepa Roy.
\newblock Computing optimal repairs for functional dependencies.
\newblock In {\em Proceedings of the 37th {ACM} {SIGMOD-SIGACT-SIGAI} Symposium
  on Principles of Database Systems, Houston, TX, USA, June 10-15, 2018}, pages
  225--237, 2018.

\bibitem{loftus2018causal}
Joshua~R Loftus, Chris Russell, Matt~J Kusner, and Ricardo Silva.
\newblock Causal reasoning for algorithmic fairness.
\newblock {\em CoRR}, abs/1805.05859, 2018.

\bibitem{meliou2010complexity}
Alexandra Meliou, Wolfgang Gatterbauer, Katherine~F Moore, and Dan Suciu.
\newblock The complexity of causality and responsibility for query answers and
  non-answers.
\newblock {\em Proceedings of the VLDB Endowment}, 4(1):34--45, 2010.

\bibitem{mintz2009distant}
Mike Mintz, Steven Bills, Rion Snow, and Dan Jurafsky.
\newblock Distant supervision for relation extraction without labeled data.
\newblock In {\em Proceedings of the Joint Conference of the 47th Annual
  Meeting of the ACL and the 4th International Joint Conference on Natural
  Language Processing of the AFNLP: Volume 2-Volume 2}, pages 1003--1011.
  Association for Computational Linguistics, 2009.

\bibitem{nabi2018fair}
Razieh Nabi and Ilya Shpitser.
\newblock Fair inference on outcomes.
\newblock In {\em Proceedings of the... AAAI Conference on Artificial
  Intelligence. AAAI Conference on Artificial Intelligence}, volume 2018, page
  1931. NIH Public Access, 2018.

\bibitem{pearl2003causality}
Judea Pearl.
\newblock Causality: models, reasoning, and inference.
\newblock {\em Econometric Theory}, 19(675-685):46, 2003.

\bibitem{pearl2009causality}
Judea Pearl.
\newblock {\em Causality}.
\newblock Cambridge university press, 2009.

\bibitem{pearl2009causal}
Judea Pearl et~al.
\newblock Causal inference in statistics: An overview.
\newblock {\em Statistics Surveys}, 3:96--146, 2009.

\bibitem{DBLP:conf/sigmod/PopaDST00}
Lucian Popa, Alin Deutsch, Arnaud Sahuguet, and Val Tannen.
\newblock A chase too far?
\newblock In {\em Proceedings of the 2000 {ACM} {SIGMOD} International
  Conference on Management of Data, May 16-18, 2000, Dallas, Texas, {USA.}},
  pages 273--284, 2000.

\bibitem{ratner2017snorkel}
Alexander Ratner, Stephen~H Bach, Henry Ehrenberg, Jason Fries, Sen Wu, and
  Christopher R{\'e}.
\newblock Snorkel: Rapid training data creation with weak supervision.
\newblock {\em Proceedings of the VLDB Endowment}, 11(3):269--282, 2017.

\bibitem{ratner2016data}
Alexander~J Ratner, Christopher~M De~Sa, Sen Wu, Daniel Selsam, and Christopher
  R{\'e}.
\newblock Data programming: Creating large training sets, quickly.
\newblock In {\em Advances in neural information processing systems}, pages
  3567--3575, 2016.

\bibitem{raykar2010learning}
Vikas~C Raykar, Shipeng Yu, Linda~H Zhao, Gerardo~Hermosillo Valadez, Charles
  Florin, Luca Bogoni, and Linda Moy.
\newblock Learning from crowds.
\newblock {\em Journal of Machine Learning Research}, 11(Apr):1297--1322, 2010.

\bibitem{roy2014formal}
Sudeepa Roy and Dan Suciu.
\newblock A formal approach to finding explanations for database queries.
\newblock In {\em Proceedings of the 2014 ACM SIGMOD international conference
  on Management of data}, pages 1579--1590. ACM, 2014.

\bibitem{rubin1970thesis}
Donald~B Rubin.
\newblock {\em The Use of Matched Sampling and Regression Adjustment in
  Observational Studies}.
\newblock Ph.D. Thesis, Department of Statistics, Harvard University,
  Cambridge, MA, 1970.

\bibitem{rubin1986statistics}
Donald~B Rubin.
\newblock Statistics and causal inference: Comment: Which ifs have causal
  answers.
\newblock {\em Journal of the American Statistical Association},
  81(396):961--962, 1986.

\bibitem{rubin2008comment}
Donald~B Rubin.
\newblock Comment: The design and analysis of gold standard randomized
  experiments.
\newblock {\em Journal of the American Statistical Association},
  103(484):1350--1353, 2008.

\bibitem{russell2017worlds}
Chris Russell, Matt~J Kusner, Joshua Loftus, and Ricardo Silva.
\newblock When worlds collide: integrating different counterfactual assumptions
  in fairness.
\newblock In {\em Advances in Neural Information Processing Systems}, pages
  6414--6423, 2017.

\bibitem{DBLP:conf/icdt/SalimiB15}
Babak Salimi and Leopoldo~E. Bertossi.
\newblock From causes for database queries to repairs and model-based diagnosis
  and back.
\newblock In {\em ICDT}, pages 342--362, 2015.

\bibitem{salimi2016quantifying}
Babak Salimi, Leopoldo~E Bertossi, Dan Suciu, and Guy Van~den Broeck.
\newblock Quantifying causal effects on query answering in databases.
\newblock In {\em TaPP}, 2016.

\bibitem{salimi2018hypdb}
Babak Salimi, Corey Cole, Peter Li, Johannes Gehrke, and Dan Suciu.
\newblock Hypdb: a demonstration of detecting, explaining and resolving bias in
  olap queries.
\newblock {\em Proceedings of the VLDB Endowment}, 11(12):2062--2065, 2018.

\bibitem{salimi2018bias}
Babak Salimi, Johannes Gehrke, and Dan Suciu.
\newblock Bias in olap queries: Detection, explanation, and removal.
\newblock In {\em Proceedings of the 2018 International Conference on
  Management of Data}, pages 1021--1035. ACM, 2018.

\bibitem{salimi2019capuchin}
Babak Salimi, Luke Rodriguez, Bill Howe, and Dan Suciu.
\newblock Capuchin: Causal database repair for algorithmic fairness.
\newblock {\em CoRR}, abs/1902.08283, 2019.

\bibitem{salimi2019interventional}
Babak Salimi, Luke Rodriguez, Bill Howe, and Dan Suciu.
\newblock Interventional fairness: Causal database repair for algorithmic
  fairness.
\newblock In {\em Proceedings of the 2019 International Conference on
  Management of Data}, pages 793--810. ACM, 2019.

\bibitem{simoiu2017problem}
Camelia Simoiu, Sam Corbett-Davies, Sharad Goel, et~al.
\newblock The problem of infra-marginality in outcome tests for discrimination.
\newblock {\em The Annals of Applied Statistics}, 11(3):1193--1216, 2017.

\bibitem{verma2018fairness}
Sahil Verma and Julia Rubin.
\newblock Fairness definitions explained.
\newblock In {\em 2018 IEEE/ACM International Workshop on Software Fairness
  (FairWare)}, pages 1--7. IEEE, 2018.

\bibitem{xu2018provenance}
Jane Xu, Waley Zhang, Abdussalam Alawini, and Val Tannen.
\newblock Provenance analysis for missing answers and integrity repairs.
\newblock {\em IEEE Data Eng. Bull.}, 41(1):39--50, 2018.

\bibitem{zafar2017fairness}
Muhammad~Bilal Zafar, Isabel Valera, Manuel Gomez~Rodriguez, and Krishna~P
  Gummadi.
\newblock Fairness beyond disparate treatment \& disparate impact: Learning
  classification without disparate mistreatment.
\newblock In {\em Proceedings of the 26th International Conference on World
  Wide Web}, pages 1171--1180. International World Wide Web Conferences
  Steering Committee, 2017.

\bibitem{zliobaite2015survey2}
Indre Zliobaite.
\newblock A survey on measuring indirect discrimination in machine learning.
\newblock {\em CoRR}, abs/1511.00148, 2015.

