\documentclass[11pt]{article}

\usepackage{deauthor}

\usepackage{upmathgrad2}
\usepackage{UPnotations}

\usepackage{pifont}
\usepackage{amsmath,bm}
\usepackage{amsthm}
\usepackage{bbm}
\usepackage{caption}
\usepackage{amsthm}
\usepackage{pifont}
%\usepackage[ruled,linesnumbered]{algorithm2e}


\newtheorem{definitionnew}{Definition}[section]
\newtheorem{assumption}{Assumption}
\usepackage{wrapfig}
\def\dname{CMLP}
\usepackage{graphicx}
\usepackage{cite}
\usepackage{wrapfig}
\usepackage{tabu}
% \urlstyle{same}
\usepackage{xcolor}
\usepackage{stfloats}
% new package
\usepackage{multirow,fixltx2e}
\usepackage{caption}
\usepackage{float}
\usepackage{microtype}
\usepackage{makecell}
\usepackage{booktabs}


%\newlength\savewidth\newcommand\shline{\noalign{\global\savewidth\arrayrulewidth
%  \global\arrayrulewidth 1pt}\hline\noalign{\global\arrayrulewidth\savewidth}}

\begin{document}
\title{Distilling Causal Metaknowledge from Knowledge Graphs}

% \author{Yuan Meng$^1$, Yancheng Dong$^1$, Shixuan Liu$^2$, Xinzhu Ma$^3$, Chaohao Yuan$^1$, Yue He$^1$, Furui Liu$^4$, Pei Jian$^5$, Peng Cui$^1$}
% \email{{yuanmeng, dongyc20, yuanch22, heyue18 }@mails.tsinghua.edu.cn,
% liushixuan@nudt.edu.cn
% }
% \email{xinzhu.ma@sydney.edu.au, 104256204@qq.com,  jpei@cs.sfu.ca,  cuip@tsinghua.edu.cn}
% \affiliation{$^1$ Tsinghua University $^2$National University of Defense Technology
% \\  $^3$ The University of Sydney  $^4$ Huawei Technologies Ltd.  $^5$ Simon Fraser University}

\author{Yuan Meng, Yancheng Dong, Shixuan Liu, Chaohao Yuan, Yue He, Jian Pei, Peng Cui}% <-this % stops a space
% \email{{yuanmeng, dongyc20, yuanch22, heyue18 }@mails.tsinghua.edu.cn,
% liushixuan@nudt.edu.cn
% }%
% \email{xinzhu.ma@sydney.edu.au, 104256204@qq.com,  jpei@cs.sfu.ca,  cuip@tsinghua.edu.cn}%
% \affiliation{$^1$ Tsinghua University $^2$National University of Defense Technology
% \\  $^3$ The University of Sydney  $^4$ Huawei Technologies Ltd.  $^5$ Simon Fraser University}
% \thanks{Yuan Meng, Yancheng Dong, Chaohao Yuan, Yue He and Peng Cui  are with  Tsinghua University.}% <-this % stops a space
% \thanks{Shixuan Liu is with  National University of Defense Technology.}
% \thanks{Xinzhu Ma is with  the University of Sydney.}
% \thanks{Furui Liu is with  Huawei Technologies Ltd.}
% \thanks{Pei Jian is with Duke University}
% \thanks{J. Doe and J. Doe are with Anonymous University.}% <-this % stops a space
% \thanks{Manuscript received April 19, 2005; revised August 26, 2015.}}



\maketitle

\begin{abstract}
\input{submissions/causal-meta-knowledge/abstract.tex}
\end{abstract}


\section{Introduction}
\label{section:introduction}
\input{submissions/causal-meta-knowledge/introduction.tex}






\section{Preliminaries and Problem Statement}
\label{section:model}
\input{submissions/causal-meta-knowledge/pre.tex}


% introduce the representation
% \section{Structural Causal Knowledge Model}

\section{Proposed Method: ~\dname}
\label{section:model}
\input{submissions/causal-meta-knowledge/model.tex}


\section{Experimental Study}
\label{section:experiment}
\input{submissions/causal-meta-knowledge/experiment.tex}

\section{Related Work}
\label{section:related}
\input{submissions/causal-meta-knowledge/related.tex}

\section{Conclusion and Future work}
\label{section:conclusion}
\input{submissions/causal-meta-knowledge/conclusion.tex}


%\bibliographystyle{plain}
%\bibliography{submissions/causal-meta-knowledge/sample}

\begin{thebibliography}{10}

\bibitem{10.1214/ss/1177009870}
John Aldrich.
\newblock {Correlations Genuine and Spurious in Pearson and Yule}.
\newblock {\em Statistical Science}, 10(4):364 -- 376, 1995.

\bibitem{balazevic2019tucker}
Ivana Bala\v{z}evi\'c, Carl Allen, and Timothy~M Hospedales.
\newblock Tucker: Tensor factorization for knowledge graph completion.
\newblock In {\em Empirical Methods in Natural Language Processing}, 2019.

\bibitem{bordes2013translating}
Antoine Bordes, Nicolas Usunier, Alberto Garcia-Duran, Jason Weston, and Oksana
  Yakhnenko.
\newblock Translating embeddings for modeling multi-relational data.
\newblock {\em Advances in neural information processing systems}, 26, 2013.

\bibitem{chen2022fuzzy}
Xuelu Chen, Ziniu Hu, and Yizhou Sun.
\newblock Fuzzy logic based logical query answering on knowledge graphs.
\newblock In {\em Proceedings of the AAAI Conference on Artificial
  Intelligence}, volume~36, pages 3939--3948, 2022.

\bibitem{cui2011based}
Xiao Cui and Hao Shi.
\newblock A*-based pathfinding in modern computer games.
\newblock {\em International Journal of Computer Science and Network Security},
  2011.

\bibitem{evans2011metaknowledge}
James~A Evans and Jacob~G Foster.
\newblock Metaknowledge.
\newblock {\em Science}, 2011.

\bibitem{fortunato2018science}
Santo Fortunato, Carl~T Bergstrom, Katy B{\"o}rner, James~A Evans, Dirk
  Helbing, Sta{\v{s}}a Milojevi{\'c}, Alexander~M Petersen, Filippo Radicchi,
  Roberta Sinatra, Brian Uzzi, et~al.
\newblock Science of science.
\newblock {\em Science}, 2018.

\bibitem{galarraga2015fast}
Luis Gal{\'a}rraga, Christina Teflioudi, Katja Hose, and Fabian~M Suchanek.
\newblock Fast rule mining in ontological knowledge bases with amie.
\newblock {\em The VLDB Journal}, 24(6):707--730, 2015.

\bibitem{galarraga2013amie}
Luis~Antonio Gal{\'a}rraga, Christina Teflioudi, Katja Hose, and Fabian
  Suchanek.
\newblock Amie: association rule mining under incomplete evidence in
  ontological knowledge bases.
\newblock In {\em Proceedings of the 22nd international conference on World
  Wide Web}, pages 413--422, 2013.

\bibitem{galarraga_amie_2013}
Luis~Antonio Galárraga, Christina Teflioudi, Katja Hose, and Fabian Suchanek.
\newblock {AMIE}: association rule mining under incomplete evidence in
  ontological knowledge bases.
\newblock In {\em Proceedings of the 22nd international conference on World
  Wide Web - {WWW} '13}, pages 413--422. {ACM} Press.

\bibitem{gerhardus2020high}
Andreas Gerhardus and Jakob Runge.
\newblock High-recall causal discovery for autocorrelated time series with
  latent confounders.
\newblock {\em Advances in Neural Information Processing Systems},
  33:12615--12625, 2020.

\bibitem{giudice2022dual}
Enrico Giudice, Jack Kuipers, and Giusi Moffa.
\newblock The dual pc algorithm for structure learning.
\newblock In {\em International Conference on Probabilistic Graphical Models},
  pages 301--312. PMLR, 2022.

\bibitem{glymour2016causal}
Madelyn Glymour, Judea Pearl, and Nicholas~P Jewell.
\newblock {\em Causal inference in statistics: A primer}.
\newblock John Wiley \& Sons, 2016.

\bibitem{heusner2018best}
Manuel Heusner, Thomas Keller, and Malte Helmert.
\newblock Best-case and worst-case behavior of greedy best-first search.
\newblock International Joint Conferences on Artificial Intelligence, 2018.

\bibitem{himmelstein2017systematic}
Daniel~Scott Himmelstein, Antoine Lizee, Christine Hessler, Leo Brueggeman,
  Sabrina~L Chen, Dexter Hadley, Ari Green, Pouya Khankhanian, and Sergio~E
  Baranzini.
\newblock Systematic integration of biomedical knowledge prioritizes drugs for
  repurposing.
\newblock {\em Elife}, 6:e26726, 2017.

\bibitem{imbens2010rubin}
Guido~W Imbens and Donald~B Rubin.
\newblock Rubin causal model.
\newblock In {\em Microeconometrics}, pages 229--241. Springer, 2010.

\bibitem{ji2021survey}
Shaoxiong Ji, Shirui Pan, Erik Cambria, Pekka Marttinen, and S~Yu Philip.
\newblock A survey on knowledge graphs: Representation, acquisition, and
  applications.
\newblock {\em IEEE Transactions on Neural Networks and Learning Systems},
  33(2):494--514, 2021.

\bibitem{lanning2014dijkstra}
Daniel~R Lanning, Gregory~K Harrell, and Jin Wang.
\newblock Dijkstra's algorithm and google maps.
\newblock In {\em Proceedings of the 2014 ACM Southeast Regional Conference},
  2014.

\bibitem{le2016fast}
Thuc~Duy Le, Tao Hoang, Jiuyong Li, Lin Liu, Huawen Liu, and Shu Hu.
\newblock A fast pc algorithm for high dimensional causal discovery with
  multi-core pcs.
\newblock {\em IEEE/ACM transactions on computational biology and
  bioinformatics}, 16(5):1483--1495, 2016.

\bibitem{lee2016learning}
Sanghack Lee and Vasant Honavar.
\newblock On learning causal models from relational data.
\newblock In {\em Thirtieth AAAI Conference on Artificial Intelligence}, 2016.

\bibitem{lee2020towards}
Sanghack Lee and Vasant Honavar.
\newblock Towards robust relational causal discovery.
\newblock In {\em Uncertainty in Artificial Intelligence}. PMLR, 2020.

\bibitem{li2021kg4vis}
Haotian Li, Yong Wang, Songheng Zhang, Yangqiu Song, and Huamin Qu.
\newblock Kg4vis: A knowledge graph-based approach for visualization
  recommendation.
\newblock {\em IEEE Transactions on Visualization and Computer Graphics},
  28(1):195--205, 2021.

\bibitem{lin2021multi}
Zizheng Lin, Haowen Ke, Ngo-Yin Wong, Jiaxin Bai, Yangqiu Song, Huan Zhao, and
  Junpeng Ye.
\newblock Multi-relational graph based heterogeneous multi-task learning in
  community question answering.
\newblock In {\em Proceedings of the 30th ACM International Conference on
  Information \& Knowledge Management}, pages 1038--1047, 2021.

\bibitem{maier2013sound}
Marc Maier, Katerina Marazopoulou, David Arbour, and David Jensen.
\newblock A sound and complete algorithm for learning causal models from
  relational data.
\newblock In {\em Uncertainty in Artificial Intelligence}, page 371. Citeseer,
  2013.

\bibitem{maier2010learning}
Marc Maier, Brian Taylor, Huseyin Oktay, and David Jensen.
\newblock Learning causal models of relational domains.
\newblock In {\em Proceedings of the AAAI Conference on Artificial
  Intelligence}, 2010.

\bibitem{marx2019testing}
Alexander Marx and Jilles Vreeken.
\newblock Testing conditional independence on discrete data using stochastic
  complexity.
\newblock In {\em The 22nd International Conference on Artificial Intelligence
  and Statistics}, 2019.

\bibitem{meilicke2019anytime}
Christian Meilicke, Melisachew~Wudage Chekol, Daniel Ruffinelli, and Heiner
  Stuckenschmidt.
\newblock Anytime bottom-up rule learning for knowledge graph completion.
\newblock In {\em IJCAI}, pages 3137--3143, 2019.

\bibitem{omran2019embedding}
Pouya~Ghiasnezhad Omran, Kewen Wang, and Zhe Wang.
\newblock An embedding-based approach to rule learning in knowledge graphs.
\newblock {\em IEEE Transactions on Knowledge and Data Engineering}, 2019.

\bibitem{pearl2010causal}
Judea Pearl.
\newblock Causal inference.
\newblock {\em Causality: Objectives and Assessment}, pages 39--58, 2010.

\bibitem{qu2020rnnlogic}
Meng Qu, Junkun Chen, Louis-Pascal Xhonneux, Yoshua Bengio, and Jian Tang.
\newblock Rnnlogic: Learning logic rules for reasoning on knowledge graphs.
\newblock In {\em International Conference on Learning Representations}, 2021.

\bibitem{ratajczak2022task}
Florin Ratajczak, Mitchell Joblin, Martin Ringsquandl, and Marcel Hildebrandt.
\newblock Task-driven knowledge graph filtering improves prioritizing drugs for
  repurposing.
\newblock {\em BMC bioinformatics}, 23(1):1--19, 2022.

\bibitem{rossi2021knowledge}
Andrea Rossi, Denilson Barbosa, Donatella Firmani, Antonio Matinata, and Paolo
  Merialdo.
\newblock Knowledge graph embedding for link prediction: A comparative
  analysis.
\newblock {\em ACM Transactions on Knowledge Discovery from Data (TKDD)},
  15(2):1--49, 2021.

\bibitem{ruffinelli2020you}
Daniel Ruffinelli, Samuel Broscheit, and Rainer Gemulla.
\newblock You can teach an old dog new tricks! on training knowledge graph
  embeddings.
\newblock 2020.

\bibitem{sadeghian2019drum}
Ali Sadeghian, Mohammadreza Armandpour, Patrick Ding, and Daisy~Zhe Wang.
\newblock Drum: End-to-end differentiable rule mining on knowledge graphs.
\newblock {\em Advances in Neural Information Processing Systems}, 32, 2019.

\bibitem{salimi2020causal}
Babak Salimi, Harsh Parikh, Moe Kayali, Lise Getoor, Sudeepa Roy, and Dan
  Suciu.
\newblock Causal relational learning.
\newblock In {\em Proceedings of the 2020 ACM SIGMOD International Conference
  on Management of Data}, 2020.

\bibitem{sondhi2019reduced}
Arjun Sondhi and Ali Shojaie.
\newblock The reduced pc-algorithm: Improved causal structure learning in large
  random networks.
\newblock {\em J. Mach. Learn. Res.}, 20(164):1--31, 2019.

\bibitem{spirtes2000causation}
Peter Spirtes, Clark~N Glymour, Richard Scheines, and David Heckerman.
\newblock {\em Causation, prediction, and search}.
\newblock MIT press, 2000.

\bibitem{tang2020investigating}
Xianfeng Tang, Huaxiu Yao, Yiwei Sun, Yiqi Wang, Jiliang Tang, Charu Aggarwal,
  Prasenjit Mitra, and Suhang Wang.
\newblock Investigating and mitigating degree-related biases in graph
  convoltuional networks.
\newblock In {\em Proceedings of the 29th ACM International Conference on
  Information \& Knowledge Management}, pages 1435--1444, 2020.

\bibitem{tiwari2021revisiting}
Sudhanshu Tiwari, Iti Bansal, and Carlos~R Rivero.
\newblock Revisiting the evaluation protocol of knowledge graph completion
  methods for link prediction.
\newblock In {\em Proceedings of the Web Conference 2021}, pages 809--820,
  2021.

\bibitem{wang2019multi}
Hongwei Wang, Fuzheng Zhang, Miao Zhao, Wenjie Li, Xing Xie, and Minyi Guo.
\newblock Multi-task feature learning for knowledge graph enhanced
  recommendation.
\newblock In {\em The World Wide Web Conference}, 2019.

\bibitem{wang2019kgat}
Xiang Wang, Xiangnan He, Yixin Cao, Meng Liu, and Tat-Seng Chua.
\newblock Kgat: Knowledge graph attention network for recommendation.
\newblock In {\em Proceedings of the 25th ACM SIGKDD International Conference
  on Knowledge Discovery \& Data Mining}, 2019.

\bibitem{wang2021benchmarking}
Zihao Wang, Hang Yin, and Yangqiu Song.
\newblock Benchmarking the combinatorial generalizability of complex query
  answering on knowledge graphs.
\newblock In {\em NeurIPS Datasets and Benchmarks Track}, 2021.

\bibitem{wu2021self}
Jiancan Wu, Xiang Wang, Fuli Feng, Xiangnan He, Liang Chen, Jianxun Lian, and
  Xing Xie.
\newblock Self-supervised graph learning for recommendation.
\newblock In {\em Proceedings of the 44th international ACM SIGIR conference on
  research and development in information retrieval}, pages 726--735, 2021.

\bibitem{yang2017differentiable}
Fan Yang, Zhilin Yang, and William~W Cohen.
\newblock Differentiable learning of logical rules for knowledge base
  reasoning.
\newblock {\em Advances in neural information processing systems}, 30, 2017.

\bibitem{zhang2020aser}
Hongming Zhang, Xin Liu, Haojie Pan, Yangqiu Song, and Cane Wing-Ki Leung.
\newblock Aser: A large-scale eventuality knowledge graph.
\newblock In {\em Proceedings of the web conference 2020}, pages 201--211,
  2020.

\bibitem{zheng2018dags}
Xun Zheng, Bryon Aragam, Pradeep Ravikumar, and Eric~P. Xing.
\newblock {DAGs with NO TEARS: Continuous Optimization for Structure Learning}.
\newblock In {\em Advances in Neural Information Processing Systems}, 2018.

\bibitem{zheng2020learning}
Xun Zheng, Chen Dan, Bryon Aragam, Pradeep Ravikumar, and Eric~P. Xing.
\newblock {Learning sparse nonparametric DAGs}.
\newblock In {\em International Conference on Artificial Intelligence and
  Statistics}, 2020.

\end{thebibliography}

\end{document}

