\documentclass{article}
%\usepackage[utf8]{inputenc}
\usepackage{fullpage}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{subfigure}
\usepackage{tabularx}
%\usepackage{url}
\usepackage{times}  % DO NOT CHANGE THIS
\usepackage{helvet}  % DO NOT CHANGE THIS
\usepackage{courier}  % DO NOT CHANGE THIS
%\usepackage[hyphens]{url}  % DO NOT CHANGE THIS
\usepackage{subcaption}
\usepackage{graphicx}
\urlstyle{rm} % DO NOT CHANGE THIS
\def\UrlFont{\rm}  % DO NOT CHANGE THIS
\usepackage{natbib}  % DO NOT CHANGE THIS AND DO NOT ADD ANY OPTIONS TO IT
\usepackage{caption} % DO NOT CHANGE THIS AND DO NOT ADD ANY OPTIONS TO IT
\usepackage{algorithm}
\usepackage{algorithmic}
%\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{verbatim}
\newcommand{\eqr}{\ensuremath{P(L_{\epsilon}(Q(D))}}
\begin{document}

%\title{Welcome Letter from IEEE TCDE Chair}
%\author{Murat Kantarcioglu \thanks{ muratk@utdallas.edu, University of Texas at Dallas and Harvard University}}
%\date{}
%\maketitle

As the recent research trends indicate, tracking, storing and analyzing “big data” may result in significant value gains in a wide range of domains, from health care to government services. Still, several critical issues need to be addressed to capture the full potential of big data, from building accountable and transparent data management systems to ensuring data privacy. Clearly, IEEE Technical Community of Data Engineering (TCDE) could play an instrumental role in addressing these fundamental challenges, thereby further contributing to achieving the goals of the big data revolution. As the new TCDE chair, with the help of TCDE Executive committee and our community members, I hope to start a number of new initiatives in the following areas:
\begin{itemize}
\item \textbf{Data Engineering for Social Good:} As data storage, management and analytics are the fundamental building blocks for many different areas ranging from ML to bioinformatics, a wider range of interdisciplinary activities could be organized by TCDE with other stakeholders. One area that we could be looking at is to create specific activities for “Data Engineering for Social Good” and showcase the research coming out of the TCDE community on addressing important societal challenges. For example, as a researcher that works on data security and privacy issues,  I would be very interested in exhibiting important tools and techniques built by our community that help to address important data privacy challenges. In the coming months, we would be looking into investing into such interdisciplinary activities. Please reach out to me if you have some ideas.

\item \textbf{Increase Diversity, Equity and Inclusion (D\&I):} Another important challenge that we plan to focus on is to increase the diversity and inclusion of the future data engineering workforce. As a faculty member, I actively work on multiple initiatives to promote diversity and an inclusive atmosphere in my research group and actively reach out to underrepresented groups via activities such as women in data science and university clubs. TCDE could sponsor specific activities such as mentorship programs for underrepresented groups and build mechanisms to gather feedback from the community to increase the diversity and inclusion. Our efforts could be expanded to include not only undergrad and graduate students but also high school students, particularly, from disadvantaged backgrounds. Specific fund raising activities and corporate sponsorships could be arranged to fund workshops and hackathons for high school students. In particular, we should be looking into new D\&I initiatives that help the broader community and extend beyond a set of activities in a single conference. Again, we would appreciate new D\&I activity ideas and suggestions.

\item \textbf{New Bi-monthly Newsletter, and Web Page:} Given all the great things done in our community,  we should promote some of the important initiatives and ideas more. We plan to have a new website for TCDE that has information about all the ongoing activities and resources. In addition, we will be launching a bi-monthly newsletter that highlights important news items, ongoing initiatives and upcoming opportunities for our community. You would be able to get this newsletter if you are a member of TCDE (if not, please become a member, it is FREE).
\end{itemize}
Clearly, without active support of the TCDE community, many of the above ideas and/or other initiatives will not be successful. It is clear that getting the feedback of the entire community from around the world would be important to make the TCDE even more relevant and successful in the future. To achieve this goal, in addition to attending ICDE conference every year, I plan to visit IEEE local chapters and colleagues around the world and understand their needs and suggestions. If you see me at a conference or an event, please come say hi and share your feedback about these initiatives.  I would also be happy to receive any feedback by email.

I am looking forward to working with you all to increase the TCDE profile over the years.
\end{document}
