% !TEX root=../../deissue.tex 


% 1 Introduction:

% 1.1 Describe challenges of COVID-19.

% 1.2 How to address these challenges. 

% 1.3 A data-science pipeline. Data discovery, data integration and cleaning, automatic visualization, efficient tracking and searching (china mobile), trend prediction/search

% 1.4 Contributions:

% 2 System architecture

% 3 Data preparation 

% 4 Automatic Visualization.

% 5 Efficient tracking and searching å

% 6 Trend prediction

% \documentclass[11pt]{article}
% \usepackage{deauthor,times,graphicx}

\input{commands}

% \makeatletter           

\begin{document}

\title{\textsc{DeepEye}: A Data Science System for Monitoring and Exploring COVID-19 Data}

\author[${\dag}$]{Yuyu Luo}
\author[${\ddag}$]{Nan Tang}
\author[${\dag}$]{Guoliang Li}
\author[${\dag}$]{Wenbo Li}
\author[${\dag}$]{Tianyu Zhao}
\author[${\dag}$]{Xiang Yu}
\affil[${\dag}$]{Department of Computer Science, Tsinghua University}
\affil[${\ddag}$]{Qatar Computing Research Institute, HBKU}
\affil[ ]{\small \{luoyy18@mails., liguoliang@, li-wb17@mails., zhaoty17@mails., x-yu17@mails.\}tsinghua.edu.cn, ntang@hbku.edu.qa}

% \author{ \hspace{-1em} %\alignauthor 
% 	Yuyu Luo$^{\dag}$\hspace{1em}
% 	Nan Tang$^{\ddag}$\hspace{1em} 
% 	Guoliang Li$^{\dag}$\hspace{1em}
% 	Wenbo Li$^{\dag}$\hspace{1em}
% 	Tianyu Zhao$^{\dag}$\hspace{1em}
% 	Xiang Yu$^{\dag}$
% 	\\
% \affaddr{\small$^{\dag}$Department of Computer Science, Tsinghua University \hspace{2ex} $^{\ddag}$Qatar Computing Research Institute, HBKU} \\
% \hspace{-1em}
% 	{\small \{luoyy18@mails., liguoliang@, li-wb17@mails., zhaoty17@mails., x-yu17@mails.\}tsinghua.edu.cn, ntang@hbku.edu.qa}
% }


\maketitle

\input{sections/abstract}
\input{sections/introduction}
\input{sections/system}
\input{sections/dataprep}
\input{sections/descriptive}
\input{sections/diagnostic}
\input{sections/perspective}
\input{sections/conclusions}

% \bibliographystyle{abbrv}
% \bibliography{DA}  

\begin{thebibliography}{10}

\bibitem{DBLP:journals/pvldb/AbedjanCDFIOPST16}
Z.~Abedjan, X.~Chu, and et.al.
\newblock Detecting data errors: Where are we and what needs to be done?
\newblock {\em {PVLDB}}, 9(12):993--1004, 2016.

\bibitem{DBLP:conf/cidr/BinnigSKUZZ17}
C.~Binnig, L.~D. Stefani, T.~Kraska, E.~Upfal, E.~Zgraggen, and Z.~Zhao.
\newblock Toward sustainable insights, or why polygamy is bad for you.
\newblock In {\em {CIDR}}.

\bibitem{carcione2020simulation1}
J.~M. Carcione, J.~E. Santos, C.~Bagaini, and J.~Ba.
\newblock A simulation of a covid-19 epidemic based on a deterministic seir
  model.
\newblock {\em arXiv preprint arXiv:2004.03575}, 2020.

\bibitem{dong2020interactive}
E.~Dong, H.~Du, and L.~Gardner.
\newblock An interactive web-based dashboard to track covid-19 in real time.
\newblock {\em The Lancet Infectious Diseases}, 2020.

\bibitem{DBLP:journals/vi/LiMSSZWZC18}
D.~Li, H.~Mei, Y.~Shen, S.~Su, W.~Zhang, J.~Wang, M.~Zu, and W.~Chen.
\newblock Echarts: {A} declarative framework for rapid construction of
  web-based visualization.
\newblock {\em Vis. Informatics}, 2(2):136--146, 2018.

\bibitem{10.14778/3137765.3137833}
G.~Li.
\newblock Human-in-the-loop data integration.
\newblock {\em Proc. VLDB Endow.}, 10(12):2006–2017, Aug. 2017.

\bibitem{visclean-icde}
Y.~Luo, C.~Chai, X.~Qin, N.~Tang, and G.~Li.
\newblock Interactive cleaning for progressive visualization through composite
  questions.
\newblock In {\em ICDE}, 2020.

\bibitem{deepeyeicde}
Y.~Luo, X.~Qin, N.~Tang, and G.~Li.
\newblock {DeepEye: Towards Automatic Data Visualization}.
\newblock In {\em ICDE}, 2018.

\bibitem{DBLP:conf/kdd/PaulLTYF17}
D.~Paul, F.~Li, M.~K. Teja, X.~Yu, and R.~Frost.
\newblock Compass: Spatio temporal sentiment analysis of {US} election what
  twitter says!
\newblock In {\em SIGKDD}, 2017.

\bibitem{DBLP:journals/vldb/QinLTL20}
X.~Qin, Y.~Luo, N.~Tang, and G.~Li.
\newblock Making data visualization more efficient and effective: a survey.
\newblock {\em {VLDB} J.}, 29(1):93--117, 2020.

\bibitem{rocklov2020high}
J.~Rockl{\"o}v and H.~Sj{\"o}din.
\newblock High population densities catalyse the spread of covid-19.
\newblock {\em Journal of travel medicine}, 27(3):taaa038, 2020.

\end{thebibliography}


\end{document}
