\documentclass[11pt]{article}
\usepackage{deauthor}
\usepackage{enumitem}
\usepackage{algorithmic}
\usepackage{algorithm}
\usepackage{xcolor}
\usepackage{xspace}
\usepackage{graphicx}
%\usepackage[caption=false]{subfig}
\usepackage{footnote}
\usepackage{hyperref}
\usepackage{multirow}
\usepackage{subfig}
\usepackage{enumitem}
\usepackage{comment}



% simple command to highlight revising
\newcommand\revise[1]{\textcolor{black}{#1}}
% simple command to take notes during drafting process
\newcommand\todo[1]{\textcolor{red}{#1}}
% hybrid index placeholder
\newcommand{\hybridindex}{HQI\xspace}


\begin{document}


\title{Fact Ranking over Large-Scale Knowledge Graphs with Reasoning Embedding Models}

\author{Hongyu Ren$\dagger$\footnote{work done during an internship at Apple.}, Ali Mousavi*, Anil Pacaci*, Shihabur R. Chowdhury*, Jason Mohoney$\ddagger$$^*$, \\ Ihab F. Ilyas*, Yunyao Li*, Theodoros Rekatsinas*\\
  *Apple \\
  $\dagger$Stanford University, hyren@stanford.edu \\
  $\ddagger$University of Wisconsin-Madison, mohoney2@wisc.edu\\
  *{amousavi, apacaci, shihab, iilyas, yunyaoli, thodrek}@apple.com
}


\maketitle
\renewcommand\thesection{\arabic{section}}
\setcounter{section}{0}
\setcounter{figure}{0}
\setcounter{table}{0}

\input{submissions/Ali2023/000_abstract}

\input{submissions/Ali2023/010_introduction}
\input{submissions/Ali2023/020_preliminary}
\input{submissions/Ali2023/030_usecase}
\input{submissions/Ali2023/031_unified}
\input{submissions/Ali2023/040_system}
\input{submissions/Ali2023/050_experiment}
\input{submissions/Ali2023/032_related_entities}
% \input{vldb2022/060_related}
\input{submissions/Ali2023/070_conclusion}
\input{submissions/Ali2023/100_appendix}
%\clearpage

\begin{thebibliography}{10}
\itemsep=1pt
\begin{small}


\bibitem{bollacker2008freebase} K.~Bollacker, C.~Evans, P.~Paritosh, T.~Sturge, and J.~Taylor. \newblock Freebase: a collaboratively created graph database for structuring human knowledge. \newblock {\em SIGMOD}, 2008.

\bibitem{transe} A.~Bordes, N.~Usunier, A.~Garcia-Dur\'{a}n, J.~Weston, and O.~Yakhnenko. \newblock Translating Embeddings for Modeling Multi-Relational Data. \newblock {\em Neural Information Processing Systems}, 2787–-2795, 2013.

\bibitem{bouraga2014knowledge} S.~Bouraga, I.~Jurerta, S.~Faulkner, and C.~Herssens. \newblock Knowledge-based recommendation systems: a survey. \newblock {\em International Journal of Intelligent Information Technologies}, 10(2):1--19, 2014.

% \bibitem{catherine2016personalized} R.~Catherine, and W.~Cohen. \newblock Personalized recommendations using knowledge graphs: A probabilistic logic programming approach. \newblock {\em ACM conference on recommender systems}, 325--332, 2016.

\bibitem{chami2020machine} I.~Chami, S.~Abu-El-Haija, B.~Perozzi, C.~Re, and K.~Murphy. \newblock Machine learning on graphs: A model and comprehensive taxonomy. \newblock {\em arXiv preprint}, arXiv:2005.03675, 2020.

\bibitem{DBLP:journals/corr/Cohen16b} W.~Cohen. \newblock TensorLog: {A} Differentiable Deductive Database. \newblock {\em arXiv preprint}, arXiv:1605.06523, 2016.

\bibitem{de2018formal} C.~De Sa, I.~Ilyas, B.~Kimelfeld, C.~R{\'e}, and T.~Rekatsinas. \newblock A formal framework for probabilistic unclean databases. \newblock {\em arXiv preprint}, arXiv:1801.06750, 2018.

\bibitem{knowledgevault} X.~Dong, E.~Gabrilovich, G.~Heitz, W.~Horn, N.~Lao, K.~Murphy, T.~Strohmann, S.~Sun, and W.~Zhang. \newblock Knowledge vault: A web-scale approach to probabilistic knowledge fusion. \newblock {\em ACM SIGKDD International Conference on Knowledge Discovery \& Data Mining}, 601--610, 2014.

\bibitem{Dong2019DataIA} D.~Xin, and T.~Rekatsinas. \newblock Data Integration and Machine Learning: A Natural Synergy. \newblock {\em ACM SIGKDD International Conference on Knowledge Discovery \& Data Mining}, 2019.

\bibitem{10.14778/2732951.2732962} X.~Dong, E.~Gabrilovich, G.~Heitz, W.~Horn, K.~Murphy, S.~Sun, and W.~Zhang. \newblock From Data Fusion to Knowledge Fusion. \newblock {\em VLDB}, 7(10):881--892, 2014.


% \bibitem{guo2022manu}, R.~Guo, X.~Luan, L.~Xiang, X.~Yan, X.~Yi, J.~Luo, Q.~Cheng, W.~Xu, J.~Luo, F.~Liu, and others. \newblock Manu: A Cloud Native Vector Database Management System. \newblock {\em arXiv preprint},  arXiv:2206.13843

\bibitem{hamilton2018embedding} W.~Hamilton, P.~Bajaj, M.~Zitnik, D.~Jurafsky, and J.~Leskovec. \newblock Embedding Logical Queries on Knowledge Graphs. \newblock {\em Neural Information Processing Systems}, 2018.

\bibitem{heidari2020record} A.~Heidari, G.~Michalopoulos, S.~Kushagra, I.~Ilyas, and T.~Rekatsinas. \newblock Record fusion: A learning approach. \newblock {\em arXiv preprint}, arXiv:2006.10208, 2020.

\bibitem{10.1145/3447548.3467342} H.~Huang, L.~Sun, B.~Du, C.~Liu, W.~Lv, and H.~Xiong. \newblock Representation Learning on Knowledge Graphs for Node Importance Estimation. \newblock {\em ACM SIGKDD Conference on Knowledge Discovery \& Data Mining}, 646-655, 2021.

\bibitem{apple_kp} I.~Ilyas, T.~Rekatsinas, V.~Konda, J.~Pound, X.~Qi, and M.~Soliman. \newblock Saga: A Platform for Continuous Construction and Serving of Knowledge At Scale. \newblock {\em ACM SIGMOD International Conference on Management of data}, 2022.

\bibitem{ilyas2019data} I.~Ilyas, and X.~Chu. \newblock Data Cleaning. \newblock {\em Morgan \& Claypool}, 2019.

\bibitem{ji2021survey} S.~Ji, S.~Pan, E.~Cambria, P.~Marttinen, and S.Y.~Philip. \newblock A survey on knowledge graphs: Representation, acquisition, and applications. \newblock {\em IEEE Transactions on Neural Networks and Learning Systems}, 2021.

\bibitem{kingma2014adam} D.~Kingma, and J.~Ba. \newblock Adam: A method for stochastic optimization. \newblock {\em International Conference on Learning Representations (ICLR)}, 2015.

\bibitem{lerer2019pytorch} A.~Lerer, L.~Wu, J.~Shen, T.~Lacroix, L.~Wehrstedt, A.~Bose, and A.~Peysakhovich. \newblock Pytorch-biggraph: A large-scale graph embedding system. \newblock {\em Conference on Machine Learning and Systems (MLSys)}, 2019.


\bibitem{liu2019roberta} Y.~Liu, M.~Ott, N.~Goyal, J.~Du, M.~Joshi, D.~Chen, O.~Levy, M.~Lewis, L.~Zettlemoyer, and V.~Stoyanov. \newblock Roberta: A robustly optimized bert pretraining approach. \newblock {\em arXiv preprint}, arXiv:1907.11692, 2019.

% \bibitem{mohoney2023high} J.~Mohoney, A.~Pacaci, S.~Chowdhury, A.~Mousavi, I.~Ilyas, U.F.~Minhas, J.~Pound, and T.~Rekatsinas. \newblock High-Throughput Vector Similarity Search in Knowledge Graphs. \newblock {\em arXiv preprint},  arXiv:2304.01926

\bibitem{mohoney2021marius} J.~Mohoney, R.~Waleffe, H.~Xu, T.~Rekatsinas, S.~Venkataraman. \newblock Marius: Learning Massive Graph Embeddings on a Single Machine. \newblock {\em USENIX Symposium on Operating Systems Design and Implementation (OSDI)}, 2021.


\bibitem{industry_kgs} N.~Noy, Y.~Gao, A.~Jain, A.~Narayanan, A.~Patterson, and J.~Taylor. \newblock Industry-Scale Knowledge Graphs: Lessons and Challenges. \newblock {\em Queue}, 17(2):48--75, 2019.


\bibitem{pujara2013knowledge} J.~Pujara, H.~Miao, L.~Getoor, and W.~Cohen. \newblock Knowledge graph identification. \newblock {\em International semantic web conference}, 542-557, 2013.


\bibitem{holoclean} T.~Rekatsinas, X.~Chu, I.~Ilyas, and C.~R\'{e}. \newblock HoloClean: Holistic Data Repairs with Probabilistic Inference. \newblock {\em VLDB Endowment}, 10(11):1190--1201, 2017.

\bibitem{ren2021smore} H.~Ren, H.~Dai, B.~Dai, X.~Chen, D.~Zhou, J.~Leskovec, and D.~Schuurmans. \newblock SMORE: Knowledge Graph Completion and Multi-hop Reasoning in Massive Knowledge Graphs. \newblock {\em arXiv preprint}, arXiv:2110.14890, 2021.

\bibitem{ren2020query2box} H.~Ren, W.~Hu, and J.~Leskovec. \newblock Query2box: Reasoning over Knowledge Graphs in Vector Space using Box Embeddings. \newblock {\em International Conference on Learning Representations (ICLR)}, 2020.

\bibitem{ren2020beta} H.~Ren, and J.~Leskovec. \newblock Beta Embeddings for Multi-Hop Logical Reasoning in Knowledge Graphs. \newblock {\em Neural Information Processing Systems (NeurIPS)}, 2020.

\bibitem{rossi2021knowledge} A.~Rossi, D.~Barbosa, D.~Firmani, A.~Matinata, P.~Merialdo. \newblock Knowledge graph embedding for link prediction: A comparative analysis. \newblock {\em ACM Transactions on Knowledge Discovery from Data}, 15(2)1--49, 2021.

\bibitem{sun2019rotate} Z.~Sun, Z.~Deng, J.~Nie, and J.~Tang. \newblock Rotate: Knowledge graph embedding by relational rotation in complex space. \newblock {\em International Conference on Learning Representations (ICLR)}, 2019.

\bibitem{sun2014fine} L.~Sun, M.J.~Franklin, S.~Krishnan, and R.S.~Xin. \newblock Fine-grained partitioning for aggressive data skipping, \newblock {\em ACM SIGMOD International Conference on Management of Data}, 1115-1126, 2014

\bibitem{sun2019re} Z.~Sun, S.~Vashishth, S.~Sanyal, P.~Talukdar, and Y.~Yang. \newblock A re-evaluation of knowledge graph completion methods. \newblock {\em arXiv preprint}, arXiv:1911.03903, 2019.

\bibitem{DBLP:conf/iclr/TabacofC20} P.~Tabacof and L.~Costabello. \newblock Probability Calibration for Knowledge Graph Embedding Models. \newblock {\em International Conference on Learning Representations (ICLR)}, 2020.

\bibitem{trouillon2016complex} T.~Trouillon, J.~Welbl, S.~Riedel, E.~Gaussier, G.~Bouchard. \newblock Complex embeddings for simple link prediction. \newblock {\em International Conference on Machine Learning (ICML)}, 2016.

% \bibitem{vartak2013chic} M.~Vartak, S.~Madden. \newblock CHIC: a combination-based recommendation system. \newblock {\em ACM SIGMOD International Conference on Management of Data}, 981--984, 2013.

\bibitem{wikidata} D.~Vrande\v{c}i\'{c}, and M.~Kr\"{o}tzsch. \newblock Wikidata: A Free Collaborative Knowledgebase. \newblock {\em Communications of the ACM}, 57(10):78--85, 2014.

 \bibitem{wang2021milvus} J.~Wang, X.~Yi, R.~Guo, H.~Jin, P.~Xu, S.~Li, X.~Wang, X.~Guo, C.~Li, X.~Xu, and others. \newblock Milvus: A purpose-built vector data management system. \newblock {\em ACM SIGMOD International Conference on Management of Data}, 2614--2627, 2021.

\bibitem{wei2021why} C.~Wei, S.M.~Xie, and T.~Ma. \newblock Why Do Pretrained Language Models Help in Downstream Tasks? An Analysis of Head and Prompt Tuning. \newblock {\em Advances in Neural Information Processing Systems}, 2021.

\bibitem{weikum2021knowledge} G.~Weikum. \newblock Knowledge graphs 2021: a data odyssey. \newblock {\em VLDB Endowment}, 14(12):3233--3238, 2021.

\bibitem{qd-tree} Z.~Yang, B.~Chandramouli, C.~Wang, J.~Gehrke, Y.~Li, U.F.~Minhas, P.~Larson, D.~Kossman, and R.~Acharya. \newblock Qd-Tree: Learning Data Layouts for Big Data Analytics. \newblock {\em ACM SIGMOD International Conference on Management of Data}, 193--208, 2020.

% \bibitem{yang2020pase} W.~Yang, T.~Li, G.~Fang, and H.~Wei. \newblock Pase: Postgresql ultra-high-dimensional approximate nearest neighbor search extension. \newblock {\em ACM SIGMOD International Conference on Management of Data}, 2241--2253, 2020.

\bibitem{distmult} B.~Yang, W.~Yih, X.~He, J.~Gao, L.~Deng. \newblock Embedding Entities and Relations for Learning and Inference in Knowledge Bases. \newblock {\em International Conference on Learning Representations (ICLR)}, 2015.

\bibitem{you2020handling} J.~You, X.~Ma, Y.~Ding, M.~Kochenderfer, and J.~Leskovec. \newblock Handling missing data with graph representation learning. \newblock {\em Advances in Neural Information Processing Systems (NeurIPS)}, 2020.

\bibitem{zhang2019quaternion} S.~Zhang, Y.~Tay, L.~Yao, Q.~Liu. \newblock Quaternion knowledge graph embeddings. \newblock {\em Advances in Neural Information Processing Systems (NeurIPS)}, 2019.

\bibitem{zhu2019graphvite} Z.~Zhu, S.~Xu, J.~Tang, and M.~Qu. \newblock Graphvite: A high-performance cpu-gpu hybrid system for node embedding. \newblock {\em The World Wide Web Conference (WWW)}, 2019.

\bibitem{poincare} M.~Nickel, and D.~Kiela. \newblock Poincaré embeddings for learning hierarchical representations \newblock {\em Advances in neural information processing systems (NeurIPS)}, 2017.

\bibitem{mohoney2023high} J.~Mohoney, A.~Pacaci, S.R.~Chowdhury, A.~Mousavi, I.~Ilyas, U.F.~Minhas, J.~POund, T.~Rekatsinas \newblock High-Throughput Vector Similarity Search in Knowledge Graphs \newblock{\em ACM SIGMOD/PODS International Conference on Management of Data (SIGMOD)}, 2023.

\end{small}
\end{thebibliography}


\end{document}