
\bibitem{propublicaJ}
Julia Angwin, Jeff Larson, Surya Mattu, and Lauren Kirchner.
\newblock Machine bias: Risk assessments in criminal sentencing.
\newblock {\em ProPublica}, May 2016.

\bibitem{DBLP:journals/pvldb/AsudehJMS18}
Abolfazl Asudeh, H.~V. Jagadish, Gerome Miklau, and Julia Stoyanovich.
\newblock On obtaining stable rankings.
\newblock {\em {PVLDB}}, 12(3):237--250, 2018.

\bibitem{DBLP:conf/sigmod/AsudehJS019}
Abolfazl Asudeh, H.~V. Jagadish, Julia Stoyanovich, and Gautam Das.
\newblock Designing fair ranking schemes.
\newblock In {\em Proceedings of the 2019 International Conference on
  Management of Data, {SIGMOD} Conference 2019, Amsterdam, The Netherlands,
  June 30 - July 5, 2019.}, pages 1259--1276, 2019.

\bibitem{DBLP:conf/icde/AsudehJJ19}
Abolfazl Asudeh, Zhongjun Jin, and H.~V. Jagadish.
\newblock Assessing and remedying coverage for a given dataset.
\newblock In {\em 35th {IEEE} International Conference on Data Engineering,
  {ICDE} 2019, Macao, China, April 8-11, 2019}, pages 554--565, 2019.

\bibitem{CitronP14}
Danielle~K. Citron and Frank~A. Pasquale.
\newblock The scored society: Due process for automated predictions.
\newblock {\em Washington Law Review}, 89, 2014.

\bibitem{BookerWydenClarke}
{Cory Booker, Ron Wyden, Yvette Clarke}.
\newblock {Algorithmic Accountability Act}.
\newblock
  \url{https://www.wyden.senate.gov/imo/media/doc/Algorithmic\%20Accountability\%20Act\%20of\%202019\%20Bill\%20Text.pdf},
  2019.
\newblock [Online; accessed 3-May-2019].

\bibitem{amazon_hiring}
Jeffrey Dastin.
\newblock Amazon scraps secret ai recruiting tool that showed bias against
  women.
\newblock {\em Reuters}, October 2018.

\bibitem{diversity}
Marina Drosou, HV~Jagadish, Evaggelia Pitoura, and Julia Stoyanovich.
\newblock Diversity in {Big Data}: A review.
\newblock {\em Big Data}, 5(2), 2017.

\bibitem{DBLP:journals/corr/abs-1803-09010}
Timnit Gebru, Jamie Morgenstern, Briana Vecchione, Jennifer~Wortman Vaughan,
  Hanna~M. Wallach, Hal~Daum{\'{e}} III, and Kate Crawford.
\newblock Datasheets for datasets.
\newblock {\em CoRR}, abs/1803.09010, 2018.

\bibitem{DBLP:phd/de/Gebser2011}
Martin Gebser.
\newblock {\em Proof theory and algorithms for answer set programming}.
\newblock PhD thesis, University of Potsdam, 2011.

\bibitem{gladwell}
Malcolm Gladwell.
\newblock The order of things.
\newblock {\em The New Yorker}, February 14, 2011.

\bibitem{DBLP:journals/corr/abs-1805-03677}
Sarah Holland, Ahmed Hosny, Sarah Newman, Joshua Joseph, and Kasia Chmielinski.
\newblock The dataset nutrition label: {A} framework to drive higher data
  quality standards.
\newblock {\em CoRR}, abs/1805.03677, 2018.

\bibitem{amazon_delivery}
David Ingold and Spencer Soper.
\newblock Amazon doesn’t consider the race of its customers. should it?
\newblock {\em Bloomberg}, April 2016.

\bibitem{DBLP:conf/sigmod/KeyHPA12}
Alicia Key, Bill Howe, Daniel Perry, and Cecilia~R. Aragon.
\newblock Vizdeck: self-organizing dashboards for visual analytics.
\newblock In {\em Proceedings of the {ACM} {SIGMOD} International Conference on
  Management of Data, {SIGMOD} 2012, Scottsdale, AZ, USA, May 20-24, 2012},
  pages 681--684, 2012.

\bibitem{DBLP:conf/icse/KoeneDS18}
Ansgar~R. Koene, Liz Dowthwaite, and Suchana Seth.
\newblock {IEEE} p7003{\texttrademark} standard for algorithmic bias
  considerations: work in progress paper.
\newblock In {\em Proceedings of the International Workshop on Software
  Fairness, FairWare@ICSE 2018, Gothenburg, Sweden, May 29, 2018}, pages
  38--41, 2018.

\bibitem{DBLP:journals/tog/Mackinlay86}
Jock~D. Mackinlay.
\newblock Automating the design of graphical presentations of relational
  information.
\newblock {\em {ACM} Trans. Graph.}, 5(2):110--141, 1986.

\bibitem{DBLP:conf/fat/MitchellWZBVHSR19}
Margaret Mitchell, Simone Wu, Andrew Zaldivar, Parker Barnes, Lucy Vasserman,
  Ben Hutchinson, Elena Spitzer, Inioluwa~Deborah Raji, and Timnit Gebru.
\newblock Model cards for model reporting.
\newblock In {\em Proceedings of the Conference on Fairness, Accountability,
  and Transparency, FAT* 2019, Atlanta, GA, USA, January 29-31, 2019}, pages
  220--229, 2019.

\bibitem{DBLP:journals/concurrency/MoreauLA08}
Luc Moreau, Bertram Lud{\"{a}}scher, Ilkay Altintas, Roger~S. Barga, Shawn
  Bowers, Steven~P. Callahan, George~Chin Jr., Ben Clifford, Shirley Cohen,
  Sarah~Cohen Boulakia, Susan~B. Davidson, Ewa Deelman, Luciano~A.
  Digiampietri, Ian~T. Foster, Juliana Freire, James Frew, Joe Futrelle, Tara
  Gibson, Yolanda Gil, Carole~A. Goble, Jennifer Golbeck, Paul~T. Groth,
  David~A. Holland, Sheng Jiang, Jihie Kim, David Koop, Ales Krenek, Timothy~M.
  McPhillips, Gaurang Mehta, Simon Miles, Dominic Metzger, Steve Munroe, Jim
  Myers, Beth Plale, Norbert Podhorszki, Varun Ratnakar, Emanuele Santos,
  Carlos~Eduardo Scheidegger, Karen Schuchardt, Margo~I. Seltzer, Yogesh~L.
  Simmhan, Cl{\'{a}}udio~T. Silva, Peter Slaughter, Eric~G. Stephan, Robert
  Stevens, Daniele Turi, Huy~T. Vo, Michael Wilde, Jun Zhao, and Yong Zhao.
\newblock Special issue: The first provenance challenge.
\newblock {\em Concurrency and Computation: Practice and Experience},
  20(5):409--418, 2008.

\bibitem{2019-draco}
Dominik Moritz, Chenglong Wang, Gregory Nelson, Halden Lin, Adam~M. Smith, Bill
  Howe, and Jeffrey Heer.
\newblock Formalizing visualization design knowledge as constraints: Actionable
  and extensible models in draco.
\newblock {\em IEEE Trans. Visualization \& Comp. Graphics (Proc. InfoVis)},
  2019.

\bibitem{op}
Open provenance.
\newblock \url{https://openprovenance.org}.
\newblock [Online; accessed 14-August-2019].

\bibitem{DBLP:conf/ssdbm/PingSH17}
Haoyue Ping, Julia Stoyanovich, and Bill Howe.
\newblock Datasynthesizer: Privacy-preserving synthetic datasets.
\newblock In {\em Proceedings of the 29th International Conference on
  Scientific and Statistical Database Management, Chicago, IL, USA, June 27-29,
  2017}, pages 42:1--42:5, 2017.

\bibitem{DBLP:journals/tvcg/QuH18}
Zening Qu and Jessica Hullman.
\newblock Keeping multiple views consistent: Constraints, validations, and
  exceptions in visualization authoring.
\newblock {\em {IEEE} Trans. Vis. Comput. Graph.}, 24(1):468--477, 2018.

\bibitem{DBLP:conf/vldb/RodriguezSPSH18}
Luke Rodriguez, Babak Salimi, Haoyue Ping, Julia Stoyanovich, and Bill Howe.
\newblock {MobilityMirror}: Bias-adjusted transportation datasets.
\newblock In {\em Big Social Data and Urban Computing - First Workshop,
  BiDU@VLDB 2018, Rio de Janeiro, Brazil, August 31, 2018, Revised Selected
  Papers}, pages 18--39, 2018.

\bibitem{salganik}
Matthew~J. Salganik.
\newblock {\em Bit By Bit: Social Research in the Digital Age}.
\newblock Princeton University Press, 2019.

\bibitem{DBLP:conf/sigmod/SalimiRHS19}
Babak Salimi, Luke Rodriguez, Bill Howe, and Dan Suciu.
\newblock Interventional fairness: Causal database repair for algorithmic
  fairness.
\newblock In {\em Proceedings of the 2019 International Conference on
  Management of Data, {SIGMOD} Conference 2019, Amsterdam, The Netherlands,
  June 30 - July 5, 2019.}, pages 793--810, 2019.

\bibitem{DBLP:journals/tvcg/SatyanarayanMWH17}
Arvind Satyanarayan, Dominik Moritz, Kanit Wongsuphasawat, and Jeffrey Heer.
\newblock Vega-lite: {A} grammar of interactive graphics.
\newblock {\em {IEEE} Trans. Vis. Comput. Graph.}, 23(1):341--350, 2017.

\bibitem{DBLP:conf/edbt/StoyanovichAM11}
Julia Stoyanovich, Sihem Amer{-}Yahia, and Tova Milo.
\newblock Making interval-based clustering rank-aware.
\newblock In {\em {EDBT} 2011, 14th International Conference on Extending
  Database Technology, Uppsala, Sweden, March 21-24, 2011, Proceedings}, pages
  437--448, 2011.

\bibitem{DBLP:conf/edbt/StoyanovichYJ18}
Julia Stoyanovich, Ke~Yang, and H.~V. Jagadish.
\newblock Online set selection with fairness and diversity constraints.
\newblock In {\em Proceedings of the 21th International Conference on Extending
  Database Technology, {EDBT} 2018, Vienna, Austria, March 26-29, 2018.}, pages
  241--252, 2018.

\bibitem{sun2019mithralabelJ}
Chenkai Sun, Abolfazl Asudeh, H.~V. Jagadish, Bill Howe, and Julia Stoyanovich.
\newblock {MithraLabel}: Flexible dataset nutritional labels for responsible
  data science.
\newblock In {\em Proceedings of the 28th {ACM} International Conference on
  Information and Knowledge Management ({CIKM})}, 2019.

\bibitem{gdpr}
{The European Union}.
\newblock {Regulation (EU) 2016/679: General Data Protection Regulation
  (GDPR)}.
\newblock \url{https://gdpr-info.eu/}, 2016.
\newblock [Online; accessed 15-August-2019].

\bibitem{Idaho}
{The Idaho house of Representatives}.
\newblock {House Bill No. 118}.
\newblock \url{https://legislature.vermont.gov/bill/status/2018/H.378}, 2019.
\newblock [Online; accessed 15-August-2019].

\bibitem{Vacca}
{The New York City Council}.
\newblock {Int. No. 1696-A: A Local Law in relation to automated decision
  systems used by agencies}.
\newblock
  \url{https://legistar.council.nyc.gov/LegislationDetail.aspx?ID=3137815&GUID=437A6A6D-62E1-47E2-9C42-461253F9C6D0},
  2017.
\newblock [Online; accessed on 15-August-2019].

\bibitem{Vermont}
{Vermont General Assembly}.
\newblock {An act relating to the creation of the Artificial Intelligence Task
  Force}.
\newblock
  \url{https://legislature.idaho.gov/wp-content/uploads/sessioninfo/2019/legislation/H0118A2.pdf},
  2018.
\newblock [Online; accessed 15-August-2019].

\bibitem{DBLP:conf/ijcai/YangGS19}
Ke~Yang, Vasilis Gkatzelis, and Julia Stoyanovich.
\newblock Balanced ranking with diversity constraints.
\newblock In {\em Proceedings of the Twenty-Eighth International Joint
  Conference on Artificial Intelligence, {IJCAI} 2019, Macao, China, August
  10-16, 2019}, pages 6035--6042, 2019.

\bibitem{DBLP:conf/ssdbm/YangS17}
Ke~Yang and Julia Stoyanovich.
\newblock Measuring fairness in ranked outputs.
\newblock In {\em Proceedings of the 29th International Conference on
  Scientific and Statistical Database Management, Chicago, IL, USA, June 27-29,
  2017}, pages 22:1--22:6, 2017.

\bibitem{DBLP:conf/sigmod/YangSAHJM18}
Ke~Yang, Julia Stoyanovich, Abolfazl Asudeh, Bill Howe, H.~V. Jagadish, and
  Gerome Miklau.
\newblock A nutritional label for rankings.
\newblock In {\em Proceedings of the 2018 International Conference on
  Management of Data, {SIGMOD} Conference 2018, Houston, TX, USA, June 10-15,
  2018}, pages 1773--1776, 2018.

\bibitem{DBLP:conf/cikm/ZehlikeB0HMB17}
Meike Zehlike, Francesco Bonchi, Carlos Castillo, Sara Hajian, Mohamed Megahed,
  and Ricardo~A. Baeza{-}Yates.
\newblock {FA*IR}: {A} fair top-k ranking algorithm.
\newblock In {\em Proceedings of the 2017 {ACM} on Conference on Information
  and Knowledge Management, {CIKM} 2017, Singapore, November 06 - 10, 2017},
  pages 1569--1578, 2017.

\bibitem{DBLP:journals/datamine/Zliobaite17}
Indre Zliobaite.
\newblock Measuring discrimination in algorithmic decision making.
\newblock {\em Data Min. Knowl. Discov.}, 31(4):1060--1089, 2017.

