\documentclass[11pt]{article} 

\usepackage{deauthor,times,graphicx}
%\usepackage{url}
%\usepackage{hyperref}

\begin{document}
The June issue of the Data Engineering Bulletin features a collection
of papers curated by Prof. Tien Tuan Anh Dinh on the topic of
Transparent Database Systems. It is the first issue of the Bulletin
dedicated to addressing the rising of blockchain technology and its
implication for data management.

A blockchain is an immutable digital ledger of transaction records. It
is decentralized, distributed, and encrypted, making it a potential
solution for a variety of data-driven applications with varying
transparency and privacy requirements.

Several papers in this issue concentrated on leveraging the benefits
of blockchains for data management. For example, Korth discussed how
to best balance transparency and privacy so that blockchains can
provide users with the level of trust that centralized data management
systems cannot. Peng et al., on the other hand, focus on the potential
benefits for data providers and consumers should we succeed in
developing a system that allows privacy-preserving verifiable data
sharing using blockchain technology.

While blockchain databases have the potential to offer a variety of
benefits such as transparency, privacy, ownership, and trust,
currently, they lack meaningful query and analytics support, making it
difficult for them to support many real-life applications. A digital
ledger, to some extent, is a complicated ``OLTP'' system optimized for
decentralized immutability. Applications that require ``OLAP'' support
may be forced to rely on systems that re-centralize the distributed
data, negating all the benefits that blockchains can provide. We are
looking forward to discussing these challenges in future Bulletin
issues.
\end{document}
