\documentclass[11pt]{article}


\title{Federated Truth Discovery for Mobile Crowdsensing with Privacy-Preserving Trustworthiness Assessment}

\author{Leye Wang$^{1,2}$, Guanghong Fan$^{1,2}$, Xiao Han$^{3,}$\footnote{Corresponding author} \\
 \small $^1$Key Lab of High Confidence Software Technologies (Peking University), Ministry of Education, China \\
\small$^2$School of Computer Science, Peking University, China\\
\small$^3$School of Information Management and Engineering, Shanghai University of Finance and Economics, China\\
\texttt{\small leyewang@pku.edu.cn, fgh@stu.pku.edu.cn, xiaohan@mail.shufe.edu.cn}
}

\begin{document}
	
\maketitle

\begin{abstract}
With the prevalence of smart mobile devices empowered by considerable sensing capabilities, crowdsensing has become one promising way to sense urban phenomena (e.g., traffic and environment) at a large scale. In crowdsensing, a fundamental issue is discovering the truth from participants' noisy sensed data. Traditionally, participants need to upload their raw sensed data with locations for truth discovery, but this may leak participants' private information such as home and work locations. In this paper, we propose a federated truth discovery method that can learn the truth without collecting participants' sensed data and locations. Our method ensures that the obtained truth quality has no performance loss compared to the original truth discovery method if all the participants keep online; even if some participants lose connections unpredictably, our method can still learn the truth based on rest participants' data.
Meanwhile, as participants' sensed data are unknown to the server, it is hard for the crowdsensing organizer to justify each participant's sensing trustworthiness. This brings difficulties to crowdsensing management such as participant recruitment and incentive allocation. We further propose a federated ranking mechanism to generate a leader-board for participants' trustworthiness, which can also tolerate participants' connection loss. Both theoretical analysis and real-data empirical evaluations have been done to verify the effectiveness of FedTruthFinder.

\end{abstract}


\input{submissions/LeyeWang/intro}
\input{submissions/LeyeWang/original_truth_finder}
\input{submissions/LeyeWang/method}
\input{submissions/LeyeWang/incentive}
\input{submissions/LeyeWang/experiment}
\input{submissions/LeyeWang/related_work}
\input{submissions/LeyeWang/discussion}



\input{submissions/LeyeWang/appendix}




%%
%% The next two lines define the bibliography style to be used, and
%% the bibliography file.

\begin{thebibliography}{10}

\bibitem{Bonawitz2017PracticalSA}
K.~Bonawitz, V.~Ivanov, B.~Kreuter, A.~Marcedone, H.~McMahan, S.~Patel,
  D.~Ramage, A.~Segal, and K.~Seth.
\newblock Practical secure aggregation for privacy-preserving machine learning.
\newblock {\em CCS}, 2017.

\bibitem{chai2020secure}
D.~Chai, L.~Wang, K.~Chen, and Q.~Yang.
\newblock Secure federated matrix factorization.
\newblock {\em IEEE Intelligent Systems}, 2020.

\bibitem{ganti2011mobile}
R.~K. Ganti, F.~Ye, and H.~Lei.
\newblock Mobile crowdsensing: current state and future challenges.
\newblock {\em IEEE Communications Magazine}, 49(11):32--39, 2011.

\bibitem{han2021hidden}
X.~Han, L.~Wang, and W.~Fan.
\newblock Is hidden safe? location protection against machine-learning
  prediction attacks in social networks.
\newblock {\em MIS Quarterly}, 45(2):821--858, 2021.

\bibitem{konevcny2016federated}
J.~Kone{\v{c}}n{\`y}, H.~B. McMahan, F.~X. Yu, P.~Richt{\'a}rik, A.~T. Suresh,
  and D.~Bacon.
\newblock Federated learning: Strategies for improving communication
  efficiency.
\newblock {\em arXiv:1610.05492}, 2016.

\bibitem{li2014the}
H.~{Li}, B.~{Zhao}, and A.~{Fuxman}.
\newblock The wisdom of minority: discovering and targeting the right group of
  workers for crowdsourcing.
\newblock In {\em WWW}, pages 165--176, 2014.

\bibitem{li2016survey}
Y.~Li, J.~Gao, C.~Meng, Q.~Li, L.~Su, B.~Zhao, W.~Fan, and J.~Han.
\newblock A survey on truth discovery.
\newblock {\em SIGKDD Explor. Newsl.}, 17(2):1–16, Feb. 2016.

\bibitem{Li2018AnET}
Y.~Li, C.~Miao, L.~Su, J.~Gao, Q.~Li, B.~Ding, Z.~Qin, and K.~Ren.
\newblock An efficient two-layer mechanism for privacy-preserving truth
  discovery.
\newblock {\em KDD}, 2018.

\bibitem{Li2020TowardsDP}
Y.~Li, H.~Xiao, Z.~Qin, C.~Miao, L.~Su, J.~Gao, K.~Ren, and B.~Ding.
\newblock Towards differentially private truth discovery for crowd sensing
  systems.
\newblock {\em ICDCS}, pages 1156--1166, 2020.

\bibitem{liu2020secure}
Y.~{Liu}, Y.~{Kang}, C.~{Xing}, T.~{Chen}, and Q.~{Yang}.
\newblock A secure federated transfer learning framework.
\newblock {\em IEEE Intelligent Systems}, 35(4):70--82, 2020.

\bibitem{ma2014opportunities}
H.~Ma, D.~Zhao, and P.~Yuan.
\newblock Opportunities in mobile crowd sensing.
\newblock {\em IEEE Communications Magazine}, 52(8):29--35, 2014.

\bibitem{meng2015truth}
C.~Meng, W.~Jiang, Y.~Li, J.~Gao, L.~Su, H.~Ding, and Y.~Cheng.
\newblock Truth discovery on crowd sensing of correlated entities.
\newblock In {\em Proceedings of the 13th ACM Conference on Embedded Networked
  Sensor Systems}, pages 169--182, 2015.

\bibitem{Miao2015CloudEnabledPT}
C.~Miao, W.~Jiang, L.~Su, Y.~Li, S.~Guo, Z.~Qin, H.~Xiao, J.~Gao, and K.~Ren.
\newblock Cloud-enabled privacy-preserving truth discovery in crowd sensing
  systems.
\newblock In {\em SenSys}, 2015.

\bibitem{Miao2019PrivacyPreservingTD}
C.~Miao, W.~Jiang, L.~Su, Y.~Li, S.~Guo, Z.~Qin, H.~Xiao, J.~Gao, and K.~Ren.
\newblock Privacy-preserving truth discovery in crowd sensing systems.
\newblock {\em ACM Transactions on Sensor Networks}, 15:1 -- 32, 2019.

\bibitem{Miao2017ALP}
C.~Miao, L.~Su, W.~Jiang, Y.~Li, and M.~Tian.
\newblock A lightweight privacy-preserving truth discovery framework for mobile
  crowd sensing systems.
\newblock {\em INFOCOM}, pages 1--9, 2017.

\bibitem{ouyang2015truth}
R.~W. Ouyang, M.~Srivastava, A.~Toniolo, and T.~J. Norman.
\newblock Truth discovery in crowdsourced detection of spatial events.
\newblock {\em IEEE transactions on knowledge and data engineering},
  28(4):1047--1060, 2015.

\bibitem{Peng2018DataQG}
D.~Peng, F.~Wu, and G.~Chen.
\newblock Data quality guided incentive mechanism design for crowdsensing.
\newblock {\em IEEE Transactions on Mobile Computing}, 17:307--319, 2018.

\bibitem{epflmobility}
M.~Piorkowski, N.~Sarafijanovic-Djukic, and M.~Grossglauser.
\newblock {CRAWDAD} dataset epfl/mobility (v. 2009-02-24).
\newblock Downloaded from \url{https://crawdad.org/epfl/mobility/20090224},
  Feb. 2009.

\bibitem{Primault2019TheLR}
V.~Primault, A.~Boutet, S.~B. Mokhtar, and L.~Brunie.
\newblock The long road to computational location privacy: A survey.
\newblock {\em IEEE Communications Surveys \& Tutorials}, 21:2772--2793, 2019.

\bibitem{Reddy2010ExaminingMF}
S.~Reddy, D.~Estrin, M.~Hansen, and M.~Srivastava.
\newblock Examining micro-payments for participatory sensing data collections.
\newblock {\em UbiComp}, 2010.

\bibitem{shamir1979share}
A.~Shamir.
\newblock How to share a secret.
\newblock {\em Communications of the ACM}, 22(11):612--613, 1979.

\bibitem{tang2011secure}
C.~Tang, G.~Shi, and Z.~Yao.
\newblock Secure multi-party computation protocol for sequencing problem.
\newblock {\em SCIENTIA SINICA Informationis}, 41(7):789--797, 2011.

\bibitem{Tang2018NonInteractivePT}
X.~Tang, C.~Wang, X.~Yuan, and Q.~Wang.
\newblock Non-interactive privacy-preserving truth discovery in crowd sensing
  applications.
\newblock {\em INFOCOM}, pages 1988--1996, 2018.

\bibitem{Wang2014SurrogateMS}
D.~Wang, T.~Abdelzaher, and L.~M. Kaplan.
\newblock Surrogate mobile sensing.
\newblock {\em IEEE Communications Magazine}, 52:36--41, 2014.

\bibitem{wang2013credibility}
D.~Wang, L.~Kaplan, T.~Abdelzaher, and C.~C. Aggarwal.
\newblock On credibility estimation tradeoffs in assured social sensing.
\newblock {\em IEEE Journal on Selected Areas in Communications},
  31(6):1026--1037, 2013.

\bibitem{wang2012truth}
D.~Wang, L.~Kaplan, H.~Le, and T.~Abdelzaher.
\newblock On truth discovery in social sensing: A maximum likelihood estimation
  approach.
\newblock In {\em IPSN}, pages 233--244, 2012.

\bibitem{Wang2017LocationPT}
L.~Wang, D.~Yang, X.~Han, T.~Wang, D.~Zhang, and X.~Ma.
\newblock Location privacy-preserving task allocation for mobile crowdsensing
  with differential geo-obfuscation.
\newblock {\em WWW}, 2017.

\bibitem{Wang2019MobileCT}
L.~Wang, D.~Yang, X.~Han, D.~Zhang, and X.~Ma.
\newblock Mobile crowdsourcing task allocation with differential-and-distortion
  geo-obfuscation.
\newblock {\em IEEE Transactions on Dependable and Secure Computing},
  18:967--981, 2021.

\bibitem{Wang2020SparseMC}
L.~Wang, D.~Zhang, D.~Yang, B.~Y. Lim, X.~Han, and X.~Ma.
\newblock Sparse mobile crowdsensing with differential and distortion location
  privacy.
\newblock {\em IEEE Transactions on Information Forensics and Security},
  15:2735--2749, 2020.

\bibitem{wang2016differential}
L.~Wang, D.~Zhang, D.~Yang, B.~Y. Lim, and X.~Ma.
\newblock Differential location privacy for sparse mobile crowdsensing.
\newblock In {\em ICDM}, pages 1257--1262. IEEE, 2016.

\bibitem{Wang2021AST}
T.~Wang, C.~Lv, C.~Wang, F.~Chen, and Y.~Luo.
\newblock A secure truth discovery for data aggregation in mobile crowd
  sensing.
\newblock {\em Secur. Commun. Networks}, 2021:2296386:1--2296386:15, 2021.

\bibitem{Wang2019PersonalizedPT}
Z.~Wang, J.~Hu, R.~Lv, J.~Wei, Q.~Wang, D.~Yang, and H.~Qi.
\newblock Personalized privacy-preserving task allocation for mobile
  crowdsensing.
\newblock {\em IEEE Transactions on Mobile Computing}, 18:1330--1341, 2019.

\bibitem{Whitehill2009WhoseVS}
J.~Whitehill, P.~Ruvolo, T.~Wu, J.~Bergsma, and J.~Movellan.
\newblock Whose vote should count more: Optimal integration of labels from
  labelers of unknown expertise.
\newblock In {\em NeurIPS}, 2009.

\bibitem{Xu2019EfficientAP}
G.~Xu, H.~Li, S.~Liu, M.~Wen, and R.~Lu.
\newblock Efficient and privacy-preserving truth discovery in mobile crowd
  sensing systems.
\newblock {\em IEEE Transactions on Vehicular Technology}, 68:3854--3865, 2019.

\bibitem{yang2019federated}
Q.~Yang, Y.~Liu, T.~Chen, and Y.~Tong.
\newblock Federated machine learning: Concept and applications.
\newblock {\em ACM Transactions on Intelligent Systems and Technology},
  10(2):12, 2019.

\bibitem{yin2008truth}
X.~Yin, J.~Han, and S.~Y. Philip.
\newblock Truth discovery with multiple conflicting information providers on
  the web.
\newblock {\em IEEE Transactions on Knowledge and Data Engineering},
  20(6):796--808, 2008.

\bibitem{ZHANG2020101848}
C.~Zhang, C.~Xu, L.~Zhu, Y.~Li, C.~Zhang, and H.~Wu.
\newblock An efficient and privacy-preserving truth discovery scheme in
  crowdsensing applications.
\newblock {\em Computers \& Security}, 97:101848, 2020.

\bibitem{Zhang2021ReliableAP}
C.~Zhang, L.~Zhu, C.~Xu, X.~Liu, and K.~Sharif.
\newblock Reliable and privacy-preserving truth discovery for mobile
  crowdsensing systems.
\newblock {\em IEEE Transactions on Dependable and Secure Computing},
  18:1245--1260, 2021.

\bibitem{zhang20144w1h}
D.~Zhang, L.~Wang, H.~Xiong, and B.~Guo.
\newblock 4w1h in mobile crowd sensing.
\newblock {\em IEEE Communications Magazine}, 52(8):42--48, 2014.

\bibitem{Zheng2018LearningTT}
Y.~Zheng, H.~Duan, and C.~Wang.
\newblock Learning the truth privately and confidently: Encrypted
  confidence-aware truth discovery in mobile crowdsensing.
\newblock {\em IEEE Transactions on Information Forensics and Security},
  13:2475--2489, 2018.

\bibitem{Zheng2020PrivacyAwareAE}
Y.~Zheng, H.~Duan, X.~Yuan, and C.~Wang.
\newblock Privacy-aware and efficient mobile crowdsensing with truth discovery.
\newblock {\em IEEE Transactions on Dependable and Secure Computing},
  17:121--133, 2020.

\end{thebibliography}


\end{document}
%\endinput
%%
%% End of file `sample-sigconf.tex'.
