\documentclass[11pt]{article}
% arxiv pdflatex detection
\pdfoutput=1

\usepackage{deauthor}
\usepackage{times}
\usepackage{wrapfig}
\usepackage{graphicx}
\usepackage{xspace}
% \usepackage[it,small]{caption}
% \usepackage[export]{adjustbox}
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{textcomp}
\usepackage{graphicx}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{xcolor}


% ensure times
\usepackage{txfonts}
\usepackage{url}

\usepackage{balance}  % for  \balance command ON LAST PAGE  (only there!)
\usepackage{booktabs} % For formal tables
\usepackage{enumitem}
\usepackage{multirow}
\usepackage{subcaption}

% \usepackage[pdfpagelabels=false]{hyperref}

\usepackage{listings}

\usepackage{outlines}
\usepackage{authblk}


% Note-related commands.
\usepackage{etoolbox, totcount}
\newtoggle{shownotes}
\toggletrue{shownotes}
\newtotcounter{numnotes}
\newcommand{\note}[3]{
  \iftoggle{shownotes}{\stepcounter{numnotes}\textcolor{#1}{#2: #3}}{}
}

\newtoggle{showusernotes}
% \toggletrue{showusernote}
\newcommand{\joey}[1]{
    \iftoggle{showusernotes}{\note{cyan}{joey}{#1}}{}
}
\newcommand{\gabe}[1]{
    \iftoggle{showusernotes}{\note{magenta}{gabe}{#1}}{}
}
\newcommand{\shankari}[1]{
    \iftoggle{showusernotes}{\note{purple}{shankari}{#1}}{}
}
% Break URLs properly
\def\UrlBreaks{\do-\do\.\do\@\do\\\do\!\do\_\do\|\do\;\do\>\do\]\do\)\do\,\do\?\do\'\do+\do\=\do\#}
\def\UrlBigBreaks{\do\:\do\/}


\title{CoVista: A Unified View on Privacy Sensitive Mobile Contact Tracing Effort}
% \author{Junli Liu}
% % \affil{Integrative Cell Biology Laboratory, School of Biological and Biomedical Sciences,
%   % The Bio physical Sciences Institute, Durham University, Durham, UK}
%
% \author{James Rowe}
% \author{Keith Lindsey}
% % \affil{Some other laboratory, Elsewhere}
% % \author{foo bar}
% % \author{baz boo}
% % \afil

\author{David Culler, Prabal Dutta, Gabe Fierro, Joseph E. Gonzalez, Nathan Pemberton, \\
Johann Schleier-Smith, K. Shankari, Alvin Wan, Thomas Zachariah \\
{\small \texttt{\{culler, prabal, gt.fierro, jegonzal, nathanp\}@berkeley.edu}}\\
{\small \texttt{\{jssmith, shankari, alvinwan, tzachari\}@berkeley.edu}}\\
UC Berkeley
}


% \author{Gabe Fierro}
% \author{Joseph E. Gonzalez}
% \author{Nathan Pemberton}
% \author{Johann Schleier-Smith}
% \author{K. Shankari}
% \author{Alvin Wan}
% \author{Thomas Zachariah}
% \affil{UC Berkeley}

\begin{document}

\maketitle

\begin{abstract}
Governments around the world have become increasingly frustrated with tech giants dictating public health policy. The software created by Apple and Google enables individuals to track their own potential exposure through collated exposure notifications. However, the same software prohibits location tracking, denying key information needed by public health officials for robust contract tracing. This information is needed to treat and isolate COVID-19 positive people, identify transmission hotspots, and protect against continued spread of infection.
In this article, we present two simple ideas: the \textbf{lighthouse} and the \textbf{covid-commons} that address the needs of public health authorities while preserving the privacy-sensitive goals of the Apple and google exposure notification protocols. 
\end{abstract}

\input{intro}

\input{background}

\input{lighthouse}

\input{commons}


\input{conclusion}


% \bibliographystyle{IEEEtran}
% \bibliography{ms}
% \bibliography{submissions/BerkeleyCovista/ms}

% Generated by IEEEtran.bst, version: 1.14 (2015/08/26)
\begin{thebibliography}{10}
\providecommand{\url}[1]{#1}
\csname url@samestyle\endcsname
\providecommand{\newblock}{\relax}
\providecommand{\bibinfo}[2]{#2}
\providecommand{\BIBentrySTDinterwordspacing}{\spaceskip=0pt\relax}
\providecommand{\BIBentryALTinterwordstretchfactor}{4}
\providecommand{\BIBentryALTinterwordspacing}{\spaceskip=\fontdimen2\font plus
\BIBentryALTinterwordstretchfactor\fontdimen3\font minus
  \fontdimen4\font\relax}
\providecommand{\BIBforeignlanguage}[2]{{%
\expandafter\ifx\csname l@#1\endcsname\relax
\typeout{** WARNING: IEEEtran.bst: No hyphenation pattern has been}%
\typeout{** loaded for the language `#1'. Using the pattern for}%
\typeout{** the default language instead.}%
\else
\language=\csname l@#1\endcsname
\fi
#2}}
\providecommand{\BIBdecl}{\relax}
\BIBdecl

\bibitem{agen}
\BIBentryALTinterwordspacing
A.~Inc., \emph{"Apple and Google partner on COVID-19 contact tracing
  technology"}, 10 April 2020 (accessed 25 May 2020). [Online]. Available:
  \url{https://web.archive.org/web/20200410171128/https://www.apple.com/newsroom/2020/04/apple-and-google-partner-on-covid-19-contact-tracing-technology/}
\BIBentrySTDinterwordspacing

\bibitem{pact}
J.~Chan, D.~Foster, S.~Gollakota, E.~Horvitz, J.~Jaeger, S.~Kakade, T.~Kohno,
  J.~Langford, J.~Larson, P.~Sharma, S.~Singanamalla, J.~Sunshine, and
  S.~Tessaro, ``Pact: Privacy sensitive protocols and mechanisms for mobile
  contact tracing,'' 2020.

\bibitem{dp3t}
\BIBentryALTinterwordspacing
C.~e.~a. Troncoso, \emph{Decentralized Privacy-Preserving Proximity Tracing}.
  [Online]. Available:
  \url{https://github.com/DP-3T/documents/blob/master/DP3T%20White%20Paper.pdf}
\BIBentrySTDinterwordspacing

\bibitem{traceTogether20pct}
\BIBentryALTinterwordspacing
\emph{20 April 2020 - One Month On}, 20 April 2020 (Accessed 24 May 2020).
  [Online]. Available:
  \url{https://web.archive.org/web/20200524045214/https://support.tracetogether.gov.sg/hc/en-sg/articles/360046475654-20-April-2020-One-Month-On}
\BIBentrySTDinterwordspacing

\bibitem{hvacTransmission}
J.~Lu, J.~Gu, K.~Li, C.~Xu, W.~Su, and Z.~e.~a. Lai, ``Covid-19 outbreak
  associated with air conditioning in restaurant, guangzhou, china, 2020,''
  \emph{Emerging Infectious Disease}, 2020,
  https://doi.org/10.3201/eid2607.200764.

\bibitem{asianDiscrimination}
\BIBentryALTinterwordspacing
E.~Y.-J. Kang, \emph{Asian Americans Feel The Bite Of Prejudice During The
  COVID-19 Pandemic}, National Public Radio, 31 March 2020 (Accessed 2 April
  2020). [Online]. Available:
  \url{https://web.archive.org/web/20200402203217/https://www.npr.org/local/309/2020/03/31/824397216/asian-americans-feel-the-bite-of-prejudice-during-the-c-o-v-i-d-19-pandemic}
\BIBentrySTDinterwordspacing

\bibitem{koreaClub}
\BIBentryALTinterwordspacing
H.~Shin and J.~Smith, ``South korea scrambles to contain nightclub coronavirus
  outbreak,'' \emph{Reuters}, 2020. [Online]. Available:
  \url{https://www.reuters.com/article/us-health-coronavirus-southkorea/south-korea-scrambles-to-contain-nightclub-coronavirus-outbreak-idUSKBN22N0DA}
\BIBentrySTDinterwordspacing

\bibitem{hinch2020effective}
\BIBentryALTinterwordspacing
R.~Hinch, W.~Probert, A.~Nurtay, M.~Kendall, C.~Wymant, M.~Hall, and C.~Fraser,
  ``Effective configurations of a digital contact tracing app: A report to
  nhsx,'' 2020. [Online]. Available:
  \url{https://github.com/BDI-pathogens/covid-19_instant_tracing/blob/master/Report
  - Effective Configurations of a Digital Contact Tracing App.pdf}
\BIBentrySTDinterwordspacing

\bibitem{agen_pha_announce}
\BIBentryALTinterwordspacing
\emph{Exposure Notification API launches to support public health agencies},
  Apple Incorporated, Google LLC, 20 May 2020 (Accessed 24 May 2020). [Online].
  Available:
  \url{http://web.archive.org/web/20200524152945/https://blog.google/inside-google/company-announcements/apple-google-exposure-notification-api-launches/}
\BIBentrySTDinterwordspacing

\bibitem{bay_area_testing}
\BIBentryALTinterwordspacing
C.~Ho, ``Bay area coronavirus tests: Where can i get one?'' 21 May 2020
  (Accessed 25 May 2020). [Online]. Available:
  \url{http://web.archive.org/web/20200525201614/https://www.sfchronicle.com/health/article/Where-can-I-get-a-coronavirus-test-in-the-Bay-15136054.php}
\BIBentrySTDinterwordspacing

\bibitem{local_testing_sites}
\BIBentryALTinterwordspacing
N.~A. of~County and C.~H. Officials, ``Directory of local health departments,''
  24 May 2020 (Accessed 24 May 2020). [Online]. Available:
  \url{http://web.archive.org/web/20200524090932/https://www.naccho.org/membership/lhd-directory}
\BIBentrySTDinterwordspacing

\bibitem{tri_state_coalition}
\BIBentryALTinterwordspacing
N.~N. York, ``What you need to know about {N}ew {Y}ork’s ‘monumental’
  contact tracing program,'' 22 April 2020 (Accessed 24 May 2020). [Online].
  Available:
  \url{http://web.archive.org/web/20200524162632/https://www.nbcnewyork.com/news/coronavirus/what-you-need-to-know-about-new-yorks-monumental-contact-tracing-program/2385611/}
\BIBentrySTDinterwordspacing

\end{thebibliography}



\end{document}
