\documentclass[11pt]{article}

\usepackage{deauthor}
\usepackage{times}
\usepackage{authblk}

\input{submissions/junchao/header}
\input{submissions/junchao/plotdata}


\begin{document}

\title{Power-of-Collaboration: A Sustainable Resilient Ledger \\ Built Democratically}

\author{Junchao Chen,\quad Suyash Gupta$^{\dagger}$,\quad Sajjad Rahnama,\quad Mohammad Sadoghi\\
    \textit{Moka Blox LLC} \\ 
    Exploratory Systems Lab \\ 
    University of California, Davis \\ 
    $^{\dagger}$University of California, Berkeley
}


\maketitle

\begin{abstract}
\input{submissions/junchao/abstract}
\end{abstract}

\input{submissions/junchao/intro}
\input{submissions/junchao/prelim}
\input{submissions/junchao/back}
\input{submissions/junchao/algo}
\input{submissions/junchao/evaluation}
%\input{related}
\input{submissions/junchao/concl}

\section{Acknowledgments}
This work was supported in part by (1) {\em Oracle Cloud Credits} and 
related resources provided by the Oracle for Research program and (2) the 
{\em NSF STTR} under {\em Award Number} 2112345 provided to {\em Moka Blox LLC}.


%\balance
%\bibliographystyle{plain}
%\bibliography{submissions/junchao/refined}

\begin{thebibliography}{10}

\bibitem{sharper}
Mohammad~Javad Amiri, Divyakant Agrawal, and Amr El~Abbadi.
\newblock {\em {SharPer: Sharding Permissioned Blockchains Over Network
  Clusters}}, page 76–88.
\newblock Association for Computing Machinery, 2021.

\bibitem{bedrock}
Mohammad~Javad Amiri, Chenyuan Wu, Divyakant Agrawal, Amr~El Abbadi, Boon~Thau
  Loo, and Mohammad Sadoghi.
\newblock The bedrock of {BFT:} {A} unified platform for {BFT} protocol design
  and implementation.
\newblock {\em CoRR}, abs/2205.04534, 2022.

\bibitem{pbftj}
Miguel Castro and Barbara Liskov.
\newblock Practical byzantine fault tolerance and proactive recovery.
\newblock {\em ACM Trans. Comput. Syst.}, 20(4):398--461, 2002.

\bibitem{ahl}
Hung Dang, Tien Tuan~Anh Dinh, Dumitrel Loghin, Ee-Chien Chang, Qian Lin, and
  Beng~Chin Ooi.
\newblock Towards scaling blockchain systems via sharding.
\newblock In {\em Proceedings of the 2019 International Conference on
  Management of Data}, pages 123--140. ACM, 2019.

\bibitem{badcoin}
Alex de~Vries.
\newblock Bitcoin's growing energy problem.
\newblock {\em Joule}, 2(5):801--805, 2018.

\bibitem{sybil-attack}
John~R. Douceur.
\newblock The sybil attack.
\newblock In Peter Druschel, Frans Kaashoek, and Antony Rowstron, editors, {\em
  Peer-to-Peer Systems}, pages 251--260, Berlin, Heidelberg, 2002. Springer
  Berlin Heidelberg.

\bibitem{poe}
Suyash Gupta, Jelle Hellings, Sajjad Rahnama, and Mohammad Sadoghi.
\newblock {Proof-of-Execution}: Reaching consensus through fault-tolerant
  speculation.
\newblock In {\em Proceedings of the 24th International Conference on Extending
  Database Technology}, 2021.

\bibitem{blockchain-book}
Suyash Gupta, Jelle Hellings, and Mohammad Sadoghi.
\newblock {\em {Fault-Tolerant Distributed Transactions on Blockchain}}.
\newblock Synthesis Lectures on Data Management. Morgan {\&} Claypool
  Publishers, 2021.

\bibitem{rcc}
Suyash Gupta, Jelle Hellings, and Mohammad Sadoghi.
\newblock {RCC:} resilient concurrent consensus for high-throughput secure
  transaction processing.
\newblock In {\em 37th {IEEE} International Conference on Data Engineering,
  {ICDE} 2021, Chania, Greece, April 19-22, 2021}, pages 1392--1403. {IEEE},
  2021.

\bibitem{geobft}
Suyash Gupta, Sajjad Rahnama, Jelle Hellings, and Mohammad Sadoghi.
\newblock {ResilientDB}: Global scale resilient blockchain fabric.
\newblock {\em Proc. VLDB Endow.}, 13(6):868--883, 2020.

\bibitem{flexitrust}
Suyash Gupta, Sajjad Rahnama, Shubham Pandey, Natacha Crooks, and Mohammad
  Sadoghi.
\newblock Dissecting {BFT} consensus: In trusted components we trust!
\newblock {\em CoRR}, abs/2202.01354, 2022.

\bibitem{bc-processing}
Suyash Gupta and Mohammad Sadoghi.
\newblock Blockchain transaction processing.
\newblock In {\em Encyclopedia of Big Data Technologies}, pages 1--11.
  Springer, 2019.

\bibitem{byz-cluster-sending}
Jelle Hellings and Mohammad Sadoghi.
\newblock Brief announcement: The fault-tolerant cluster-sending problem.
\newblock In Jukka Suomela, editor, {\em 33rd International Symposium on
  Distributed Computing, {DISC} 2019}, volume 146 of {\em LIPIcs}, pages
  45:1--45:3, 2019.

\bibitem{delayedrepl}
Jelle Hellings and Mohammad Sadoghi.
\newblock Coordination-free byzantine replication with minimal communication
  costs.
\newblock In {\em 23rd International Conference on Database Theory, {ICDT}},
  pages 17:1--17:20, 2020.

\bibitem{cryptobook}
Jonathan Katz and Yehuda Lindell.
\newblock {\em Introduction to Modern Cryptography}.
\newblock Chapman and Hall/CRC, 2nd edition, 2014.

\bibitem{bitcoin}
Satoshi Nakamoto.
\newblock Bitcoin: A peer-to-peer electronic cash system, 2009.

\bibitem{ringbft}
Sajjad Rahnama, Suyash Gupta, Rohan Sogani, Dhruv Krishnan, and Mohammad
  Sadoghi.
\newblock {RingBFT: Resilient Consensus over Sharded Ring Topology}.
\newblock In {\em Proceedings of the 25th International Conference on Extending
  Database Technology}, pages 2:298--2:311. OpenProceedings.org, 2022.

\bibitem{pooled-mining}
Meni Rosenfeld.
\newblock Analysis of {Bitcoin} pooled mining reward systems, 2011.

\bibitem{mirbft}
Chrysoula Stathakopoulou, Matej Pavlovic, and Marko Vukolic.
\newblock State machine replication scalability made simple.
\newblock In Y{\'{e}}rom{-}David Bromberg, Anne{-}Marie Kermarrec, and Christos
  Kozyrakis, editors, {\em EuroSys '22: Seventeenth European Conference on
  Computer Systems}, pages 17--33. {ACM}, 2022.

\bibitem{basil}
Florian Suri-Payer, Matthew Burke, Zheng Wang, Yunhao Zhang, Lorenzo Alvisi,
  and Natacha Crooks.
\newblock Basil: Breaking up bft with acid (transactions).
\newblock In {\em Proceedings of the ACM SIGOPS 28th Symposium on Operating
  Systems Principles}, SOSP '21, page 1–17. Association for Computing
  Machinery, 2021.

\bibitem{badbadcoin}
Harald Vranken.
\newblock Sustainability of bitcoin and blockchains.
\newblock {\em Current Opinion in Environmental Sustainability}, 28:1--9, 2017.

\bibitem{ether}
Gavin Wood.
\newblock {Ethereum: A secure decentralised generalised transaction ledger}.
\newblock 2015.

\bibitem{hotstuff}
Maofan Yin, Dahlia Malkhi, Michael~K. Reiter, Guy~Golan Gueta, and Ittai
  Abraham.
\newblock {HotStuff}: {BFT} consensus with linearity and responsiveness.
\newblock In {\em Proceedings of the ACM Symposium on Principles of Distributed
  Computing}, pages 347--356. ACM, 2019.

\bibitem{scalable-ledger}
Kaiwen Zhang and Hans-Arno Jacobsen.
\newblock Towards dependable, scalable, and pervasive distributed ledgers with
  blockchains.
\newblock In {\em 2018 IEEE 38th International Conference on Distributed
  Computing Systems (ICDCS)}, pages 1337--1346, 2018.

\end{thebibliography}

\end{document}




