\section{Preliminaries}
We adopt the standard communication and failure model adopted by most \BFT{} 
protocols~\cite{poe,pbftj,geobft}. We consider a service $\Service$ of the 
form $\Service = \{\Replicas{}, \Miners{}, \Clients{} \}$. The set $\Replicas$ 
consists of $\n{\Replicas{}}$ replicas of which at most $\f{\Replicas{}}$ can 
behave arbitrarily. The remaining $\n{\Replicas}-\f{\Replicas}$ are honest: 
they will follow the protocol and remain live. Similarly, the set $\Miners$ 
consists of $\n{\Miners{}}$ miners of which at most $\f{\Miners{}}$ can act 
maliciously. We assign each {\em anonymous miner} and replica a unique identifier, 
which can be obtained by a call to the function $\ID{}$. The range of these 
identifiers are $[0, \abs{\Replicas}]$ for replicas and $[0, \abs{\Miners}]$ 
for miners. We further consider the existence of a finite set of clients 
$\Clients$ of which arbitrarily many can be malicious.

We assume {\em authenticated communication}: replicas employ standard 
cryptographic primitives such as \MAC{} and digital signatures (\DS{}) to 
sign messages. We denote a message $m$ signed by a replica $\Replica{}$ using 
\DS{} as {\bf $\SignMessage{m}{\Replica{}}$}. We permit malicious replicas to 
impersonate each other but no entity can impersonate an honest replica. We assume 
that like Bitcoin miners are identifier through their public-keys (i.e., anonymous), 
while the identities of replicas is known before consensus (i.e., known verified 
identity). We employ a \emph{collision-resistant} hash function $\Hash{\cdot}$ 
to map an arbitrary value $v$ to a constant-sized digest 
$\Hash{v}$~\cite{cryptobook}. Each replica only accepts a message if it is 
{\bf \em well-formed}.

We adopt the same partial synchrony model adopted in most consensus systems: 
safety is guaranteed in an asynchronous environment where messages can get 
lost, delayed, or duplicated. Liveness, however, is only guaranteed during the 
periods of synchrony~\cite{pbftj,poe,rcc,geobft,hotstuff}.
%Any consensus protocol is expected to meet the following guarantees:
%
\begin{description}
\item[\bf Safety.] 
If two honest replicas $\Replica{1}$ and $\Replica{2}$ order a transaction 
$\Transaction{}$ at sequence numbers $k$ and $k'$, then $k = k'$.

\item[\bf Liveness.]
If a client sends a transaction $\Transaction{}$, then it will eventually 
receive a response for $\Transaction{}$.
\end{description}

