\documentclass[11pt]{article} 

\usepackage{deauthor,times,graphicx}
%\usepackage{url}
\usepackage{hyperref}

\begin{document}
machine learning and AI will play a critical role in our data-driven
future. This explains the surge of interest in many machine learning
and AI related courses, conferences, and publications. The question
here is, in our data-driven future, what is the role of data
management?

Michael Stonebreaker and El Kindi Rezig tried answered this question
in their opinion piece ``Machine Learning and Big Data: What is
Important?'' Drawing from their experience working with big data in
real-life medical and business applications, they highlighted the
importance of data preparation, including data integration, data
enrichment, and data augmentation (for training). They argued that an
ML data management system that is capable of tracking and optimizing
the interactive steps of data preparation and machine learning is long
overdue.

Lei Chen et al put together an interesting issue consisting of 5
papers on the topic of ``Future of Work.'' They envisioned a future
where AI and machines automate most of the work, but humans are in the
loop to provide intellectual self-actualization. The papers looked
into today's crowdsourcing platforms and investigate problems such as
using active learning to make data labeling more efficient and
effective. In addition, the issue highlighted ethical challenges in
the future of work by using examples of today's self-employment
platforms such as Uber and Amazon Mechanical Turk.
\end{document}

