\documentclass[11pt]{article} 

\usepackage{deauthor,times,graphicx}
%\usepackage{url}
\usepackage{hyperref}

\begin{document}

\subsection*{ICDE 2018}

Repeating my comment from the last issue-

The IEEE International Conference on Data Engineering will be held in April 14-19, 2018 in Paris, France.  This is the flagship conference of the Computer Society's Technical Committee on Data Engineering.  It is a great conference, at a great location.  What could possibly be better than April in Paris at ICDE!  I am attending and hope to see you there.

\subsection*{About the Bulletin}

This March current issue marks the end of editorial tenure for the Bulletin's current set of editors.  So it is once again time for me to pat myself on the back.  This current set, Tim Kraska, Tova Milo, and Haixun Wang, continue my outstanding success (he says modestly) in finding and choosing great editors.  All three have done truly fine jobs at producing issues that bring to our readers surveys of the latest work in very current areas. The success of the Bulletin depends on great issue editors.  I want to thank Tim, Tova, and Haixun for being exactly that with the fine jobs that they have done.  There was unexpected ``scrambling" over the past two years, so I want to thank them also for their flexibility in coping with this.  


\subsection*{The Current Issue}

Don't you get tired of someone shouting ``FAKE NEWS!".  Or perhaps even worse, being exposed to fake news before it has been labeled as such?  Our political conversations seem increasingly to include many variations of ``fake news" and discussions about which news is fake.  ``Sad." So where am I going with this?

The database world has been working on a key aspect of this problem for many years.  The technical area is called ``data provenance".  And it addresses the problem of where information comes from and how it impacts the subsequent processing of data and the reported results.  The June, 2010 issue was the last one on provenance.  And seven years is a long time in an active technical area, especially an area as important as this.

The current issue is focused on the applications of provenance.  Without delving into the current political scene, a reader will clearly see how extensively provenance management can be used.  As we gain more insight into its application scenarios, we also gain more insight into how to manage provenance.  This symbiotic relationship is driving the field forward.   Tova Milo, our Bulletin editor for the issue, has done an excellent job in bringing the issue together, making it a great place to learn about and track progress in the field.  The result is an issue well worth reading.



\end{document}


