\documentclass[11pt]{article}

\usepackage{deauthor}
\usepackage{times, enumerate}
\usepackage{graphicx}
\usepackage{authblk}
\usepackage{url}
\def\UrlBreaks{\do\/\do-}
\usepackage{breakurl}
%\usepackage[breaklinks]{hyperref}
\usepackage{wrapfig}
\usepackage{enumitem}

\graphicspath{{figs/}}

%\usepackage[usenames,dvipsnames,svgnames]{xcolor}

\newcommand{\hdr}[1]{\noindent\textbf{#1.}}
\newcommand{\todo}[1]{\textcolor{purple}{\textbf{[#1]}}}
\newcommand{\tammo}[1]{\textcolor{blue}{\textbf{#1}}}
\newcommand{\felix}[1]{\textcolor{green}{\textbf{[#1]}}}
\newcommand{\jacek}[1]{\textcolor{magenta}{\textbf{[#1]}}}


\begin{document}

\title{Automated Data Validation in Machine Learning Systems}
%
\author{Felix Biessmann, Jacek Golebiowski, Tammo Rukat, Dustin Lange, Philipp Schmidt\\
{\small \texttt{\{biessman,jacekgo,tammruka,langed,phschmid\}@amazon.com}}\\
Amazon}

\maketitle

\input{submissions/data-validation-amazon/00-abstract}
\input{submissions/data-validation-amazon/01-introduction}
\input{submissions/data-validation-amazon/02-validation-metrics}
\input{submissions/data-validation-amazon/03-validation-solutions}
\input{submissions/data-validation-amazon/04-conclusion}


%\begin{small}
%	\bibliographystyle{plain}
%	\bibliography{data-validation-ml-systems}
%\end{small}


\begin{thebibliography}{10}

\bibitem{Polyzotis2018}
{\em {Data Lifecycle Challenges in Production Machine Learning: A Survey}},
  number (Vol. 47, No. 2). SIGMOD Record, 2018.

\bibitem{Abadi2016}
Martin Abadi, Andy Chu, Ian Goodfellow, H.~Brendan McMahan, Ilya Mironov, Kunal
  Talwar, and Li~Zhang.
\newblock Deep learning with differential privacy.
\newblock In {\em Proceedings of the 2016 ACM SIGSAC Conference on Computer and
  Communications Security}, CCS '16, pages 308--318, New York, NY, USA, 2016.
  Association for Computing Machinery.

\bibitem{Abedjan2018}
Ziawasch Abedjan, Lukasz Golab, Felix Naumann, and Thorsten Papenbrock.
\newblock {Data Profiling}.
\newblock {\em Synthesis Lectures on Data Management}, 10(4):1--154, nov 2018.

\bibitem{Athalye18}
Anish Athalye, Logan Engstrom, Andrew Ilyas, and Kevin Kwok.
\newblock Synthesizing robust adversarial examples.
\newblock volume~80 of {\em Proceedings of Machine Learning Research}, pages
  284--293, Stockholmsm{\"a}ssan, Stockholm Sweden, 10--15 Jul 2018. PMLR.

\bibitem{Bagdasaryan2019}
Eugene Bagdasaryan, Omid Poursaeed, and Vitaly Shmatikov.
\newblock Differential privacy has disparate impact on model accuracy.
\newblock In H.~Wallach, H.~Larochelle, A.~Beygelzimer, F.~Alch\'{e}-Buc,
  E.~Fox, and R.~Garnett, editors, {\em Advances in Neural Information
  Processing Systems}, volume~32, pages 15479--15488. Curran Associates, Inc.,
  2019.

\bibitem{Baylor2017}
Denis Baylor, Eric Breck, Heng~Tze Cheng, Noah Fiedel, Chuan~Yu Foo, Zakaria
  Haque, Salem Haykal, Mustafa Ispir, Vihan Jain, Levent Koc, Chiu~Yuen Koo,
  Lukasz Lew, Clemens Mewald, Akshay~Naresh Modi, Neoklis Polyzotis, Sukriti
  Ramesh, Sudip Roy, Steven~Euijong Whang, Martin Wicke, Jarek Wilkiewicz, Xin
  Zhang, and Martin Zinkevich.
\newblock {TFX: A TensorFlow-based production-scale machine learning platform}.
\newblock In {\em Proceedings of the ACM SIGKDD International Conference on
  Knowledge Discovery and Data Mining}, volume Part F129685, pages 1387--1395,
  New York, NY, USA, aug 2017. Association for Computing Machinery.

\bibitem{Bhagoji_2018}
Arjun~Nitin Bhagoji, Daniel Cullina, Chawin Sitawarin, and Prateek Mittal.
\newblock Enhancing robustness of machine learning systems via data
  transformations.
\newblock {\em 2018 52nd Annual Conference on Information Sciences and Systems
  (CISS)}, Mar 2018.

\bibitem{Biessmann2018a}
Felix Biessmann, David Salinas, Sebastian Schelter, Philipp Schmidt, and Dustin
  Lange.
\newblock {"Deep" Learning for Missing Value Imputationin Tables with
  Non-Numerical Data}.
\newblock In {\em Proceedings of the 27th ACM International Conference on
  Information and Knowledge Management - CIKM '18}, pages 2017--2025, New York,
  New York, USA, 2018. ACM Press.

\bibitem{Biggio_2013}
Battista Biggio, Igino Corona, Davide Maiorca, Blaine Nelson, Nedim {\v
  S}rndi{\'c}, Pavel Laskov, Giorgio Giacinto, and Fabio Roli.
\newblock Evasion attacks against machine learning at test time.
\newblock {\em Lecture Notes in Computer Science}, pages 387--402, 2013.

\bibitem{Bose2017a}
Joos~Hendrik B{\"{o}}se, Valentin Flunkert, Jan Gasthaus, Tim Januschowski,
  Dustin Lange, David Salinas, Sebastian Schelter, Matthias Seeger, and Yuyang
  Wang.
\newblock {Probabilistic demand forecasting at scale}.
\newblock {\em Proceedings of the VLDB Endowment}, 10(12):1694--1705, 2017.

\bibitem{Breck2019}
Eric Breck, Neoklis Polyzotis, Sudip Roy, Steven~Euijong Whang, and Martin
  Zinkevich.
\newblock {DATA VALIDATION FOR MACHINE LEARNING}.
\newblock Technical report, 2019.

\bibitem{Ceritli2020}
Taha Ceritli, Christopher~K.I. Williams, and James Geddes.
\newblock ptype: probabilistic type inference.
\newblock {\em Data Mining and Knowledge Discovery}, 34(3):870--904, may 2020.

\bibitem{Dallachiesat2013}
Michele Dallachiesat, Amr Ebaid, Ahmed Eldawy, Ahmed Elmagarmid, Ihab~F. Ilyas,
  Mourad Ouzzani, and Nan Tang.
\newblock {NADEEF: A commodity data cleaning system}.
\newblock In {\em Proceedings of the ACM SIGMOD International Conference on
  Management of Data}, 2013.

\bibitem{DAmour2020}
Alexander D'Amour, Katherine Heller, Dan Moldovan, Ben Adlam, Babak Alipanahi,
  Alex Beutel, Christina Chen, Jonathan Deaton, Jacob Eisenstein, Matthew~D.
  Hoffman, Farhad Hormozdiari, Neil Houlsby, Shaobo Hou, Ghassen Jerfel, Alan
  Karthikesalingam, Mario Lucic, Yian Ma, Cory McLean, Diana Mincu, Akinori
  Mitani, Andrea Montanari, Zachary Nado, Vivek Natarajan, Christopher Nielson,
  Thomas~F. Osborne, Rajiv Raman, Kim Ramasamy, Rory Sayres, Jessica Schrouff,
  Martin Seneviratne, Shannon Sequeira, Harini Suresh, Victor Veitch, Max
  Vladymyrov, Xuezhi Wang, Kellie Webster, Steve Yadlowsky, Taedong Yun,
  Xiaohua Zhai, and D.~Sculley.
\newblock {Underspecification Presents Challenges for Credibility in Modern
  Machine Learning}.
\newblock 2020.

\bibitem{Dong2018}
Xin~Luna Dong and Theodoros Rekatsinas.
\newblock {Data Integration and Machine Learning: A Natural Synergy}.
\newblock {\em Proceedings ofthe VLDB Endowment, Vol.}, 11(12):2094--2097,
  2018.

\bibitem{Dwork08differentialprivacy}
Cynthia Dwork.
\newblock Differential privacy: A survey of results.
\newblock In {\em In Theory and Applications of Models of Computation}, pages
  1--19. Springer, 2008.

\bibitem{Dworak_2006_diff}
Cynthia Dwork, Frank McSherry, Kobbi Nissim, and Adam Smith.
\newblock Calibrating noise to sensitivity in private data analysis.
\newblock In Shai Halevi and Tal Rabin, editors, {\em Theory of Cryptography},
  pages 265--284, Berlin, Heidelberg, 2006. Springer Berlin Heidelberg.

\bibitem{Dworak2014differantial}
Cynthia Dwork and Aaron Roth.
\newblock The algorithmic foundations of differential privacy.
\newblock {\em Found. Trends Theor. Comput. Sci.}, 9(3--4):211--407, August
  2014.

\bibitem{feinman2017detecting}
Reuben Feinman, Ryan~R. Curtin, Saurabh Shintre, and Andrew~B. Gardner.
\newblock Detecting adversarial samples from artifacts, 2017.

\bibitem{Fredrikson2015}
Matt Fredrikson, Somesh Jha, and Thomas Ristenpart.
\newblock {Model inversion attacks that exploit confidence information and
  basic countermeasures}.
\newblock In {\em Proceedings of the ACM Conference on Computer and
  Communications Security}, 2015.

\bibitem{gong2017adversarial}
Zhitao Gong, Wenlu Wang, and Wei-Shinn Ku.
\newblock Adversarial and clean data are not twins, 2017.

\bibitem{goodfellow2014explaining}
Ian~J. Goodfellow, Jonathon Shlens, and Christian Szegedy.
\newblock Explaining and harnessing adversarial examples, 2014.

\bibitem{grosse2017statistical}
Kathrin Grosse, Praveen Manoharan, Nicolas Papernot, Michael Backes, and
  Patrick McDaniel.
\newblock On the (statistical) detection of adversarial examples, 2017.

\bibitem{Hayes2019}
Jamie Hayes, Luca Melis, George Danezis, and Emiliano~De Cristofaro.
\newblock {LOGAN: Membership Inference Attacks Against Generative Models}.
\newblock {\em Proceedings on Privacy Enhancing Technologies},
  2019(1):133--152, 2019.

\bibitem{Heidari2019}
Alireza Heidari, Joshua McGrath, Ihab~F Ilyas, and Theodoros Rekatsinas.
\newblock {HoloDetect: Few-Shot Learning for Error Detection}.
\newblock {\em ACM Reference Format}, 2019.

\bibitem{hendrycks2016early}
Dan Hendrycks and Kevin Gimpel.
\newblock Early methods for detecting adversarial images, 2016.

\bibitem{Ho_2015}
Chien-Ju Ho, Aleksandrs Slivkins, Siddharth Suri, and Jennifer~Wortman Vaughan.
\newblock Incentivizing high quality crowdwork.
\newblock {\em Proceedings of the 24th International Conference on World Wide
  Web - WWW '15}, 2015.

\bibitem{Hosseini2019AreOR}
H.~Hosseini, S.~Kannan, and R.~Poovendran.
\newblock Are odds really odd? bypassing statistical detection of adversarial
  examples.
\newblock {\em ArXiv}, abs/1907.12138, 2019.

\bibitem{Huang2017}
Zhipeng Huang and Yeye He.
\newblock {Auto-Detect: Data-Driven Error Detection in Tables}.
\newblock {\em SIGMOD}, 2017.

\bibitem{Jayaraman2019}
Bargav Jayaraman and David Evans.
\newblock {\em {Evaluating Differentially Private Machine Learning in
  Practice}}.
\newblock 28th USENIX Security Symposium, 2019.

\bibitem{Kraska2018}
Tim Kraska, Alex Beutel, Ed~H Chi, Jeffrey Dean, and Neoklis Polyzotis.
\newblock {The case for learned index structures}.
\newblock In {\em Proceedings of the ACM SIGMOD International Conference on
  Management of Data}, pages 489--504, 2018.

\bibitem{Krishnan2017}
Sanjay Krishnan, Michael~J Franklin, Ken Goldberg, and Eugene Wu.
\newblock {BoostClean: Automated Error Detection and Repair for Machine
  Learning}.

\bibitem{Krishnan:2016b}
Sanjay Krishnan, Jiannan Wang, Eugene Wu, Michael~J. Franklin, and K.~Goldberg.
\newblock {ActiveClean: Interactive data cleaning for statistical modeling}.
\newblock {\em Proceedings of the VLDB Endowment}, 9(12):948--959, 2016.

\bibitem{Krishnan2019}
Sanjay Krishnan and Eugene Wu.
\newblock {AlphaClean: Automatic Generation of Data Cleaning Pipelines}.
\newblock apr 2019.

\bibitem{Kruse2018}
Sebastian Kruse and Felix Naumann.
\newblock {Efficient Discovery of Approximate Dependencies}.
\newblock {\em PVLDB}, 11(7):759--772, 2018.

\bibitem{Kumar2017}
Arun Kumar, Matthias Boehm, and Jun Yang.
\newblock {Data Management in Machine Learning: Challenges, Techniques, and
  Systems}.
\newblock In {\em SIGMOD}, 2017.

\bibitem{Kurakin2017AdversarialEI}
A.~Kurakin, Ian~J. Goodfellow, and S.~Bengio.
\newblock Adversarial examples in the physical world.
\newblock {\em ArXiv}, abs/1607.02533, 2017.

\bibitem{aleks2017deep}
Aleksander Madry, Aleksandar Makelov, Ludwig Schmidt, Dimitris Tsipras, and
  Adrian Vladu.
\newblock Towards deep learning models resistant to adversarial attacks, 2017.

\bibitem{MahdaviBerlinmahdavilahijani}
Mohammad~TU {Mahdavi Berlin mahdavilahijani}, tu-berlinde {Ziawasch Abedjan},
  Raul {Castro Fernandez MIT}, Samuel {Madden MIT}, Mourad Ouzzani, Michael
  {Stonebraker MIT}, Nan Tang, Mohammad Mahdavi, Ziawasch Abedjan, Raul {Castro
  Fernandez}, Samuel Madden, and Michael Stonebraker.
\newblock {Raha: A Configuration-Free Error Detection System}.
\newblock 18(19).

\bibitem{Mehrabi2019}
Ninareh Mehrabi, Fred Morstatter, Nripsuta Saxena, Kristina Lerman, and Aram
  Galstyan.
\newblock {A Survey on Bias and Fairness in Machine Learning}.
\newblock aug 2019.

\bibitem{metzen2017detecting}
Jan~Hendrik Metzen, Tim Genewein, Volker Fischer, and Bastian Bischoff.
\newblock On detecting adversarial perturbations, 2017.

\bibitem{Mironov2017}
I.~{Mironov}.
\newblock R{\'e}nyi differential privacy.
\newblock In {\em 2017 IEEE 30th Computer Security Foundations Symposium
  (CSF)}, pages 263--275, 2017.

\bibitem{MoosaviDezfooli2016DeepFoolAS}
Seyed-Mohsen Moosavi-Dezfooli, Alhussein Fawzi, and P.~Frossard.
\newblock Deepfool: A simple and accurate method to fool deep neural networks.
\newblock {\em 2016 IEEE Conference on Computer Vision and Pattern Recognition
  (CVPR)}, pages 2574--2582, 2016.

\bibitem{Nguyen_2015}
Anh Nguyen, Jason Yosinski, and Jeff Clune.
\newblock Deep neural networks are easily fooled: High confidence predictions
  for unrecognizable images.
\newblock {\em 2015 IEEE Conference on Computer Vision and Pattern Recognition
  (CVPR)}, Jun 2015.

\bibitem{pang2017robust}
Tianyu Pang, Chao Du, Yinpeng Dong, and Jun Zhu.
\newblock Towards robust detection of adversarial examples, 2017.

\bibitem{Papenbrock2015}
Thorsten Papenbrock, Jens Ehrlich, Jannik Marten, Tommy Neubert, Jan-Peer
  Rudolph, Martin Sch{\"{o}}nberg, Jakob Zwiener, and Felix Naumann.
\newblock {Functional dependency discovery}.
\newblock {\em Proceedings of the VLDB Endowment}, 8(10):1082--1093, jun 2015.

\bibitem{papernot2016semisupervised}
Nicolas Papernot, Mart{\'\i}n Abadi, {\'U}lfar Erlingsson, Ian Goodfellow, and
  Kunal Talwar.
\newblock Semi-supervised knowledge transfer for deep learning from private
  training data, 2016.

\bibitem{Cavallo1987}
Michael Pittarelli.
\newblock {Roger Cavallo}.
\newblock {\em Proceedings of the Thirteenth International Conference on Very
  Large Data Bases}, (January):71--81, 1987.

\bibitem{Rabanser2018}
Stephan Rabanser, Stephan G{\"{u}}nnemann, and Zachary~C Lipton.
\newblock {Failing loudly: An empirical study of methods for detecting dataset
  shift}, 2018.

\bibitem{Rekatsinas2017}
Theodoros Rekatsinas, Xu~Chu, Ihab~F Ilyas, and Christopher R{\'{e}}.
\newblock {HoloClean: Holistic Data Repairs with Probabilistic Inference}.
\newblock {\em Proceedings ofthe VLDB Endowment}, 10(11), 2017.

\bibitem{Rukat2020}
Tammo Rukat, Dustin Lange, Sebastian Schelter, and Felix Biessmann.
\newblock {Towards Automated ML Model Monitoring: Measure, Improve and Quantify
  Data Quality}.
\newblock Technical report.

\bibitem{Samek2019}
Wojciech Samek and Klaus~Robert M{\"{u}}ller.
\newblock {Towards Explainable Artificial Intelligence}.
\newblock In {\em Lecture Notes in Computer Science (including subseries
  Lecture Notes in Artificial Intelligence and Lecture Notes in
  Bioinformatics)}, volume 11700 LNCS, pages 5--22. Springer Verlag, 2019.

\bibitem{Schelter2017}
Sebastian Schelter, Joos-Hendrik Boese, Johannes Kirschnick, Thoralf Klein, and
  Stephan Seufert.
\newblock {Automatically tracking metadata and provenance of machine learning
  experiments}.
\newblock {\em Machine Learning Systems workshop at NeurIPS}, 2017.

\bibitem{Schelter2018}
Sebastian Schelter, Dustin Lange, Philipp Schmidt, Meltem Celikel, Felix
  Biessmann, Andreas Grafberger, and Meltem Ce-Likel.
\newblock {Automating Large-Scale Data Quality Verification}.
\newblock {\em PVLDB}, 11(12):1781--1794, 2018.

\bibitem{Schelter2020}
Sebastian Schelter, Rukat Tammo, and Felix Biessmann.
\newblock {Learning to Validate the Predictions of Black Box Classifiers on
  Unseen Data}.
\newblock {\em SIGMOD}, 2020.

\bibitem{schmidt2019quantifying}
Philipp Schmidt and Felix Biessmann.
\newblock Quantifying interpretability and trust in machine learning systems,
  2019.

\bibitem{schmidt2020risk}
Philipp Schmidt and Felix Biessmann.
\newblock Calibrating human-ai collaboration: Impact of risk, ambiguity and
  transparency on algorithmic bias.
\newblock In Andreas Holzinger, Peter Kieseberg, A~Min Tjoa, and Edgar Weippl,
  editors, {\em Machine Learning and Knowledge Extraction}, pages 431--449,
  Cham, 2020. Springer International Publishing.

\bibitem{Sculley2015}
D~Sculley, Gary Holt, Daniel Golovin, Eugene Davydov, Todd Phillips, Dietmar
  Ebner, Vinay Chaudhary, Michael Young, and Dan Dennison.
\newblock {Hidden Technical Debt in Machine Learning Systems}.
\newblock {\em Nips}, pages 2494--2502, 2015.

\bibitem{Shokri2017}
Reza Shokri, Marco Stronati, Congzheng Song, and Vitaly Shmatikov.
\newblock {Membership Inference Attacks Against Machine Learning Models}.
\newblock {\em Proceedings - IEEE Symposium on Security and Privacy}, pages
  3--18, 2017.

\bibitem{Stoyanovich2020}
Julia Stoyanovich, Bill Howe, and H.~V. Jagadish.
\newblock {Responsible data management}.
\newblock {\em Proceedings of the VLDB Endowment}, 13(12):3474--3488, 2020.

\bibitem{Sweeney2002}
Latanya Sweeney.
\newblock K-anonymity: A model for protecting privacy.
\newblock {\em Int. J. Uncertain. Fuzziness Knowl.-Based Syst.},
  10(5):557--570, October 2002.

\bibitem{szegedy2013intriguing}
Christian Szegedy, Wojciech Zaremba, Ilya Sutskever, Joan Bruna, Dumitru Erhan,
  Ian Goodfellow, and Rob Fergus.
\newblock Intriguing properties of neural networks, 2013.

\bibitem{wang_2018}
H.~{Wang}, S.~{Guo}, J.~{Cao}, and M.~{Guo}.
\newblock Melody: A long-term dynamic quality-aware incentive mechanism for
  crowdsourcing.
\newblock {\em IEEE Transactions on Parallel and Distributed Systems},
  29(4):901--914, 2018.

\bibitem{WortmanVaughan2018}
Jennifer {Wortman Vaughan}.
\newblock {Making Better Use of the Crowd: How Crowdsourcing Can Advance
  Machine Learning Research}.
\newblock Technical report, 2018.

\bibitem{Yang2020}
Ke~Yang, Biao Huang, and Sebastian Schelter.
\newblock {Fairness-Aware Instrumentation of Preprocessing Pipelines for
  Machine Learning}.
\newblock 2020.

\bibitem{zhang2019}
Haichao Zhang and Jianyu Wang.
\newblock Defense against adversarial attacks using feature scattering-based
  adversarial training, 2019.

\bibitem{Zhang2020}
Jie~M. Zhang, Mark Harman, Lei Ma, and Yang Liu.
\newblock {Machine Learning Testing: Survey, Landscapes and Horizons}.
\newblock {\em IEEE Transactions on Software Engineering}, pages 1--1, feb
  2020.

\bibitem{Zhao2019}
Yue Zhao, Zain Nasrullah, and Zheng Li.
\newblock {PyOD: A python toolbox for scalable outlier detection}.
\newblock {\em Journal of Machine Learning Research}, 2019.

\bibitem{Dingyuan2019}
Dingyuan Zhu, Ziwei Zhang, Peng Cui, and Wenwu Zhu.
\newblock Robust graph convolutional networks against adversarial attacks.
\newblock In {\em Proceedings of the 25th ACM SIGKDD International Conference
  on Knowledge Discovery and Data Mining}, KDD '19, pages 1399--1407, New York,
  NY, USA, 2019. Association for Computing Machinery.

\bibitem{Ziemann2016}
Mark Ziemann, Yotam Eren, and Assam El-Osta.
\newblock {Gene name errors are widespread in the scientific literature}.
\newblock {\em Genome Biology}, 17(1):177, aug 2016.

\end{thebibliography}


\end{document}
