\documentclass[11pt]{article} 

\usepackage{deauthor,times,graphicx}
%\usepackage{url}
\usepackage{hyperref}

\begin{document}


\subsection*{Opinions and Viewpoints}

Starting from this issue, the Data Engineering Bulletin will feature
opinions and viewpoints from distinguished researchers in the database
community and beyond. The landscape of data management has changed
dramatically since the Internet, the explosion of big data, and the
rise of machine learning. It is important to ponder on the state of
database research, its impact on industrial practice, and new
initiatives the database community should undertake. For this reason,
we bring in thought leaders to help stimulate the discussions and move
the field forward.

In this issue, we asked two renowned experts in the field, David Lomet
and Alon Halevy, to share their thoughts about some history and future
trends of data management. David comtemplates on the role of caching
in the past and future. His analysis provides deep insights into why
data caching systems continue to dominate the market and how to
achieve higher performance that does not rely on simply increasing
main memory cache size. Alon considers aspects of data that are
important to decision making but are traditionally ignored by our
research community. His pieces covers the management of subjective
data, building unbiased presentations of data that are tailored to the
subjective world-view of the recipient, and the subjective nature of
human decision making.

\subsection*{The Current Special Issue}
Philippe Bonnet put together an exciting issue on the inter-operations
among applications, database systems, operating system, and
hardware. The six articles in the issue illustrate various forms of
cross-layer support.

\end{document}

