\documentclass[11pt]{article}

\usepackage{deauthor}
\usepackage{times,graphicx}

% user packages

\usepackage{url}
\usepackage{todonotes}
\usepackage{subcaption}
\usepackage{pifont}
\usepackage{newtxtext}
\usepackage{newtxmath}
\usepackage{newclude}
\usepackage{multirow}
\usepackage{hyperref}
\usepackage{CJK}
\usepackage{cite}
\usepackage{booktabs}
\usepackage{balance}
\newcommand{\xmark}{\ding{55}}
\newcommand{\cmark}{\ding{51}}

\renewcommand{\dblfloatpagefraction}{.9}

% unnecessary commands

\usepackage{paralist}
\newcommand{\entity}{\mathcal{E}}
\newcommand{\relation}{\mathcal{R}}
\newcommand{\lang}{\mathcal{L}}
\newcommand{\model}{\mathcal{M}}
\newcommand{\term}{\mathcal{T}}
\newcommand{\kgnew}{\mathcal{KG}}

\title{Implicit Sentiment Analysis of Chinese Texts \\ based on Contextual Information and Knowledge Enhancement}

\author{ Zhenghui Cao$^{\dagger}$
\hspace{2em}  Siqi Wang$^{\ddagger}$
\hspace{2em}  Haofen Wang$^{\ddagger}$ \thanks{*Corresponding author}
\hspace{2em}  Wenqiang Zhang$^{\dagger}$ \\
$^{\dagger}$ Fudan University, Shanghai, China \hspace{1em}
\texttt{\small\{caozh20,wqzhang\}@fudan.edu.cn}\\
$^{\ddagger}$ Tongji University, Shanghai, China \hspace{1em}
\texttt{\small \{siqi\_wang,nobot\}@tongji.edu.cn}}

\begin{document}

\maketitle

\input{submissions/knowledge-sentiment-analysis/chapter0.abstract.tex}
\input{submissions/knowledge-sentiment-analysis/chapter1.introduction.tex}
\input{submissions/knowledge-sentiment-analysis/chapter2.relatedwork.tex}
\input{submissions/knowledge-sentiment-analysis/chapter3.methodology.tex}
\input{submissions/knowledge-sentiment-analysis/chapter4.experimentalsetup.tex}
\input{submissions/knowledge-sentiment-analysis/chapter5.resultsandanalysis.tex}
\input{submissions/knowledge-sentiment-analysis/chapter6.conclusion.tex}

\section{Acknowledgments}
%The authors would like to thank the anonymous reviewers for insightful comments and helpful suggestions.
This work was supported by National Natural Science Foundation of China (No.62176185)

%\bibliographystyle{plain}
%\bibliography{submissions/knowledge-sentiment-analysis/main}

\begin{thebibliography}{10}

\bibitem{balahur2011detecting}
Alexandra Balahur, Jes{\'u}s~M Hermida, and Andr{\'e}s Montoyo.
\newblock Detecting implicit expressions of sentiment in text based on
  commonsense knowledge.
\newblock In {\em Proceedings of the 2nd Workshop on Computational Approaches
  to Subjectivity and Sentiment Analysis (WASSA 2.011)}, pages 53--60, 2011.

\bibitem{balahur2012detecting}
Alexandra Balahur, Jes{\'u}s~M Hermida, and Andr{\'e}s Montoyo.
\newblock Detecting implicit expressions of emotion in text: A comparative
  analysis.
\newblock {\em Decision support systems}, 53(4):742--753, 2012.

\bibitem{bordes2013translating}
Antoine Bordes, Nicolas Usunier, Alberto Garcia-Duran, Jason Weston, and Oksana
  Yakhnenko.
\newblock Translating embeddings for modeling multi-relational data.
\newblock {\em Advances in neural information processing systems}, 26, 2013.

\bibitem{che2010ltp}
Wanxiang Che, Zhenghua Li, and Ting Liu.
\newblock Ltp: A chinese language technology platform.
\newblock In {\em Coling 2010: Demonstrations}, pages 13--16, 2010.

\bibitem{chen2016implicit}
Huan-Yuan Chen and Hsin-Hsi Chen.
\newblock Implicit polarity and implicit aspect recognition in opinion mining.
\newblock In {\em Proceedings of the 54th Annual Meeting of the Association for
  Computational Linguistics (Volume 2: Short Papers)}, pages 20--25, 2016.

\bibitem{ChenQiuChang2022}
Qiuchang CHEN, Hui ZHAO, Enguang ZUO, ZHAO Yuxia, and Wenyu WEI.
\newblock Implicit sentiment analysis based on context aware tree recurrent
  neutral network.
\newblock {\em Computer Engineering and Applications}, 58(07):167--175.

\bibitem{erik2017sentiment}
Cambria Erik, Poria Soujanya, Gelbukh Alexander, and Thelwall Mike.
\newblock Sentiment analysis is a big suitcase.
\newblock {\em IEEE Intelligent Systems}, 32(6):74--80, 2017.

\bibitem{jian2016constitution}
Liao Jian, Li~Yang, and Wang Suge.
\newblock The constitution of a fine-grained opinion annotated corpus on weibo.
\newblock In {\em Chinese Computational Linguistics and Natural Language
  Processing Based on Naturally Annotated Big Data}, pages 227--240. Springer,
  2016.

\bibitem{li2022c3kg}
Dawei Li, Yanran Li, Jiayi Zhang, Ke~Li, Chen Wei, Jianwei Cui, and Bin Wang.
\newblock C3kg: A chinese commonsense conversation knowledge graph.
\newblock {\em arXiv preprint arXiv:2204.02549}, 2022.

\bibitem{LiaoJian2018}
Jian Liao.
\newblock {\em Research on Fact-implied Implicit Sentiment Analysis Based on
  Representation Learning}.
\newblock PhD thesis, Shanxi University, 2018.

\bibitem{liao2022dynamic}
Jian Liao, Min Wang, Xin Chen, Suge Wang, and Kai Zhang.
\newblock Dynamic commonsense knowledge fused method for chinese implicit
  sentiment analysis.
\newblock {\em Information Processing \& Management}, 59(3):102934, 2022.

\bibitem{liao2019identification}
Jian Liao, Suge Wang, and Deyu Li.
\newblock Identification of fact-implied implicit sentiment based on
  multi-level semantic fused representation.
\newblock {\em Knowledge-Based Systems}, 165:197--207, 2019.

\bibitem{liao2017freerl}
Jian Liao, Suge Wang, Deyu Li, and Xiaoli Li.
\newblock Freerl: Fusion relation embedded representation learning framework
  for aspect extraction.
\newblock {\em Knowledge-Based Systems}, 135:9--17, 2017.

\bibitem{lin2015learning}
Yankai Lin, Zhiyuan Liu, Maosong Sun, Yang Liu, and Xuan Zhu.
\newblock Learning entity and relation embeddings for knowledge graph
  completion.
\newblock In {\em Twenty-ninth AAAI conference on artificial intelligence},
  2015.

\bibitem{liu2020sentiment}
Bing Liu.
\newblock {\em Sentiment analysis: Mining opinions, sentiments, and emotions}.
\newblock Cambridge university press, 2020.

\bibitem{mason2004cormet}
Zachary~J Mason.
\newblock Cormet: a computational, corpus-based conventional metaphor
  extraction system.
\newblock {\em Computational linguistics}, 30(1):23--44, 2004.

\bibitem{mehndiratta2017detection}
Pulkit Mehndiratta, Shelly Sachdeva, and Devpriya Soni.
\newblock Detection of sarcasm in text data using deep convolutional neural
  networks.
\newblock {\em Scalable Computing: Practice and Experience}, 18(3):219--228,
  2017.

\bibitem{PanDongXing2020}
Donghang PAN, Jingling YUAN, Lin Li, and Deming SHENG.
\newblock A chinese implicit sentiment classification model combining
  contextual features.
\newblock {\em Computer Engineering \& Science}, 42(2):10, 2020.

\bibitem{qian2018hierarchical}
Jing Qian, Mai ElSherief, Elizabeth Belding, and William~Yang Wang.
\newblock Hierarchical cvae for fine-grained hate speech classification.
\newblock {\em arXiv preprint arXiv:1809.00088}, 2018.

\bibitem{samuel2022direct}
David Samuel, Jeremy Barnes, Robin Kurtz, Stephan Oepen, Lilja {\O}vrelid, and
  Erik Velldal.
\newblock Direct parsing to sentiment graphs.
\newblock {\em arXiv preprint arXiv:2203.13209}, 2022.

\bibitem{sap2019atomic}
Maarten Sap, Ronan Le~Bras, Emily Allaway, Chandra Bhagavatula, Nicholas
  Lourie, Hannah Rashkin, Brendan Roof, Noah~A Smith, and Yejin Choi.
\newblock Atomic: An atlas of machine commonsense for if-then reasoning.
\newblock In {\em Proceedings of the AAAI conference on artificial
  intelligence}, volume~33, pages 3027--3035, 2019.

\bibitem{shutova2017multilingual}
Ekaterina Shutova, Lin Sun, Elkin~Dar{\'\i}o Guti{\'e}rrez, Patricia
  Lichtenstein, and Srini Narayanan.
\newblock Multilingual metaphor processing: Experiments with semi-supervised
  and unsupervised learning.
\newblock {\em Computational Linguistics}, 43(1):71--123, 2017.

\bibitem{shutova2013statistical}
Ekaterina Shutova, Simone Teufel, and Anna Korhonen.
\newblock Statistical metaphor processing.
\newblock {\em Computational Linguistics}, 39(2):301--353, 2013.

\bibitem{tai2015improved}
Kai~Sheng Tai, Richard Socher, and Christopher~D Manning.
\newblock Improved semantic representations from tree-structured long
  short-term memory networks.
\newblock {\em arXiv preprint arXiv:1503.00075}, 2015.

\bibitem{J2008LakoffGeorge}
J.~P. Thorne.
\newblock Lakoffgeorge and johnsonmark, metaphors we live by. chicago and
  london: The university of chicago press, 1980. pp. xiii + 242.
  bolingerdwight, language the loaded weapon: the use \& abuse of language
  today. london and new york: Longman, 1980. pp. ix + 214.
\newblock {\em Journal of Linguistics}, 19(1):245--248, 2008.

\bibitem{tong2013can}
Eddie~MW Tong, Deborah~H Tan, and Yan~Lin Tan.
\newblock Can implicit appraisal concepts produce emotion-specific effects? a
  focus on unfairness and anger.
\newblock {\em Consciousness and cognition}, 22(2):449--460, 2013.

\bibitem{vaswani2017attention}
Ashish Vaswani, Noam Shazeer, Niki Parmar, Jakob Uszkoreit, Llion Jones,
  Aidan~N Gomez, {\L}ukasz Kaiser, and Illia Polosukhin.
\newblock Attention is all you need.
\newblock {\em Advances in neural information processing systems}, 30, 2017.

\bibitem{wang2020chinese}
Hongbin Wang, Minghui Hou, Fan Li, and Yafei Zhang.
\newblock Chinese implicit sentiment analysis based on hierarchical knowledge
  enhancement and multi-pooling.
\newblock {\em IEEE Access}, 8:126051--126065, 2020.

\bibitem{WangSuGe2022}
Suge WANG, Min WANG, Jian LIAO, and Xin CHEN.
\newblock An implicit sentiment sentence identification method base on context
  information.
\newblock {\em Journal of Shanxi University(Natural Science Edition)},
  45(02):380--386.

\bibitem{wei2020BiLSTM}
Jiyao Wei, Jian Liao, Zhenfei Yang, Suge Wang, and Qiang Zhao.
\newblock Bi-lstm with multi-polarity orthogonal attention for implicit
  sentiment analysis.
\newblock {\em Neurocomputing}, 383:165--173, 2020.

\bibitem{YangShanLiang2021}
Shanliang YANG and CHANG Zheng.
\newblock Chinese implicit sentiment analysis based on graph attention neural
  network.
\newblock {\em Computer Engineering and Applications}, 57(24):161--167.

\bibitem{zhang2022incorporating}
Kai Zhang, Kun Zhang, Mengdi Zhang, Hongke Zhao, Qi~Liu, Wei Wu, and Enhong
  Chen.
\newblock Incorporating dynamic semantics into pre-trained language model for
  aspect-based sentiment analysis.
\newblock {\em arXiv preprint arXiv:2203.16369}, 2022.

\bibitem{zhang2011identifying}
Lei Zhang and Bing Liu.
\newblock Identifying noun product features that imply opinions.
\newblock In {\em Proceedings of the 49th annual meeting of the Association for
  Computational Linguistics: human language technologies}, pages 575--580,
  2011.

\bibitem{ZhaoRongMei2020}
Rongmei ZHAO, Xi~XIONG, Shenggen JU, Zhongzhi LI, and Chuan XIE.
\newblock Implicit sentiment analysis for chinese texts based on a hybrid
  neural network.
\newblock {\em Journal of Sichuan University(Natural Science Edition)},
  57(2):264--270, 2020.

\bibitem{zhao2012collocation}
Yanyan Zhao, Bing Qin, and Ting Liu.
\newblock Collocation polarity disambiguation using web-based pseudo contexts.
\newblock In {\em Proceedings of the 2012 Joint Conference on Empirical Methods
  in Natural Language Processing and Computational Natural Language Learning},
  pages 160--170, 2012.

\bibitem{zuo2020context}
Enguang Zuo, Hui Zhao, Bo~Chen, and Qiuchang Chen.
\newblock Context-specific heterogeneous graph convolutional network for
  implicit sentiment analysis.
\newblock {\em IEEE Access}, 8:37967--37975, 2020.

\end{thebibliography}
\end{document}

