\documentclass[11pt]{article} 

\usepackage{deauthor,times,graphicx}
%\usepackage{url}
\usepackage{hyperref}

\begin{document}

The pervasive integration of AI into daily life accentuates the
imperative of advancing Data-centric Responsible AI. This endeavor
transcends mere enhancements in model performance, aiming to ensure
that models are not only efficient but also trustworthy, fair, robust,
private, secure, and interpretable. Central to this mission is the
focus on refining the underlying data, acknowledging the integral role
of data quality in determining AI's efficacy.

In this March edition of the Data Engineering Bulletin, we delve into
data-driven approaches and the ethos of responsible AI. This issue,
meticulously curated by Steven Euijong Whang, showcases five papers
that chart a course toward a more equitable, reliable, and secure AI
landscape. These contributions not only spotlight prevailing
challenges but also introduce pioneering solutions and frameworks
poised to foster a more just AI ecosystem.

Specifically, the featured papers elucidate a spectrum of strategies
to bolster AI accountability across the machine learning
pipeline. This includes innovating data coverage techniques to rectify
underrepresentation of minority groups, applying causal modeling to
amend biases and enhance data integrity, and devising algorithmic
approaches to improve fairness and robustness in aggregating
preferences. Moreover, investigations into the resilience of Large
Language Models, such as ChatGPT, against adversarial threats,
alongside comparisons between food safety practices and data
traceability, provide fresh insights on promoting AI's reliability and
accountability.

As we explore these scholarly contributions, we are collectively
reminded of the shared duty among researchers, practitioners, and
policymakers to guide AI's trajectory toward outcomes that are
ethically sound and universally beneficial.
\end{document}


