\documentclass[11pt]{article}
\input{submissions/lei/macros}
% guidelines at http://tab.computer.org/tcde/bull_author.html
\usepackage{deauthor,times,graphicx}
%\graphicspath{{authorname/}}

%\usepackage[dvipsnames,svgnames]{xcolor}
\usepackage{tikz}
\newcommand{\sky}{\ensuremath{\textrm{Sky}}}
\usepackage{amssymb, framed}
\usepackage{tikz}
\usepackage{rotating}
\usetikzlibrary{trees,shapes,snakes,patterns}
% % % --------------------------------------- % % %
% % % Macros to write comments for internal usage % % %
% % % --------------------------------------- % % %

\newcommand{\bcom}{\color{red!60}}
%\newcommand\bcom\iffalse
\newcommand{\ecom}{\color{black}}
%\let\ecom\fi
\begin{document}
%\title{Evaluating Preference Operators with Crowd\\ (a.k.a. Noisy Oracle)}
%\title{Evaluating Preference Operators with the Crowd\\ (modeled as a Noisy Oracle)}
\title{On Benchmarking for Crowdsourcing\\ and Future of Work Platforms}
%\title{Human-in-the-loop in the Era of Big Data and AI: Benchmarking the Future of Work\thanks{This work has been partially supported by ....}} % via Pairwise Comparisons}
\author{Ria Mae Borromeo\\
Philippines Open University\\
\texttt{{\footnotesize rhborromeo@up.edu.ph}}
\and
Lei Chen\\
HKUST\\
\texttt{{\footnotesize leichen@cse.ust.hk}}
\and
Abhishek Dubey\\
Vanderbilt University\\
\texttt{{\footnotesize abhishek.dubey@vanderbilt.edu}}
\and
Sudeepa Roy\\
Duke University\\
\texttt{{\footnotesize sudeepa@cs.duke.edu}}
\and
Saravanan Thirumuruganathan\\
QCRI, HBKU\\
\texttt{{\footnotesize sthirumuruganathan@hbku.edu.qa}}
}
\maketitle

% -------------------------------------------------------- %

%\red{need to discuss the title -- not much `crowd'}

\input{submissions/lei/abstract}
\input{submissions/lei/introduction}
\input{submissions/lei/benchmarkingMetrics}
\input{submissions/lei/benchmarkdata}
%\input{benchmarkingRefImpl}
%\input{discussion}
\input{submissions/lei/research}
\input{submissions/lei/conclusions}

\input{submissions/lei/misc}

\bibliographystyle{abbrv}
\begin{thebibliography}{10}
	
	\bibitem{Figure8DataForEveryone}
	Figure eight's data for everyone.
	\newblock \url{https://www.figure-eight.com/data-for-everyone/}.
	\newblock Accessed: 07-Dec-2019.
	
	\bibitem{amer2016human}
	S.~Amer-Yahia and S.~B. Roy.
	\newblock Human factors in crowdsourcing.
	\newblock {\em Proceedings of the VLDB Endowment}, 9(13):1615--1618, 2016.
	
	\bibitem{basu2015task}
	S.~Basu~Roy, I.~Lykourentzou, S.~Thirumuruganathan, S.~Amer-Yahia, and G.~Das.
	\newblock Task assignment optimization in knowledge-intensive crowdsourcing.
	\newblock {\em The VLDB Journal—The International Journal on Very Large Data
		Bases}, 24(4):467--491, 2015.
	
	\bibitem{ChenCZC19}
	Z.~Chen, P.~Cheng, Y.~Zeng, and L.~Chen.
	\newblock Minimizing maximum delay of task assignment in spatial crowdsourcing.
	\newblock In {\em 35th {IEEE} International Conference on Data Engineering,
		{ICDE} 2019, Macao, China, April 8-11, 2019}, pages 1454--1465, 2019.
	
	\bibitem{ChenFZLXCCCTZ14}
	Z.~Chen, R.~Fu, Z.~Zhao, Z.~Liu, L.~Xia, L.~Chen, P.~Cheng, C.~C. Cao, Y.~Tong,
	and C.~J. Zhang.
	\newblock gmission: {A} general spatial crowdsourcing platform.
	\newblock {\em {PVLDB}}, 7(13):1629--1632, 2014.
	
	\bibitem{ChengCY19}
	P.~Cheng, L.~Chen, and J.~Ye.
	\newblock Cooperation-aware task assignment in spatial crowdsourcing.
	\newblock In {\em 35th {IEEE} International Conference on Data Engineering,
		{ICDE} 2019, Macao, China, April 8-11, 2019}, pages 1442--1453, 2019.
	
	\bibitem{cullina2015measuring}
	E.~Cullina, K.~Conboy, and L.~Morgan.
	\newblock Measuring the crowd: a preliminary taxonomy of crowdsourcing metrics.
	\newblock In {\em Proceedings of the 11th International Symposium on Open
		Collaboration}, page~7. ACM, 2015.
	
	\bibitem{ho2012online}
	C.-J. Ho and J.~W. Vaughan.
	\newblock Online task assignment in crowdsourcing markets.
	\newblock In {\em Twenty-Sixth AAAI Conference on Artificial Intelligence},
	2012.
	
	\bibitem{ikeda2016collaborative}
	K.~Ikeda, A.~Morishima, H.~Rahman, S.~B. Roy, S.~Thirumuruganathan,
	S.~Amer-Yahia, and G.~Das.
	\newblock Collaborative crowdsourcing with crowd4u.
	\newblock {\em Proceedings of the VLDB Endowment}, 9(13):1497--1500, 2016.
	
	\bibitem{kaufmann2011more}
	N.~Kaufmann, T.~Schulze, and D.~Veit.
	\newblock More than fun and money. worker motivation in crowdsourcing-a study
	on mechanical turk.
	\newblock In {\em AMCIS}, volume~11, pages 1--11. Detroit, Michigan, USA, 2011.
	
	\bibitem{li2016crowdsourced}
	G.~Li, J.~Wang, Y.~Zheng, and M.~J. Franklin.
	\newblock Crowdsourced data management: A survey.
	\newblock {\em IEEE Transactions on Knowledge and Data Engineering},
	28(9):2296--2319, 2016.
	
	\bibitem{mcfeely2018workplace}
	S.~McFeely and R.~Pendell.
	\newblock What workplace leaders can learn from the real gig economy. gallup,
	2018.
	
	\bibitem{pilz2013does}
	D.~Pilz and H.~Gewald.
	\newblock Does money matter? motivational factors for participation in paid-and
	non-profit-crowdsourcing communities.
	\newblock {\em Wirtschaftsinformatik}, 37:73--82, 2013.
	
	\bibitem{rahman2015task}
	H.~Rahman, S.~B. Roy, S.~Thirumuruganathan, S.~Amer-Yahia, and G.~Das.
	\newblock Task assignment optimization in collaborative crowdsourcing.
	\newblock In {\em 2015 IEEE International Conference on Data Mining}, pages
	949--954. IEEE, 2015.
	
	\bibitem{rahman2015worker}
	H.~Rahman, S.~Thirumuruganathan, S.~B. Roy, S.~Amer-Yahia, and G.~Das.
	\newblock Worker skill estimation in team-based tasks.
	\newblock {\em Proceedings of the VLDB Endowment}, 8(11):1142--1153, 2015.
	
	\bibitem{raykar2012eliminating}
	V.~C. Raykar and S.~Yu.
	\newblock Eliminating spammers and ranking annotators for crowdsourced labeling
	tasks.
	\newblock {\em Journal of Machine Learning Research}, 13(Feb):491--518, 2012.
	
	\bibitem{roy2013crowds}
	S.~B. Roy, I.~Lykourentzou, S.~Thirumuruganathan, S.~Amer-Yahia, and G.~Das.
	\newblock Crowds, not drones: modeling human factors in interactive
	crowdsourcing.
	\newblock 2013.
	
	\bibitem{yongxin2016online}
	Y.~Tong, J.~She, B.~Ding, L.~Chen, T.~Wo, and K.~Xu.
	\newblock Online minimum matching in realtime spatial data: Experiments and
	analysis.
	\newblock {\em Proceedings of the VLDB Endowment}, 9(12):1053--1064, 2016.
	
	\bibitem{zheng2017truth}
	Y.~Zheng, G.~Li, Y.~Li, C.~Shan, and R.~Cheng.
	\newblock Truth inference in crowdsourcing: Is the problem solved?
	\newblock {\em Proceedings of the VLDB Endowment}, 10(5):541--552, 2017.
	
\end{thebibliography}

\end{document}
