\section{Proposed Metrics}\label{sec:metrics}
The metrics used for the future of human and job interactions should also cover various criteria as shown below. To make the proposed metrics comprehensive and generic, we should take social and computation criteria into the metric design, The social  criteria include social impact, criticality, accessibility and robustness and the computation criteria include effectiveness and efficiency. We intend to design a set of metrics that can cover all the criteria together. The following table lists several common metrics we propose and their coverage to different criteria.  
\par
For instance, novel metrics like cognitive overhead may help measure how interested the workers are in their jobs, or whether the jobs lead to boredom and fatigue, perhaps leading to less retention, which is one of the desired criteria. Similarly, equity measures easy and universal access of the platforms to a wide range of users (including users with disabilities or without access to mobile phones), and criticality evaluates whether a job is time critical, in which case to satisfy this job requests some other criteria like fairness and latency of some other jobs may have to be compromised. See Table~\ref{tab:metric-vs-props}.

\begin{sidewaystable}
%\begin{table}[t]
    \centering
    \begin{tabular}{|c|c||c|c|c|c|c|c|c|c|}
    \hline
\multicolumn{2}{|c|}{{\bf Criteria}} & Effectiveness &  Efficiency &  Social Impact &  Criticality &  Accessibility &  Retention  &  Recruitment &  Robustness\\ \hline
\multicolumn{2}{|c|}{{\bf Metrics}} & & & & & & & & \\ \hline \hline
\multirow{6}{2cm}{Easily measurable Quantities} & Accuracy & x & & & & & & & \\ \cline{2-10}
& Completion &  & x & & & & & & \\ \cline{2-10}
& Latency &  & x & & x & & & & \\ \cline{2-10}
& Scalability & \multicolumn{8}{c|}{??} \\ \cline{2-10}
& Throughput & x & x & x & & & & & \\ \cline{2-10}
& Cost & x & & x & x & & & & \\ \hline\hline
\multirow{6}{2cm}{Human factors: not easily measurable} & Satisfaction &  & & x & & x & & & x \\ \cline{2-10}
& Task complexity &  &  &   & & x & & & \\ \cline{2-10}
& Cognitive overhead &  &  &  &  &  &  & & \\ \cline{2-10}
& Usability of the interface & x & x & x &  & x & x & & \\ \cline{2-10}
& Fairness &  &  & x & & x & & & x \\ \cline{2-10}
& Equity &  &  & x & & x & & & \\  \hline\hline

    \end{tabular}
    \caption{Criteria vs. Metrics. \red{A blind copy from the google doc -- needs discussion}}
    \label{tab:metric-vs-props}
%\end{table}
\end{sidewaystable}

