
\bibitem{zhang2017regions}
Chao Zhang, Keyang Zhang, Quan Yuan, Haoruo Peng, Yu~Zheng, Tim Hanratty,
  Shaowen Wang, and Jiawei Han.
\newblock Regions, periods, activities: Uncovering urban dynamics via
  cross-modal representation learning.
\newblock In {\em Proceedings of the 26th International Conference on World
  Wide Web}, pages 361--370. International World Wide Web Conferences Steering
  Committee, 2017.

\bibitem{shafrin2017association}
Jason Shafrin, Jeff Sullivan, Dana~P Goldman, and Thomas~M Gill.
\newblock The association between observed mobility and quality of life in the
  near elderly.
\newblock {\em PloS one}, 12(8):e0182920, 2017.

\bibitem{chan2016screening}
Ya-Fen Chan, Shou-En Lu, Bill Howe, Hendrik Tieben, Theresa Hoeft, and
  J{\"u}rgen Un{\"u}tzer.
\newblock Screening and follow-up monitoring for substance use in primary care:
  an exploration of rural--urban variations.
\newblock {\em Journal of general internal medicine}, 31(2):215--222, 2016.

\bibitem{wang2018urban}
Qi~Wang, Nolan~Edward Phillips, Mario~L Small, and Robert~J Sampson.
\newblock Urban mobility and neighborhood isolation in america’s 50 largest
  cities.
\newblock {\em Proceedings of the National Academy of Sciences},
  115(30):7735--7740, 2018.

\bibitem{litman2018evaluating}
Todd Litman.
\newblock {\em Evaluating transportation equity}.
\newblock Victoria Transport Policy Institute, 2018.

\bibitem{shaheen2017travel}
Susan Shaheen, Corwin Bell, Adam Cohen, and Balaji Yelchuru.
\newblock Travel behavior: Shared mobility and transportation equity.
\newblock Technical report, U.S.\ Department of Transportation, 2017.

\bibitem{palmateer2017justice}
Chelsey Palmateer and David~M Levinson.
\newblock Justice, exclusion, and equity: An analysis of 48 us metropolitan
  areas.
\newblock Technical report, University of Minnesota: Nexus Research Group,
  2017.

\bibitem{ricciardi2015exploring}
Anthony~Michael Ricciardi, Jianhong~Cecilia Xia, and Graham Currie.
\newblock Exploring public transport equity between separate disadvantaged
  cohorts: a case study in perth, australia.
\newblock {\em Journal of transport geography}, 43:111--122, 2015.

\bibitem{chetty2016childhood}
Raj Chetty, Nathaniel Hendren, Frina Lin, Jeremy Majerovitz, and Benjamin
  Scuderi.
\newblock Childhood environment and gender gaps in adulthood.
\newblock {\em American Economic Review}, 106(5):282--88, 2016.

\bibitem{goldman2006sustainable}
Todd Goldman and Roger Gorham.
\newblock Sustainable urban transport: Four innovative directions.
\newblock {\em Technology in society}, 28(1-2):261--273, 2006.

\bibitem{ge2016racial}
Yanbo Ge, Christopher~R Knittel, Don MacKenzie, and Stephen Zoepf.
\newblock Racial and gender discrimination in transportation network companies.
\newblock Technical report, National Bureau of Economic Research, 2016.

\bibitem{zliobaite2015survey}
Indre Zliobaite.
\newblock A survey on measuring indirect discrimination in machine learning.
\newblock {\em CoRR}, abs/1511.00148, 2015.

\bibitem{petrasic2017algorithms}
Kevin Petrasic, Benjamin Saul, James Greig, Matthew Bornfreund, and Katherine
  Lamberth.
\newblock Algorithms and bias: What lenders need to know.
\newblock {\em White \& Case}, 2017.

\bibitem{miller2015algorithms}
Claire~Cain Miller.
\newblock When algorithms discriminate.
\newblock {\em The New York Times}, 9, 2015.

\bibitem{rudin2013predictive}
Cynthia Rudin.
\newblock Predictive policing using machine learning to detect patterns of
  crime.
\newblock {\em Wired Magazine, August}, 2013.

\bibitem{barocas2017fairness}
Solon Barocas, Moritz Hardt, and Arvind Narayanan.
\newblock Fairness in machine learning.
\newblock {\em NIPS Tutorial}, 2017.

\bibitem{guynn2015google}
Jessica Guynn.
\newblock Google photos labeled black people’gorillas’.
\newblock {\em USA Today}, 1, 2015.

\bibitem{ingold2016amazon}
David Ingold and Spencer Soper.
\newblock Amazon doesn’t consider the race of its customers. should it.
\newblock {\em Bloomberg}, 2016.

\bibitem{lepri2017tyranny}
Bruno Lepri, Jacopo Staiano, David Sangokoya, Emmanuel Letouz{\'e}, and Nuria
  Oliver.
\newblock The tyranny of data? the bright and dark sides of data-driven
  decision-making for social good.
\newblock In {\em Transparent data mining for big and small data}, pages 3--24.
  Springer, 2017.

\bibitem{barocas2016big}
Solon Barocas and Andrew~D Selbst.
\newblock Big data's disparate impact.
\newblock {\em Calif. L. Rev.}, 104:671, 2016.

\bibitem{caliskan2017semantics}
Aylin Caliskan, Joanna~J Bryson, and Arvind Narayanan.
\newblock Semantics derived automatically from language corpora contain
  human-like biases.
\newblock {\em Science}, 356(6334):183--186, 2017.

\bibitem{pennington2014glove}
Jeffrey Pennington, Richard Socher, and Christopher Manning.
\newblock Glove: Global vectors for word representation.
\newblock In {\em Proceedings of the 2014 conference on empirical methods in
  natural language processing (EMNLP)}, pages 1532--1543, 2014.

\bibitem{chouldechova2018frontiers}
Alexandra Chouldechova and Aaron Roth.
\newblock The frontiers of fairness in machine learning.
\newblock {\em CoRR}, abs/1810.08810, 2018.

\bibitem{lum2016predict}
Kristian Lum and William Isaac.
\newblock To predict and serve?
\newblock {\em Significance}, 13(5):14--19, 2016.

\bibitem{young2019beyond}
Meg Young, Luke Rodriguez, Emily Keller, Feiyang Sun, Boyang Sa, Jan
  Whittington, and Bill Howe.
\newblock Beyond open vs. closed: Balancing individual privacy and public
  accountability in data sharing.
\newblock In {\em Proceedings of the Conference on Fairness, Accountability,
  and Transparency}, pages 191--200. ACM, 2019.

\bibitem{lepri2018fair}
Bruno Lepri, Nuria Oliver, Emmanuel Letouz{\'e}, Alex Pentland, and Patrick
  Vinck.
\newblock Fair, transparent, and accountable algorithmic decision-making
  processes.
\newblock {\em Philosophy \& Technology}, 31(4):611--627, 2018.

\bibitem{burrell2016machine}
Jenna Burrell.
\newblock How the machine ‘thinks’: Understanding opacity in machine
  learning algorithms.
\newblock {\em Big Data \& Society}, 3(1):2053951715622512, 2016.

\bibitem{delbosc2011using}
Alexa Delbosc and Graham Currie.
\newblock Using lorenz curves to assess public transport equity.
\newblock {\em Journal of Transport Geography}, 19(6):1252--1259, 2011.

\bibitem{lucas2016method}
Karen Lucas, Bert Van~Wee, and Kees Maat.
\newblock A method to evaluate equitable accessibility: combining ethical
  theories and accessibility-based approaches.
\newblock {\em Transportation}, 43(3):473--490, 2016.

\bibitem{feng2014trade}
Tao Feng and Harry~JP Timmermans.
\newblock Trade-offs between mobility and equity maximization under
  environmental capacity constraints: A case study of an integrated
  multi-objective model.
\newblock {\em Transportation Research Part C: Emerging Technologies},
  43:267--279, 2014.

\bibitem{thomopoulos2009incorporating}
Nikolas Thomopoulos, Susan Grant-Muller, and MR~Tight.
\newblock Incorporating equity considerations in transport infrastructure
  evaluation: Current practice and a proposed methodology.
\newblock {\em Evaluation and program planning}, 32(4):351--359, 2009.

\bibitem{raphael2002car}
Steven Raphael and Lorien Rice.
\newblock Car ownership, employment, and earnings.
\newblock {\em Journal of Urban Economics}, 52(1):109--130, 2002.

\bibitem{bullard2003addressing}
Robert~D Bullard.
\newblock Addressing urban transportation equity in the united states.
\newblock {\em Fordham Urb. LJ}, 31:1183, 2003.

\bibitem{el2016cost}
Ahmed El-Geneidy, David Levinson, Ehab Diab, Genevieve Boisjoly, David Verbich,
  and Charis Loong.
\newblock The cost of equity: Assessing transit accessibility and social
  disparity using total travel cost.
\newblock {\em Transportation Research Part A: Policy and Practice},
  91:302--316, 2016.

\bibitem{vasconcellos2018urban}
Eduardo~Alcantara Vasconcellos.
\newblock Urban transport policies in brazil: The creation of a discriminatory
  mobility system.
\newblock {\em Journal of transport geography}, 67, 2018.

\bibitem{cohen2017framework}
Stuart Cohen and Clarrissa Cabansagan.
\newblock A framework for equity in new mobility, 2017.

\bibitem{manaugh2015integrating}
Kevin Manaugh, Madhav~G Badami, and Ahmed~M El-Geneidy.
\newblock Integrating social equity into urban transportation planning: A
  critical evaluation of equity objectives and measures in transportation plans
  in north america.
\newblock {\em Transport policy}, 37:167--176, 2015.

\bibitem{ogilvie2012inequalities}
Flora Ogilvie and Anna Goodman.
\newblock Inequalities in usage of a public bicycle sharing scheme:
  socio-demographic predictors of uptake and usage of the london (uk) cycle
  hire scheme.
\newblock {\em Preventive medicine}, 55(1):40--45, 2012.

\bibitem{meng2018evaluation}
Chao Meng.
\newblock Evaluation of the equity of bikeshare system accessibility: A case
  study of chicago.
\newblock Technical report, Georgia Institute of Technology, 2018.

\bibitem{ursaki2015quantifying}
Julia Ursaki, Lisa Aultman-Hall, et~al.
\newblock Quantifying the equity of bikeshare access in us cities.
\newblock Technical report, University of Vermont. Transportation Research
  Center, 2015.

\bibitem{smith2015exploring}
C~Scott Smith, Jun-Seok Oh, and Cheyenne Lei.
\newblock Exploring the equity dimensions of us bicycle sharing systems.
\newblock Technical report, Western Michigan University. Transportation
  Research Center for Livable, 2015.

\bibitem{li2018free}
Xuefeng Li, Yong Zhang, Li~Sun, and Qiyang Liu.
\newblock Free-floating bike sharing in jiangsu: Users’ behaviors and
  influencing factors.
\newblock {\em Energies}, 11(7):1664, 2018.

\bibitem{mooney2019freedom}
Stephen~J Mooney, Kate Hosford, Bill Howe, An~Yan, Meghan Winters, Alon Bassok,
  and Jana~A Hirsch.
\newblock Freedom from the station: Spatial equity in access to dockless bike
  share.
\newblock {\em Journal of Transport Geography}, 74:91--96, 2019.

\bibitem{xu2018station}
Chengcheng Xu, Junyi Ji, and Pan Liu.
\newblock The station-free sharing bike demand forecasting with a deep learning
  approach and large-scale datasets.
\newblock {\em Transportation research part C: emerging technologies},
  95:47--60, 2018.

\bibitem{daddio2012maximizing}
David~William Daddio and N~Mcdonald.
\newblock Maximizing bicycle sharing: an empirical analysis of capital
  bikeshare usage.
\newblock {\em University of North Carolina at Chapel Hill}, 8, 2012.

\bibitem{rixey2013station}
R~Alexander Rixey.
\newblock Station-level forecasting of bikesharing ridership: station network
  effects in three us systems.
\newblock {\em Transportation Research Record}, 2387(1):46--55, 2013.

\bibitem{mcneil2017breaking}
Nathan McNeil, Jennifer Dill, John MacArthur, Joseph Broach, and Steven
  Howland.
\newblock Breaking barriers to bike share: Insights from residents of
  traditionally underserved neighborhoods.
\newblock {\em Transportation Research and Education Center (TREC)}, 2017.

\bibitem{kretman2011bringing}
SS~Kretman, DC~Johnson, and WP~Smith.
\newblock Bringing bike share to a low-income community: Lessons learned
  through community engagement, minneapolis, minnesota.
\newblock {\em Preventing Chronic Disease}, 2011.

\bibitem{brown2018ridehail}
Anne~Elizabeth Brown.
\newblock {\em Ridehail revolution: Ridehail travel and equity in Los Angeles}.
\newblock PhD thesis, UCLA, 2018.

\bibitem{hughes2016transportation}
Ryan Hughes and Don MacKenzie.
\newblock Transportation network company wait times in greater seattle, and
  relationship to socioeconomic indicators.
\newblock {\em Journal of Transport Geography}, 56:36--44, 2016.

\bibitem{wang2018spatial}
Mingshu Wang and Lan Mu.
\newblock Spatial disparities of uber accessibility: An exploratory analysis in
  atlanta, usa.
\newblock {\em Computers, Environment and Urban Systems}, 67:169--175, 2018.

\bibitem{stark2016uber}
Jennifer Stark and Nicholas Diakopoulos.
\newblock Uber seems to offer better service in areas with more white people.
  that raises some tough questions.
\newblock {\em The Washington Post}, 2016.

\bibitem{middleton2018discrimination}
Scott Scott~Russell Middleton.
\newblock {\em Discrimination, regulation, and design in ridehailing}.
\newblock PhD thesis, Massachusetts Institute of Technology, 2018.

\bibitem{jin2019uber}
Scarlett~T Jin, Hui Kong, and Daniel~Z Sui.
\newblock Uber, public transit, and urban transportation equity: A case study
  in new york city.
\newblock {\em The Professional Geographer}, pages 1--16, 2019.

\bibitem{lazar2017research}
Jonathan Lazar, Jinjuan~Heidi Feng, and Harry Hochheiser.
\newblock {\em Research methods in human-computer interaction}.
\newblock Morgan Kaufmann, 2017.

\bibitem{fotheringham2003geographically}
A~Stewart Fotheringham, Chris Brunsdon, and Martin Charlton.
\newblock {\em Geographically weighted regression: the analysis of spatially
  varying relationships}.
\newblock John Wiley \& Sons, 2003.

\bibitem{speicher2018unified}
Till Speicher, Hoda Heidari, Nina Grgic-Hlaca, Krishna~P Gummadi, Adish Singla,
  Adrian Weller, and Muhammad~Bilal Zafar.
\newblock A unified approach to quantifying algorithmic unfairness: Measuring
  individual \&group unfairness via inequality indices.
\newblock In {\em Proceedings of the 24th ACM SIGKDD International Conference
  on Knowledge Discovery \& Data Mining}, pages 2239--2248. ACM, 2018.

\bibitem{useeoc}
The~U.S. EEOC.
\newblock Uniform guidelines on employee selection procedures.
\newblock {\em March 2, 1979}, 43:111--122, 1979.

\bibitem{feldman2015certifying}
Michael Feldman, Sorelle~A Friedler, John Moeller, Carlos Scheidegger, and
  Suresh Venkatasubramanian.
\newblock Certifying and removing disparate impact.
\newblock In {\em Proceedings of the 21th ACM SIGKDD International Conference
  on Knowledge Discovery and Data Mining}, pages 259--268. ACM, 2015.

